### 2019-09-02 C11-BackEnds/Clean/document/root.tex
first config for producing a report - build -D. should work

\documentclass[11pt,a4paper]{article}
\usepackage{isabelle,isabellesym}

% further packages required for unusual symbols (see also
% isabellesym.sty), use only when needed

%\usepackage{amssymb}
  %for \<leadsto>, \<box>, \<diamond>, \<sqsupset>, \<mho>, \<Join>,
  %\<lhd>, \<lesssim>, \<greatersim>, \<lessapprox>, \<greaterapprox>,
  %\<triangleq>, \<yen>, \<lozenge>

%\usepackage{eurosym}
  %for \<euro>

\usepackage[only,bigsqcap]{stmaryrd}
  %for \<Sqinter>

%\usepackage{eufrak}
  %for \<AA> ... \<ZZ>, \<aa> ... \<zz> (also included in amssymb)

%\usepackage{textcomp}
  %for \<onequarter>, \<onehalf>, \<threequarters>, \<degree>, \<cent>,
  %\<currency>

% this should be the last package used
\usepackage{pdfsetup}

% urls in roman style, theory text in math-similar italics
\urlstyle{rm}
\isabellestyle{it}

% for uniform font size
%\renewcommand{\isastyle}{\isastyleminor}
\usepackage{wrapfig}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{lstisadof}

\newcommand{\HOL}{HOL}
\newcommand{\eg}{e.g.}
\newcommand{\ie}{i.e.}

\begin{document}

\title{Clean - An Abstract Imperative Programming Language and its Theory}
\author{Frederic Tuong and Burkhart Wolff (with Contribs of Chantal Keller)}
\maketitle
\begin{abstract}
dfgdfg dfgdfg dfgdfg
\end{abstract}

\tableofcontents

% sane default for proof documents
\parindent 0pt\parskip 0.5ex

% generated text of all theories
\input{session}

% optional bibliography
%\bibliographystyle{abbrv}
%\bibliography{root}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-09-03 C11-BackEnds/Clean/document/root.tex
build
Brought documentation roughly into shape.

@@
-\documentclass[11pt,a4paper]{article}
+\documentclass[fontsize=11pt,paper=a4,open=right,twoside,abstract=true]{scrreprt}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage{lmodern}
+\usepackage[numbers, sort&compress, sectionbib]{natbib}
 \usepackage{isabelle,isabellesym}
-
-% further packages required for unusual symbols (see also
-% isabellesym.sty), use only when needed
-
-%\usepackage{amssymb}
-  %for \<leadsto>, \<box>, \<diamond>, \<sqsupset>, \<mho>, \<Join>,
-  %\<lhd>, \<lesssim>, \<greatersim>, \<lessapprox>, \<greaterapprox>,
-  %\<triangleq>, \<yen>, \<lozenge>
-
-%\usepackage{eurosym}
-  %for \<euro>
-
 \usepackage[only,bigsqcap]{stmaryrd}
-  %for \<Sqinter>
-
-%\usepackage{eufrak}
-  %for \<AA> ... \<ZZ>, \<aa> ... \<zz> (also included in amssymb)
-
-%\usepackage{textcomp}
-  %for \<onequarter>, \<onehalf>, \<threequarters>, \<degree>, \<cent>,
-  %\<currency>
-
-% this should be the last package used
-\usepackage{pdfsetup}
-
-% urls in roman style, theory text in math-similar italics
-\urlstyle{rm}
-\isabellestyle{it}
-
-% for uniform font size
-%\renewcommand{\isastyle}{\isastyleminor}
+\usepackage{ifthen}
 \usepackage{wrapfig}
@@
 \usepackage{lstisadof}
+\IfFileExists{railsetup.sty}{\usepackage{railsetup}}{}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% command
+
+\newenvironment{matharray}[1]{\[\begin{array}{#1}}{\end{array}\]} % from 'iman.sty'
+\newcommand{\indexdef}[3]%
+{\ifthenelse{\equal{}{#1}}{\index{#3 (#2)|bold}}{\index{#3 (#1\ #2)|bold}}} % from 'isar.sty'
+\newcommand{\isactrlC}{{\bf C}}
+
+%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% fix for package declaration to be at the end
+\usepackage[pdfpagelabels, pageanchor=false, plainpages=false]{hyperref}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% document
+
+\urlstyle{rm}
+\isabellestyle{it}
 
@@
 \title{Clean - An Abstract Imperative Programming Language and its Theory}
-\author{Frederic Tuong and Burkhart Wolff (with Contribs of Chantal Keller)}
+\author{Frederic Tuong and Burkhart Wolff \\ (with Contributions of Chantal Keller)}
 \maketitle
+
 \begin{abstract}
-dfgdfg dfgdfg dfgdfg
+Clean (pronounced as: ``C lean'') is based on a simple, abstract execution model for an 
+imperative target language. "Abstract" is understood as contrast to "Concrete Semantics";
+alternatively, the term "shallow-style embedding" could be used.
+
+Clean is based on a ``no-frills'' state-exception monad  with the 
+usual definitions of \verb+bind+ and \verb+unit+ for the compositional glue of
+state-based computations. Clean offers conditionals and loops supporting C-like 
+control-flow operators such as \verb+break+ and \verb+return+.
+The memory model is fully \HOL -typed and based on a construction nesting
+subsequently extensible records. Note that the current version only supports
+monomorphic states and parameters of (directly recursive) functions.
+
+The design is striving for extreme simplicity. It is geared towards symbolic execution and
+proven correct verification tools. The underlying libraries of this package, however,
+deliberately restricts itself to the most elementary infrastructure for these tasks. 
+The package is intended to serve as demonstrator semantic backend for Isabelle/C \cite{TuongWolff19},
+serving as basis for the test-generation technique described in \cite{DBLP:conf/tap/Keller18} .
 \end{abstract}
 
+\newpage
 \tableofcontents
 
-% sane default for proof documents
 \parindent 0pt\parskip 0.5ex
 
-% generated text of all theories
-\input{session}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \input{session}
+\newpage
+\input{Clean.tex}
 
-% optional bibliography
-%\bibliographystyle{abbrv}
-%\bibliography{root}
+\input{Quicksort_concept.tex}
+
+\newpage
+\section{Appendix : Used Monad Libraries}
+\input{MonadSE.tex}
+
+\input{Seq_MonadSE.tex}
+
+\input{Symbex_MonadSE.tex}
+
+\input{SquareRoot_concept.tex}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\bibliographystyle{abbrvnat}
+\bibliography{root}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2019-09-10 C11-BackEnds/Clean/document/root.tex
document

@@
 \title{Clean - An Abstract Imperative Programming Language and its Theory}
-\author{Frederic Tuong and Burkhart Wolff \\ (with Contributions of Chantal Keller)}
+\author{%
+  \href{https://www.lri.fr/~ftuong/}{Fr\'ed\'eric Tuong}
+  \and
+  \href{https://www.lri.fr/~wolff/}{Burkhart Wolff} \\
+  \and
+  (with Contributions of \href{https://www.lri.fr/~keller/}{Chantal Keller})}
+\publishers{%
+  \mbox{LRI, Univ. Paris-Sud, CNRS, Universit\'e Paris-Saclay} \\
+  b\^at. 650 Ada Lovelace, 91405 Orsay, France \texorpdfstring{\\}{}
+}
+
 \maketitle
@@
 \begin{abstract}
-Clean (pronounced as: ``C lean'') is based on a simple, abstract execution model for an 
-imperative target language. "Abstract" is understood as contrast to "Concrete Semantics";
-alternatively, the term "shallow-style embedding" could be used.
+Clean (pronounced as: ``Céline'' [selin]) is based on a simple, abstract execution model for an
+imperative target language. ``Abstract'' is understood as contrast to ``Concrete Semantics'';
+alternatively, the term ``shallow-style embedding'' could be used.
 
-Clean is based on a ``no-frills'' state-exception monad  with the 
-usual definitions of \verb+bind+ and \verb+unit+ for the compositional glue of
-state-based computations. Clean offers conditionals and loops supporting C-like 
-control-flow operators such as \verb+break+ and \verb+return+.
-The memory model is fully \HOL -typed and based on a construction nesting
-subsequently extensible records. Note that the current version only supports
-monomorphic states and parameters of (directly recursive) functions.
+Clean is based on a ``no-frills'' state-exception monad with the usual definitions of \isa{bind} and
+\isa{unit} for the compositional glue of state-based computations. Clean offers conditionals and
+loops supporting C-like control-flow operators such as \isa{break} and \isa{return}. The memory
+model is fully \HOL{}-typed and based on a construction nesting subsequently extensible
+records. Note that the current version only supports monomorphic states and parameters of (directly
+recursive) functions.
 
-The design is striving for extreme simplicity. It is geared towards symbolic execution and
-proven correct verification tools. The underlying libraries of this package, however,
-deliberately restricts itself to the most elementary infrastructure for these tasks. 
-The package is intended to serve as demonstrator semantic backend for Isabelle/C \cite{TuongWolff19},
-serving as basis for the test-generation technique described in \cite{DBLP:conf/tap/Keller18} .
+The design is striving for extreme simplicity. It is geared towards symbolic execution and proven
+correct verification tools. The underlying libraries of this package, however, deliberately
+restricts itself to the most elementary infrastructure for these tasks. The package is intended to
+serve as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, serving as basis for the
+test-generation technique described in~\cite{DBLP:conf/tap/Keller18}.
 \end{abstract}

### 2019-09-12 C11-BackEnds/Clean/document/root.tex
switch headers
substantially improved documentation

@@
 \begin{abstract}
-Clean (pronounced as: ``Céline'' [selin]) is based on a simple, abstract execution model for an
+Clean  is based on a simple, abstract execution model for an
 imperative target language. ``Abstract'' is understood as contrast to ``Concrete Semantics'';
-alternatively, the term ``shallow-style embedding'' could be used.
+alternatively, the term ``shallow-style embedding'' could be used. It strives for a type-safe
+notation of program-variables, an incremental construction of the typed state-space in order 
+to facilitate incremental verification and open-world extensibility to new type definitions 
+intertwined with the the program definition.
 
@@
 \isa{unit} for the compositional glue of state-based computations. Clean offers conditionals and
-loops supporting C-like control-flow operators such as \isa{break} and \isa{return}. The memory
-model is fully \HOL{}-typed and based on a construction nesting subsequently extensible
-records. Note that the current version only supports monomorphic states and parameters of (directly
-recursive) functions.
+loops supporting C-like control-flow operators such as \isa{break} and \isa{return}. The state-space
+is fully \HOL{}-typed and based on an incremental construction based on extensible
+records. Direct recursion of operations is supported.
 
@@
 correct verification tools. The underlying libraries of this package, however, deliberately
-restricts itself to the most elementary infrastructure for these tasks. The package is intended to
+restrict themselves to the most elementary infrastructure for these tasks. The package is intended to
 serve as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, serving as basis for the
@@
 \newpage
-\section{Appendix : Used Monad Libraries}
+\chapter{Appendix : Used Monad Libraries}
 \input{MonadSE.tex}

### 2019-09-17 C11-BackEnds/Clean/document/root.tex

@@
 \begin{abstract}
-Clean  is based on a simple, abstract execution model for an
-imperative target language. ``Abstract'' is understood as contrast to ``Concrete Semantics'';
-alternatively, the term ``shallow-style embedding'' could be used. It strives for a type-safe
-notation of program-variables, an incremental construction of the typed state-space in order 
-to facilitate incremental verification and open-world extensibility to new type definitions 
-intertwined with the the program definition.
+Clean is based on a simple, abstract execution model for an imperative target language. ``Abstract''
+is understood as contrast to ``Concrete Semantics''; alternatively, the term ``shallow-style
+embedding'' could be used. It strives for a type-safe notation of program-variables, an incremental
+construction of typed state-space, facilitating incremental verification approaches, and supports
+open-world extensibility of new type definitions while intertwined with the original program
+definition.
 
@@
 loops supporting C-like control-flow operators such as \isa{break} and \isa{return}. The state-space
-is fully \HOL{}-typed and based on an incremental construction based on extensible
-records. Direct recursion of operations is supported.
+is fully \HOL{}-typed, its incremental construction relies on extensible records. Direct recursion
+of operations is supported.
 
 The design is striving for extreme simplicity. It is geared towards symbolic execution and proven
-correct verification tools. The underlying libraries of this package, however, deliberately
-restrict themselves to the most elementary infrastructure for these tasks. The package is intended to
-serve as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, serving as basis for the
-test-generation technique described in~\cite{DBLP:conf/tap/Keller18}.
+correct verification tools. The underlying libraries of this package, however, deliberately restrict
+themselves to the most elementary infrastructure for these tasks. The package is intended to serve
+as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, or for the test-generation
+technique described in~\cite{DBLP:conf/tap/Keller18}.
 \end{abstract}

### 2019-09-17 C11-BackEnds/Clean/document/root.tex

@@
 embedding'' could be used. It strives for a type-safe notation of program-variables, an incremental
-construction of typed state-space, facilitating incremental verification approaches, and supports
-open-world extensibility of new type definitions while intertwined with the original program
+construction of the typed state-space, support of incremental verification, and 
+open-world extensibility of new type definitions being intertwined with the program
 definition.
@@
 loops supporting C-like control-flow operators such as \isa{break} and \isa{return}. The state-space
-is fully \HOL{}-typed, its incremental construction relies on extensible records. Direct recursion
-of operations is supported.
+construction is based on the extensible record package. Direct recursion of procedures is supported.
 
-The design is striving for extreme simplicity. It is geared towards symbolic execution and proven
+Clean's design strives for extreme simplicity. It is geared towards symbolic execution and proven
 correct verification tools. The underlying libraries of this package, however, deliberately restrict
@@
 \input{Quicksort_concept.tex}
+\input{SquareRoot_concept.tex}
 
@@
 \input{MonadSE.tex}
-
 \input{Seq_MonadSE.tex}
-
 \input{Symbex_MonadSE.tex}
-
-\input{SquareRoot_concept.tex}
+\input{Hoare_MonadSE.tex}
+\input{Hoare_Clean.tex}
 

### 2019-10-14 C11-FrontEnd/document/generated/paper.tex
synchronize with fortesse revision 5360

%
\begin{isabellebody}%
\setisabellecontext{paper}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimML
%
\endisadelimML
%
\isatagML
%
\endisatagML
{\isafoldML}%
%
\isadelimML
%
\endisadelimML
%
\begin{isamarkuptitle*}%
[label = {tit},type = {scholarly_paper.title}, args={label = {tit},type = {scholarly_paper.title}, scholarly_paper.title.short_title = {}}]Deeply Integrating C11 Code Support into Isabelle/PIDE%
\end{isamarkuptitle*}\isamarkuptrue%
%
\begin{isamarkuptext*}%
[label = {bu},type = {scholarly_paper.author}, args={label = {bu},type = {scholarly_paper.author}, scholarly_paper.author.email = {wolff@lri.fr}, scholarly_paper.author.affiliation = {LRI, Univ. Paris-Sud, CNRS, Université Paris-Saclay}, scholarly_paper.author.http_site = {https://www.lri.fr/~wolff/}, scholarly_paper.author.orcid = {}}]Burkhart Wolff%
\end{isamarkuptext*}\isamarkuptrue%
%
\begin{isamarkuptext*}%
[label = {abs},type = {scholarly_paper.abstract}, args={label = {abs},type = {scholarly_paper.abstract}, scholarly_paper.abstract.keywordlist = {{User Interface, Integrated Development, Program Verification, Shallow Embedding}}}]We present a framework for C code in C11 syntax deeply integrated into the Isabelle/PIDE
  development environment. Our framework provides an abstract interface for verification back-ends
  to be plugged-in independently. Thus, various techniques such as deductive program verification or
  white-box testing can be applied to the same source, which is part of an integrated PIDE document
  model. Semantic back-ends are free to choose the supported C fragment and its semantics. In
  particular, they can differ on the chosen memory model or the specification mechanism
  for framing conditions.

  Our framework supports semantic annotations of C sources in the form of comments. Annotations
  serve to locally control back-end settings, and can express the term focus to which
  an annotation refers. Both the logical and the syntactic context are available when semantic
  annotations are evaluated. As a consequence, a formula in an annotation can refer both 
  to  HOL or C variables.

  Our approach demonstrates the degree of maturity and expressive power the Isabelle/PIDE subsystem
  has achieved in recent years. Our integration technique employs Lex and Yacc style grammars to 
  ensure efficient deterministic parsing. We present two case studies for the integration of 
  (known) semantic back-ends in order to validate the design decisions for our
  back-end interface.%
\end{isamarkuptext*}\isamarkuptrue%
%
\begin{isamarkupsection*}%
[label = {intro},type = {scholarly_paper.introduction}, args={label = {intro},type = {scholarly_paper.introduction}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}}]Introduction%
\end{isamarkupsection*}\isamarkuptrue%
%
\begin{isamarkuptext*}%
[label = {introtext},type = {scholarly_paper.introduction}, args={label = {introtext},type = {scholarly_paper.introduction}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}}]\noindent{}Recent successes like the Microsoft Hypervisor project \cite{DBLP:conf/fm/LeinenbachS09},
the verified CompCert compiler \cite{DBLP:journals/cacm/Leroy09}
and the seL4 microkernel \cite{DBLP:conf/sosp/KleinEHACDEEKNSTW09,DBLP:journals/tocs/KleinAEMSKH14} 
show that the verification of low-level systems code has become feasible.
However, a closer look at the underlying verification engines  
VCC \cite{DBLP:conf/tphol/CohenDHLMSST09}, 
or Isabelle/AutoCorres \cite{DBLP:conf/pldi/GreenawayLAK14}
show that the road is still bumpy: the  empirical cost evaluation  of the L4.verified project 
\cite{DBLP:journals/tocs/KleinAEMSKH14} reveals that a very substantial part  of the overall 
effort of about one third of the 28 man years went into the development of libraries and the 
associated tool-chain. Accordingly, the project authors \cite{DBLP:journals/tocs/KleinAEMSKH14} 
express the hope that these overall investments will not have to be repeated for 
``similar projects''.

In fact, none of these verifying compiler tool-chains capture all aspects of ``real life'' 
programming languages such as C. The variety of supported language fragments seem to contradict 
the assumption that we will all converge to one comprehensive tool-chain soon. There are so many 
different choices concerning memory models, non-standard control flow, and execution models 
that a generic framework is desirable: in which verified compilers, deductive verification, 
static analysis and test techniques (such as \cite{DBLP:conf/tap/Keller18}, 
\cite{DBLP:conf/itp/AissatVW16}) can be developed and used inside the Isabelle platform
as part of an integrated document.

In this paper we present Isabelle/C~\footnote{The current developer snapshot is provided in
  \url{https://gitlri.lri.fr/ftuong/isabelle_c}.}, a generic framework in
spirit similar to Frama-C \cite{frama-c-home-page}. In contrast to the latter, Isabelle/C is
deeply integrated into the Isabelle/PIDE document model \cite{DBLP:conf/itp/Wenzel14}. Based on
the C11 standard (ISO/IEC 9899:2011), Isabelle/C parses C11 code inside a rich IDE supporting static
scoping. SML user-programmed extensions can benefit from the parallel evaluation techniques of
Isabelle. The plug-in mechanism of Isabelle/C can integrate diverse semantic representations,
including those already made available in Isabelle/HOL \cite{DBLP:books/sp/NipkowPW02}: AutoCorres
\cite{DBLP:conf/pldi/GreenawayLAK14}, IMP2 \cite{DBLP:journals/afp/LammichW19},
Orca \cite{bockenek:hal-02069705}, or Clean (discussed in this paper). A particular advantage of
the overall approach compared to systems like Frama-C or VCC is that all these semantic
theories are conservative extensions of HOL, hence no axiom-generators are used that produce the
"background theory" and the verification conditions passed to automated provers. Isabelle/C provides
a general infrastructure for semantic annotations specific for back-ends, i.e. modules that generate
from the C source a set of definitions and derive automatically theorems over them.
Last but not least, navigation features of annotations make the logical context explicit in which 
theorems and proofs are interpreted.%
\end{isamarkuptext*}\isamarkuptrue%
%
\begin{isamarkupfigure*}%
[label = {C-sample},type = {Isa_COL.figure}, args={label = {C-sample},type = {Isa_COL.figure}, Isa_COL.figure.relative_width = {60}, Isa_COL.figure.src = {figures/A-C-Source}, Isa_COL.figure.spawn_columns = {True}}]A C11 sample in Isabelle/jEdit%
\end{isamarkupfigure*}\isamarkuptrue%
%
\begin{isamarkuptext}%
The heart of Isabelle/C, the new \isa{\isacommand{C}{\isacartoucheopen}\ {\isachardot}{\isachardot}\ {\isacartoucheclose}} command, is shown in \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{C-sample}. 
Analogously to the existing \isa{\isacommand{ML}{\isacartoucheopen}\ {\isachardot}{\isachardot}\ {\isacartoucheclose}} command, it allows for editing C
sources inside the \isa{{\isacartoucheopen}\ {\isachardot}{\isachardot}\ {\isacartoucheclose}} brackets, where C code is
parsed on the fly in a ``continuous check, continuous build'' manner. A parsed source is coloured
according to the usual conventions applying for Isabelle/HOL variables and keywords. A static
scoping analysis makes the bindings inside the source explicit such that editing gestures like
hovering and clicking may allow the user to reveal the defining variable occurrences and C type
information (see yellow sub-box in the screenshot \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{C-sample}). The C source
may contain comments to set up semantic back-ends. Isabelle/C turns out to be sufficiently efficient
for C sources such as the seL4 project.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
This paper proceeds as follows: in \csname isaDof.ref\endcsname[type={text}]{background}, we
briefly introduce Isabelle/PIDE and its document model, into which our framework is integrated. In
\csname isaDof.ref\endcsname[type={text}]{frontend_arch} and
\csname isaDof.ref\endcsname[type={text}]{ctests}, we discuss the build process and present some experimental results 
on the integrated parser. The handling of semantic annotations comments --- a vital part for 
back-end developers --- is discussed in \csname isaDof.ref\endcsname[type={text}]{annotations}, while in
\csname isaDof.ref\endcsname[type={text}]{backends} we present some techniques to integrate back-ends
into our framework at the hand of examples.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsection*}%
[label = {background},type = {scholarly_paper.technical}, args={label = {background},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''bu''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Background: PIDE and the Isabelle Document Model%
\end{isamarkupsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
\noindent{}The Isabelle system is based on a generic document model allowing for
efficient, highly-parallelized evaluation and checking of its document content (cf. 
\cite{DBLP:conf/itp/Wenzel14,DBLP:journals/corr/Wenzel14,DBLP:conf/mkm/BarrasGHRTWW13}
for the fairly innovative technologies underlying the Isabelle architecture).
These technologies allow for scaling up to fairly large  documents: we have seen documents
with 150 files be loaded in about 4 min, and individual files
--- like the x86 model generated from Antony Fox' L3 specs --- have 80~kLoC and were loaded in 
about the same time.\footnote{On a modern 6-core MacBook Pro with 32Gb memory,
these loading times were counted \emph{excluding} proof checking.}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupfigure*}%
[label = {docmodel1},type = {Isa_COL.figure}, args={label = {docmodel1},type = {Isa_COL.figure}, Isa_COL.figure.relative_width = {20}, Isa_COL.figure.src = {figures/document-model1}, Isa_COL.figure.spawn_columns = {True}}]PIDE interaction%
\end{isamarkupfigure*}\isamarkuptrue%
%
\begin{isamarkupfigure*}%
[label = {docmodel2},type = {Isa_COL.figure}, args={label = {docmodel2},type = {Isa_COL.figure}, Isa_COL.figure.relative_width = {24}, Isa_COL.figure.src = {figures/document-model2}, Isa_COL.figure.spawn_columns = {True}}]PIDE document model%
\end{isamarkupfigure*}\isamarkuptrue%
%
\begin{isamarkuptext}%
%% \begin{wrapfigure}{r}{0.2\textwidth}
%%   \includegraphics[width=0.2\textwidth]{figures/document-model1}
%%   \vspace{-20pt}
%% \end{wrapfigure}
The PIDE (prover IDE) layer in \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{docmodel1} consists of a part written in SML
and another in Scala. Roughly speaking, PIDE implements ``continuous build and continuous check''
functionality over a textual albeit generic document model. It transforms user modifications of text
elements in an instance of this model into increments --- \emph{edits} --- and
communicates them to the Isabelle system. The latter reacts by the creation of a multitude of
light-weight reevaluation threads resulting in an asynchronous stream of
\emph{reports} containing \emph{markup} that is used to annotate
text elements in the editor front-end. For example, such markup is used to highlight variables or
keywords with specific colours, to hyperlink bound variables to their defining occurrences, or to
annotate type information to terms which become displayed by specific user gestures on demand (such
as hovering). Note that PIDE is not an editor, it is the framework that coordinates these
asynchronous information streams and optimizes their evaluation to a certain extent: outdated markup
referring to modified text is dropped, and corresponding re-calculations are oriented to the user
focus, for example. For PIDE, several editor applications have been developed, where Isabelle/jEdit
(\url{https://www.jedit.org}) is the most commonly known. More
experimental alternatives based on Eclipse or Visual Studio Code exist.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{The PIDE Document Model%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
%% \begin{wrapfigure}{r}{0.24\textwidth}
%%   \vspace{-12pt}
%%   \includegraphics[width=0.24\textwidth]{figures/document-model2}
%%   \vspace{-18pt}
%% \end{wrapfigure}
The document model foresees a number of atomic sub-documents (files), which are organized in the
form of an acyclic graph in \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{docmodel2}.
%% \begin{wrapfigure}{r}{0.33\textwidth}
\begin{figure}
  \centering
\begin{minipage}{0.33\textwidth}
\begin{isar}
theory C_Command
  imports C_Eval
  keywords "C" :: thy_decl
       and "C_file" :: thy_load
\end{isar}
\end{minipage}
  \caption{Header of a theory file in the Isabelle/C project}
  \label{fig:thy}
\end{figure}
%% \end{wrapfigure}
Such graphs can be grouped into sub-graphs called \emph{sessions} which can be compiled to binaries in 
order to avoid long compilation times --- Isabelle/C as such is a session. Sub-documents have a 
unique  name (the mapping to file paths in an underlying file-system is done in an integrated build 
management). The primary format of atomic sub-documents is \isatt{.thy} (historically for
``theory''), secondary formats can be \isatt{.sty}, \isatt{.tex}, \isatt{.c} or other sub-documents processed 
by Isabelle and listed in a configuration of the build system.

A \isatt{.thy} file as in \autoref{fig:thy} consists of a \emph{context
definition} and a body consisting of a sequence of \emph{commands}. The
context definition includes the sections \isa{\isakeyword{imports}} and
\isa{\isakeyword{keywords}}.  For example our context definition states that
\isa{C{\isacharunderscore}Command} is the name of the sub-document depending on
\isa{C{\isacharunderscore}Eval} which transitively includes the parser sources as (ML files)
sub-documents, as well as the C environment and the infrastructure for defining C level
annotations. \emph{Keywords} like \isa{\isacommand{C}} or
\isa{\isacommand{C{\isacharunderscore}file}} must be declared before use.

For this work, it is vital that predefined commands allow for the dynamic creation of
\emph{user-defined} commands similarly to the definition of new functions in a shell
interpreter. Semantically, commands are transition functions $\sigma \rightarrow \sigma$ where
$\sigma$ represents the system state called \emph{logical context}. The logical context in 
interactive provers contains --- among many other things --- the declarations of types, constant
symbols as well as the database with the definitions and established theorems.
A command starts with a pre-declared keyword followed by the specific syntax of this command; an
\emph{evaluation} of a command parses the input till the next command, and transfers
the parsed input to a transition function, which can be configured in a late binding table. Thus,
the evaluation of the generic document model allows for user programmed extensions including IDE and
document generation.

Note that the Isabelle platform supports multiple syntax embeddings, i.e. the possibility
of nesting different language syntaxes inside the upper command syntax, using the
\isa{{\isacartoucheopen}\ {\isachardot}{\isachardot}\ {\isacartoucheclose}} brackets (such parsing techniques will be exploited in \csname isaDof.ref\endcsname[type={text}]{annotations}).  Accordingly, these syntactic sub-contexts may be
nested. In particular, in most of these sub-contexts, there may be a kind of semantic macro ---
called antiquotation and syntactically denoted in the format
\inlineisar+\at{name \<Open> .. \<Close>}+ --- that has access to the underlying logical context.
Similar to commands, user-defined antiquotations may be registered in a late-binding table. For
example, the standard \emph{term}-antiquotation in
\isa{\isacommand{ML}}\inlineisar|\<Open> val t = \at{term "3 +"} \<Close>| parses the argument \inlineisar|"3 +"| with
the Isabelle/HOL term parser, attempts to construct a $\lambda$-term in the internal
term representation and to bind it to \isatt{t}; however, this fails (the plus operation is
declared infix in logical context) and therefore the entire command fails.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Some Basics of PIDE Programming%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
%% \begin{wrapfigure}{r}{0.47\textwidth}
%%   \vspace{-5pt}
\begin{figure}
  \centering
\begin{minipage}{0.47\textwidth}
\begin{isar}
ML\<Open> val pos = \at{here};
    val markup = Position.here pos;
    writeln ("And a link to the declaration\
              \ of 'here' is " ^ markup) \<Close>
\end{isar}
\end{minipage}
  \caption{Referring to an editing source position with the ML antiquotation \isatt{@{\char`\{}here{\char`\}}}}
  \label{fig:ml-pos}
\end{figure}
%%   \vspace{-15pt}
%% \end{wrapfigure}
A basic data-structure relevant for PIDE is \emph{positions}; beyond the usual line
and column information they can represent ranges, list of continuous ranges, and the name of the
atomic sub-document in which they are contained. It is straightforward in \autoref{fig:ml-pos} to
use the antiquotation \inlineisar|\at{here}| to infer from the system lexer the actual position of
the antiquotation in the global document. The system converts the position to a markup
representation (a string representation) and sends the result via \isatt{writeln} to
the interface.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupfigure*}%
[label = {hyplinkout},type = {Isa_COL.figure}, args={label = {hyplinkout},type = {Isa_COL.figure}, Isa_COL.figure.relative_width = {40}, Isa_COL.figure.src = {figures/markup-demo}, Isa_COL.figure.spawn_columns = {True}}]Output window showing the evaluation result of \autoref{fig:ml-pos} (clicking on the hyperlink $\protect\house$ makes the cursor jump to the \isatt{@{\char`\{}here{\char`\}}} of \autoref{fig:ml-pos})%
\end{isamarkupfigure*}\isamarkuptrue%
%
\begin{isamarkuptext}%
%% \begin{wrapfigure}{r}{0.4\textwidth}
%%   \vspace{-8pt}
%%   \includegraphics[width=0.4\textwidth]{figures/markup-demo}
%%   \vspace{-20pt}
%% \end{wrapfigure}
In return, the PIDE output window in \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{hyplinkout} shows the little house-like
symbol $\house$, which is actually hyperlinked to the position of \inlineisar|\at{here}|. The ML
structures \isatt{Markup} and \isatt{Properties}
represent the basic libraries for annotation data which is part of the protocol sent from Isabelle
to the front-end. They are qualified as ``quasi-abstract'', which means they are intended to be an
abstraction of the serialized, textual presentation of the protocol. A markup must be tagged with a
unique id; this is done by the library \isatt{serial} function. Typical code for taking
a string \isatt{cid} from the editing window, together with its position
\isatt{pos}, and sending a specific markup referring to this in the editing window
managed by PIDE looks like this:
\begin{isar}
ML\<Open> fun report_def_occur pos cid = Position.report pos (my_markup true cid (serial ()) pos) \<Close>
\end{isar}
Note that \isatt{my{\char`\_}markup} (not shown here) generates the layout attributes of the link and 
that the \isatt{true} flag is used for markup declaring \isatt{cid} as a defining occurrence, i.e. 
as \emph{target} (rather than the \emph{source}) in the hyperlink animation in PIDE.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsection*}%
[label = {frontend_arch},type = {scholarly_paper.technical}, args={label = {frontend_arch},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''bu''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]The C11 Parser Generation Process and Architecture%
\end{isamarkupsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
Isabelle uses basically two parsing technologies:

%
\begin{enumerate}%
\item Earley parsing \cite{DBLP:journals/cacm/Earley70}
intensively used for mixfix-syntax denoting $\lambda$-terms in mathematical notation,

\item combinator parsing \cite{DBLP:journals/jfp/Hutton92} typically used for high-level 
command syntax.%
\end{enumerate}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Both technologies offer the dynamic extensibility necessary for Isabelle as an
interactive platform geared towards incremental development and sophisticated mathematical
notations. However, since it is our goal to support \emph{programming languages} in
a fast parse-check-eval cycle inside an IDE, we opt for a Lex and Yacc deterministic grammar
approach. It turns out the resulting automata based parser performs well enough for our purpose; the
gain in performance is discussed in the next section.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
In the following, we describe a novel technique for the construction and integration of
this type of parser into the Isabelle platform. Since it is mostly relevant for integrators copying
our process to similar languages such as JavaScript or Rust \footnote{E.g.
\url{http://hackage.haskell.org/package/language-javascript} or
\url{http://hackage.haskell.org/package/language-rust}}, users of the
Isabelle/C platform may skip this section: for them, the take-home message is that the overall
generation process takes about 1 hour, the compilation of the generated files takes 15s, and that
the generated files should be fairly portable to future Isabelle versions.\footnote{In our
  experiments, files generated with a version $i$ of Isabelle natively work when loaded with a more
  recent version $j$, for any versions $i$ and $j$ satisfying $2016 \leq i \leq j \leq 2019$ (at the
  time of writing).}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
We base our work on the C11 parsing library
  \url{http://hackage.haskell.org/package/language-c} implemented in Haskell by
Huber, Chakravarty, Coutts and Felgenhauer; we particularly focus on its open-source Haskell Yacc
grammar as our starting point. We would like to emphasize that this is somewhat arbitrary, our build
process can be easily adapted to more recent versions when available.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupfigure*}%
[label = {architecture},type = {Isa_COL.figure}, args={label = {architecture},type = {Isa_COL.figure}, Isa_COL.figure.relative_width = {70}, Isa_COL.figure.src = {figures/C11-Package-Architecture}, Isa_COL.figure.spawn_columns = {True}}]The architecture of Isabelle/C%
\end{isamarkupfigure*}\isamarkuptrue%
%
\begin{isamarkuptext}%
The diagram in \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{architecture} presents the architecture of
Isabelle/C. The original Haskell library was not modified, it is presented in blue together with
generated sources, in particular the final two blue boxes represent about 11~kLoC. In output, the
glue code in brown constitutes the core implementation of Isabelle/C, amounting to 6~kLoC (without
yet considering semantic back-ends).%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsubsection*}%
[label = {arch1},type = {scholarly_paper.technical}, args={label = {arch1},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''bu''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Generating the AST%
\end{isamarkupsubsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
In the following, we refer to \emph{languages} by $\mathcal{L}$,
$\mathcal{I}$. The notation $\text{AST}^{\mathcal{L}}_{\mathcal{I}}$ refers to abstract syntaxes for
language $\mathcal{L}$ implemented in language $\mathcal{I}$. For example, we refer by
$\text{AST}^{\text{C11}}_{\text{ML}}$ to an AST implementation of C11 implemented in SML. Indices
will be dropped when no confusion arises, or to highlight the fact that our approach is
sufficiently generic.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
For our case, we exploit that from a given Haskell source $\text{AST}_{\text{HS}}$,
Haskabelle generates to a maximum extent an Isabelle/HOL theory. Via the Isabelle code generator, an
$\text{AST}_{\text{ML}}$ can be obtained from a constructive $\text{AST}_{\text{HOL}}$
representation. Ultimately, the process to compile $\text{AST}_{\text{HS}}$ to $\text{AST}_{\text{ML}}$
is done only once at build time, it comprises:

%
\begin{enumerate}%
\item the generation of $\text{AST}_{\text{HOL}}$ from $\text{AST}_{\text{HS}}$, represented as a
collection of \isa{\isacommand{datatype}},

\item the execution of the \isa{\isacommand{datatype}} theory for $\text{AST}_{\text{HOL}}$ and checking of all their
proofs,

\item the generation of an $\text{AST}_{\text{ML}}$ from $\text{AST}_{\text{HOL}}$.%
\end{enumerate}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
The choice on getting an Isabelle/HOL theory in the intermediate step allows us to make
additional checks on the imported AST (e.g. non-emptiness of the imported types), as well as to use
it as a first trusted basis point for further translations and reasoning activities (in \csname isaDof.ref\endcsname[type={text}]{parser_validation}). However, relying on an intermediate $\text{AST}_{\text{HOL}}$
in the above process is technically challenging for practical reasons. This is related to the
prerequisites any HOL types must satisfy before being integrated in Isabelle: proofs of generated
rules might take some time, or additional theorems must be proved before one can invoke the ML code
generator on the types...

We present in the next descriptions below the main encountered corner cases, and how we solved
them.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Maintenance of Haskabelle%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The generation time for Step 1 involving Haskabelle is almost irrelevant (a few
seconds), but first requires to significantly update Haskabelle from an abandoned Isabelle2016
distribution.\footnote{See
  e.g. \url{https://lists.cam.ac.uk/mailman/htdig/cl-isabelle-users/2016-December/msg00096.html}
  and
  \url{https://mailmanbroy.informatik.tu-muenchen.de/pipermail/isabelle-dev/2016-October/015677.html}.}

Haskabelle is implemented in Haskell and mainly relies on a meta-programming library
haskell-src-exts.\footnote{\url{https://hackage.haskell.org/package/haskell-src-exts}} The
design of this library drastically changed in 2016, making a new port of Haskabelle proportionally
difficult. This sole reason has motivated the Isabelle developers of not maintaining anymore
Haskabelle in the Isabelle distributions (it is discarded since Isabelle2016). The interested reader
can find near our Isabelle/C source our renovated version of Haskabelle compatible with the latest
official versions of Isabelle.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Limitation of Haskabelle on certain $\text{AST}_{\text{HS}}$%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
Since the support of Haskabelle on Haskell source is not complete, there would possibly
remain Haskell construction features used by $\text{AST}_{\text{HS}}$ left for an additional
implementation task. For example, for the case of $\text{AST}^{\text{C11}}$, we have brought support
for handling mutually recursive type declarations, particularly in the case where such type
declarations are made by interleaving several Haskell keywords \isatt{type} and
\isatt{data}. (The case of a mutually type declarations performed by only using
several \isatt{data} was already supported.)%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Resources needed to execute the generated HOL datatype theory%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
To our knowledge, our chosen $\text{AST}^{\text{C11}}$ as importation has the most
enormous size among any existing ASTs, e.g., ever published in the Isabelle AFP repository (more
than 350 generated constants). Even if the generation with Haskabelle in Step 1 just takes a few
seconds, Step 2 becomes much longer to execute: the generated
\isa{\isacommand{datatype}}-theory correctly terminates only after 17 hours of elapsed
time (or 70 hours of cpu time, with a gain factor of 4). Alternatively, one can skip the execution
of proofs by activating the Isabelle \isa{quick{\isacharminus}and{\isacharminus}dirty} option: this makes the resulting
theory taking 40~min. A main reason for the resource issue is the 20 mutually recursive
sub-definitions of $\text{AST}_{\text{HOL}}$ (leading meanwhile to 6275 generated theorems). It is
well known that large mutually recursive datatypes are impacting the resource performance, other
projects encountered similar difficulties, see for instance
\url{https://lists.cam.ac.uk/pipermail/cl-isabelle-users/2016-March/msg00034.html}
and
\url{https://lists.cam.ac.uk/pipermail/cl-isabelle-users/2017-April/msg00000.html}.

Of course, in the best scenario one could imagine the generator at Step 1 executing a more optimized
algorithm to automatically remove any problematic mutual recursions as far as it is decidable (after
the execution of Haskabelle, or possibly during its call). In general, we are tending towards
generic solutions targeting modifications on the generator side (at Step 1), rather than modifying
the AST or grammar sources by hand.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{The extraction of HOL constructors versus the extraction of HOL constants%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
The code generator of Isabelle generates in ML all
\isa{\isacommand{datatype}} constructors in a cartesian products form, while regular HOL
\isa{\isacommand{definition}} constants are extracted as curried. Since an interoperable
form is important for grammar composition in \csname isaDof.ref\endcsname[type={text}]{parser}; combining Haskabelle
with Citadelle~\cite{DBLP:journals/afp/TuongW15} in Step 1 allows for configuring Citadelle to
curry all constructors, based on Haskabelle's output. For example, the last two definitions are the
lines automatically added by Citadelle (for each \isa{\isacommand{datatype}} received
from Haskabelle):
\begin{gather*}
\begin{tabular}{lll}
\isa{datatype\ {\isacharprime}a\ CStatement} & \isa{{\isacharequal}} & \isa{CLabel{\isadigit{0}}\ Ident\ {\isachardoublequote}{\isacharprime}a\ CStatement{\isachardoublequote}\ {\isachardoublequote}{\isacharprime}a\ CAttributes{\isachardoublequote}\ {\isacharprime}a} \\
                         & \isa{{\isacharbar}} & \isa{CGoto{\isadigit{0}}\ Ident\ {\isacharprime}a} \\
\isa{definition\ {\isachardoublequote}CLabel}    & \isa{{\isacharequal}} & \isa{CLabel{\isadigit{0}}{\isachardoublequote}} \\
\isa{definition\ {\isachardoublequote}CGoto}    & \isa{{\isacharequal}} & \isa{CGoto{\isadigit{0}}{\isachardoublequote}}
\end{tabular}
\end{gather*}%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsubsection{Time to generate to SML%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
We conclude with Step 3 by using the Isabelle code generator. This takes about 20~min:
its generation time is depending in a major part on respective theorems generated by the
\isa{\isacommand{datatype}}-theory.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsubsection*}%
[label = {lexer},type = {scholarly_paper.technical}, args={label = {lexer},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Constructing a Lexer for C11%
\end{isamarkupsubsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
We decided against the option of importing the equivalent Haskell lexer, as it is
coming under-developed compared to the existing PIDE lexer library, natively
supporting Unicode-like symbols (mostly for annotations). Using a more expressive position
data-structure, our C lexer is also compatible with the native ML lexer regarding the handling of
errors and backtracking (hence the perfect fit when nesting one language inside the other). Overall,
the modifications essentially boil down to taking an extreme care of comments and directives which
have intricate lexical conventions (see \csname isaDof.ref\endcsname[type={text}]{lexer_ex}).%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsubsection*}%
[label = {parser},type = {scholarly_paper.technical}, args={label = {parser},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Generating the Shift-Reduce Parser from the Grammar%
\end{isamarkupsubsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
In the original C11 library, together with $\text{AST}_{\text{HS}}$, there is a Yacc
grammar file $\text{G}_{\text{HS-YACC}}$ included, which we intend to use to conduct the C
parsing. However due to technical limitations of Haskabelle (and advanced Haskell constructs in the
associated $\text{G}_{\text{HS}}$), we do not follow the same approach as \csname isaDof.ref\endcsname[type={text}]{arch1}. Instead, an ultimate grammar $\text{G}_{\text{ML}}$ is obtained by letting
ML-Yacc participate in the generation process. In a nutshell, the overall grammar translation chain
becomes: $\text{G}_{\text{HS-YACC}} \longrightarrow_{\text{HS}} \text{G}_{\text{ML-YACC}}
\longrightarrow_{\text{ML}} \text{G}_{\text{ML}}$.

$\longrightarrow_{\text{HS}}$ is implemented by modifying the Haskell parser generator Happy,
because Happy is already natively supporting the whole $\mathcal{L}_{\text{HS-YACC}}$. Due to the
close connection between Happy and ML-Yacc, the translation is even almost linear. However cares
must be taken while translating monadic rules of $\text{G}_{\text{HS-YACC}}$, as
$\mathcal{L}_{\text{ML-YACC}}$ does not support such rules. Indeed, rules of
$\mathcal{L}_{\text{HS-YACC}}$ can be either defined as being non-monadic (like
$\mathcal{L}_{\text{ML-YACC}}$), or set to explicitly perform a monadic action.\footnote{Syntactically, the difference relies in the presence of a particular flag before writing
  the rule code, namely \isatt{{\char`\%}}:
  \url{https://www.haskell.org/happy/doc/html/sec-monads.html}} In
$\text{G}^{\text{C11}}$, monadic rules are particularly important for scoping analyses, or while
building new informative AST nodes (in contrast to disambiguating non-monadic rules, see the
difference between \isa{{\isacharat}} and \isa{{\isacharampersand}} as used in
\csname isaDof.ref\endcsname[type={text}]{annotations}).\footnote{To add support of monadic rules in
  $\mathcal{L}_{\text{ML-YACC}}$, we adopt the same linguistic strategy as
  $\mathcal{L}_{\text{HS-YACC}}$: by letting the possibility to use a special string prefix in front
  of each rule code. Furthermore, to not modify the syntactic range of
  $\mathcal{L}_{\text{ML-YACC}}$, the string prefix can be directly written as
  \emph{annotated} in rule code, for instance under the form of a special ML comment
  \isatt{(*{\char`\%}*)}.} Note that $\longrightarrow_{\text{HS}}$ is also in charge of
translating each rule code from Haskell to ML.

After executing $\longrightarrow_{\text{HS}}$, we obtain $\text{G}_{\text{ML-YACC}}$, but applying
ML-Yacc $\longrightarrow_{\text{ML}}$ on $\text{G}_{\text{ML-YACC}}$ is not enough: even if the act
of getting an efficient Shift-Reduce automaton $\text{G}_{\text{ML}}$ is immediate, we needed to
substantially modify the own grammar interpreter of ML-Yacc to implement all features of
$\mathcal{L}_{\text{HS-YACC}}$ presented as used in $\text{G}_{\text{HS-YACC}}$.\footnote{For example, for the case of monadic rules, this means to implement the necessary monadic
  optimization in the grammar interpreter. Globally, the default behavior of ML-Yacc is still
  preserved, except that we implemented the monadic support in ML-Yacc by overriding how certain
  native commands of ML-Yacc were functioning: for example \isatt{{\char`\%}arg} is now
  used to denote an implicit monadic state, and \isatt{{\char`\%}pure} to explicitly
  trigger the generation of monadic code, see
  \url{https://www.cs.princeton.edu/~appel/modern/ml/ml-yacc/manual.html\#section12}.}
Besides the grammar interpreter of ML-Yacc, we also modified $\longrightarrow_{\text{ML}}$ to
generate additional meta-programming functions recording the types of all intermediate parsing
values that might be ever present in the parser stack, see \csname isaDof.ref\endcsname[type={text}]{annotations}. Later at parsing time, the necessary generated functions will be
called to perform automatic cast operations (in \csname isaDof.ref\endcsname[type={text}]{annot2}).%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsection*}%
[label = {ctests},type = {scholarly_paper.technical}, args={label = {ctests},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Isabelle/C: Syntax Tests and Experimental Results%
\end{isamarkupsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
The question arises, to what extent our construction provides a faithful parser for
C11, and if Isabelle/C is sufficiently stable and robust to handle real world sources. A related
question is the treatment of \isatt{cpp} preprocessing directives: while a
minimal definition of the preprocessor is part of C standards since C99, practical implementations
vary substantially.  Moreover, \isatt{cpp} comes close to be Turing complete:
recursive computations can be specified, but the expansion strategy bounds the number of
unfolding. Therefore, a complete \isatt{cpp} reimplementation contradicts our
objective to provide efficient IDE support inside Isabelle. Instead, we restrict ourselves to a
common subset of macro expansions and encourage, whenever possible, Isabelle specific mechanisms
such as user programmed C annotations. C sources depending critically on a specific
\isatt{cpp} will have to be processed outside
Isabelle.\footnote{Isabelle/C has a particular option to activate (or not) an automated
call to \isatt{cpp} before any in-depth treatment.}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsubsection*}%
[label = {lexer_ex},type = {scholarly_paper.technical}, args={label = {lexer_ex},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Preprocessing Lexical Conventions: Comments and Backslash Newlines%
\end{isamarkupsubsection*}\isamarkuptrue%
%
\begin{isamarkupfigure*}%
[label = {C-sample2},type = {Isa_COL.figure}, args={label = {C-sample2},type = {Isa_COL.figure}, Isa_COL.figure.relative_width = {42}, Isa_COL.figure.src = {figures/A-C-Source2}, Isa_COL.figure.spawn_columns = {True}}]Lexing convention for comments, illustrated in the CPP documentation%
\end{isamarkupfigure*}\isamarkuptrue%
%
\begin{isamarkuptext}%
A very basic standard example taken from the GCC / CPP documentation~\footnote{\url{https://gcc.gnu.org/onlinedocs/cpp/Initial-processing.html}}
in \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{C-sample2} shows the quite intricate mixing of comment styles that
represents a challenge for our C lexer. A further complication is that it is allowed and common
practice to use backslash-newlines \isa{{\isacharbackslash}{\isasymnewline}} \emph{anywhere} in C
sources, be it inside comments, string denotations, or even regular C keywords like
\isa{i{\isacharbackslash}{\isasymnewline}n{\isacharbackslash}{\isasymnewline}t} (see also \autoref{fig:clean}).

%% \begin{wrapfigure}{r}{0.42\textwidth}
%%   \vspace{-12pt}
%%   \includegraphics[width=0.42\textwidth]{figures/A-C-Source2}
%%   \vspace{-20pt}
%% \end{wrapfigure}
In fact, many C processing tools assume that all comments have already been removed via
\isatt{cpp} before they start any processing. However, annotations in comments carry relevant information 
for back-ends as shown in  \csname isaDof.ref\endcsname[type={text}]{annotations}. Consequently, they must be explicitly 
represented in $\text{AST}^{\text{C11}}_{\text{ML}}$,
whereas the initial $\text{AST}^{\text{C11}}_{\text{HS}}$ 
is not designed to carry such extra information. 
Annotations inside comments may again contain structured information like programming code, formulas,
and proofs, which implies the need for nested syntax. Fortunately, Isabelle is designed to
manage multiple parsing layers with the technique of \emph{cascade sources}~\footnote{\url{http://isabelle.in.tum.de/repos/isabelle/file/83774d669b51/src/Pure/General/source.ML}}
(see also \csname isaDof.ref\endcsname[type={text}]{C-sample3}). We exploit this infrastructure to integrate
back-end specific syntax and annotation semantics based on the parsing technologies available.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Preprocessing Side-Effects: Antiquoting Directives vs. Pure Annotations%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
For the mentioned reasons, we present how directives are classified and how some basic
support can be implemented. As directives and preprocessing constitute a major chapter in the C
standard, we only support very specific usages, but do not exclude statically typed alternatives to
directives via user-programmed antiquotations. Still, in comparison with
\emph{comments} which can be safely removed without affecting the meaning of C code,
\emph{directives} are semantically relevant for compilation and evaluation.

%
\begin{enumerate}%
\item Classical directives: \isa{{\isacharhash}define\ x\ TOKS} makes any incoming C identifier
\isa{x} be replaced by some \emph{arbitrary} tokens \isa{TOKS},
even when included via the \isa{{\isacharhash}include} directive.

\item Typed (pseudo-)directives as commands: It is easy to overload or implement a new
\isa{{\isacharhash}define{\isacharprime}} acting only on a decided subset of well-formed \isa{TOKS}. There
are actually no differences between Isabelle/C directives and Isabelle commands: both are
internally of type $\sigma \rightarrow \sigma$ (see \csname isaDof.ref\endcsname[type={text}]{background}).

\item Non-expanding annotations: Isabelle/C annotations
$\isa{{\isacharslash}{\isacharasterisk}{\isacharat}}~\mathcal{L}_\text{annot}~\isa{{\isacharasterisk}{\isacharslash}}$ or
$\isa{{\isacharslash}{\isacharslash}{\isacharat}}~\mathcal{L}_\text{annot}$ can be freely intertwined between other tokens, even
inside directives. In contrast to (antiquoting) directives and similarly as C comments, their
designed intent is to not modify the surrounding parsing code. In \csname isaDof.ref\endcsname[type={text}]{annotations}, we will address the issue of separation and interaction of
plugged-in annotations, as well as the possibility of nesting annotations.%
\end{enumerate}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
A limitation of Isabelle and its current document model is that there is no way for user
programmed extensions to exploit implicit dependencies between
sub-documents. Thus, a sub-document referred to via \isa{{\isacharhash}include\ {\isacharless}some{\isacharunderscore}file{\isachargreater}} will not
lead to a reevaluation of a \isa{\isacommand{C}{\isacartoucheopen}\ {\isachardot}{\isachardot}\ {\isacartoucheclose}} command whenever modified. (The only 
workaround is to open all transitively required sub-documents  \emph{by hand}.)%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsubsection*}%
[label = {parser_validation},type = {scholarly_paper.technical}, args={label = {parser_validation},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]A Validation via the seL4 Test Suite%
\end{isamarkupsubsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
The AutoCorres environment contains a C99 parser developed by Michael Norrish \cite{DBLP:conf/sosp/KleinEHACDEEKNSTW09}. Besides a parser test-suite, there is the entire seL4
codebase (written in C99) which has been used for the code verification part of the seL4
project. While the parser in itself represents a component belonging to the trusted base of the
environment, it is arguably the most tested parser for a semantically well-understood translation in
a proof environment today.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
It is therefore a valuable reference for a comparison test, especially since
$\text{AST}^\text{C99}$ and $\text{AST}^\text{C11}$ are available in the same implementation
language. From $\text{AST}^\text{C11}_{\text{HOL}}$ to $\text{AST}^\text{C99}_{\text{HOL}}$ we
construct an abstraction function $C^\downarrow$. Its definition is rather straightforward but
tedious and long: the main problem is the handling of C \isa{struct}s where some thoughts
have to be spent on the flattening of the recursive tree structure. A detailed description of
$C^\downarrow$ is out of the scope of this paper; we would like to mention that it was 4 man-months
of work due to the richness of $\text{AST}^\text{C11}$. This HOL function can be used for formal
proofs over a preserving subset translation; however, so far, we only use it for code reflection
into ML. As such, the abstraction function $C^\downarrow$ is at the heart of the AutoCorres
integration into our framework described in \csname isaDof.ref\endcsname[type={text}]{autocorres}. Note that
$\text{AST}^{\text{C99}}$ seems to be already an abstraction compared to the C99 standard. This
gives rise to a particular testing methodology: we can compile the test suites as well as the seL4
source files by both ML parsers $\text{PARSE}_{\text{\emph{stop}}}^{\text{C99}}$ and
$\text{PARSE}_{\text{\emph{report}}}^{\text{C11}}$, abstract the output of the latter via
$C^\downarrow$ and compare the results.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Our test establishes that both parsers agree on the entire seL4 codebase. However
trying to compare the two parsers using other criteria is not possible, for example we had to limit
ourselves to C programs written in a subset of C99. Fundamentally, the two parsers are achieving
different tasks: the one of $\text{PARSE}_{\text{\emph{stop}}}$ is to just return a parsed AST. In
contrast, $\text{PARSE}_{\text{\emph{report}}}$ intends to maximize markup reporting, irrespective
of a final parsing success or failure, and reports are provided in parallel during its (monadic)
parsing activity. Thus, in the former scenario, the full micro-kernel written in 26~kLoC can be
parsed in 0.1s. In the latter, all reports we have thought helpful to implement are totally rendered
before 20s. Applying $C^\downarrow$ takes 0.02 seconds, so our $\text{PARSE}_{\text{\emph{report}}}$
gives an average of 2s for a 2-3~kLoC source. By interweaving a source with proofs referring to the
code elements, the responsiveness of PIDE should therefore be largely sufficient. In principle,
there is an important potential for further optimizations by more incremental forms of reporting
that follow the current focus of a user window. However we adopted the same strategy of reporting as
\isa{\isacommand{ML}} and general Isabelle commands, for which incremental operations
seem to be limited inside the atomic level of a command.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsection*}%
[label = {annotations},type = {scholarly_paper.technical}, args={label = {annotations},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Generic Semantic Annotations for C%
\end{isamarkupsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
With respect to interaction with the underlying proof-engine, there are essentially two
lines of thought in the field of deductive verification techniques:

%
\begin{enumerate}%
\item either programs and specifications --- i.e. the pre- and post-condition contracts --- are clearly 
separated, or

\item the program is annotated with the specification, typically by using some form of formal
comment.%
\end{enumerate}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Of course, it is possible to inject the essence of annotated specifications directly
into proofs, e.g. by instantiating the \isa{while} rule of the Hoare calculus by the needed
invariant inside the proof script. The resulting clear separation of programs from proofs may be
required by organisational structures in development projects. However, in many cases, modelling
information may be interesting for programmers, too. Thus, having pre- and post-conditions locally
in the source close to its point of relevance increases its maintainability. It became therefore
common practice to design languages with annotations, i.e. structured comments
\emph{inside} a programming source. Examples are ACSL standardized by ANSI/ISO (see
\url{https://frama-c.com/download/acsl.pdf}) or UML/OCL \cite{DBLP:journals/afp/BruckerTW14} for static analysis tools. When tackling with concurrency \cite{DBLP:conf/tacas/SananZHZTL17}, other forms of annotation support are required, possibly in
assembly code included in C11 code.\footnote{See for example the Securify project:
  \url{http://securify.sce.ntu.edu.sg/}} Isabelle/C supports both the
inject-into-proof style and annotate-the-source style in its document model; while the former is
kind of the default, we address in this section the necessary technical infrastructure for the
latter.%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Binding Space of Annotation Environment%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkupfigure*}%
[label = {C-sample6},type = {Isa_COL.figure}, args={label = {C-sample6},type = {Isa_COL.figure}, Isa_COL.figure.relative_width = {56}, Isa_COL.figure.src = {figures/A-C-Source6}, Isa_COL.figure.spawn_columns = {True}}]C11 code enriched with HOL proofs%
\end{isamarkupfigure*}\isamarkuptrue%
%
\begin{isamarkuptext}%
Generally speaking, a generic annotation mechanism which is sufficiently expressive to
capture idioms used in, e.g., Frama-C, Why3, or VCC is more problematic than one might think.
Consider this:
\begin{isar}
     for (int i = 0; i < n; i++) a+= a*i /*@ annotation */
\end{isar}
To which part of the AST does the annotation refer? To \isa{i}? \isa{a{\isacharasterisk}i}? The
assignment? The loop? Some verification tools use prefix annotations (as in Why3 for procedure
contracts), others even a kind of parenthesis of the form:
\begin{isar}
     /*@ annotation_begin */ ...  /*@ annotation_end */
\end{isar}
The matter gets harder since the C environment --- a table mapping C identifiers to their type and
status --- changes according to the reference point in the AST. This means that the context relevant
to type-check an annotation such as \isa{{\isacharslash}{\isacharasterisk}{\isacharat}\ assert\ {\isasymopen}a\ {\isachargreater}\ i{\isasymclose}\ {\isacharasterisk}{\isacharslash}} strongly
differs depending on the annotation's position. And the matter gets even further complicated since
Isabelle/C lives inside a proof environment; here, local theory development (rather than bold ad-hoc
axiomatizations) is a major concern.

%% \begin{wrapfigure}{r}{0.56\textwidth}
%%   \vspace{-10pt}
%%   \includegraphics[width=0.56\textwidth]{figures/A-C-Source6}
%%   \vspace{-20pt}
%% \end{wrapfigure}
The desire for fast impact analysis resulting from changes may inspire one to annotate local proofs
near directives, which is actually what is implemented in our Isabelle/C/AutoCorres example
(\csname isaDof.ref\endcsname[type={text}]{backends}), and shown again in \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{C-sample6}. In the example, the semantic back-end converts the
\isatt{cpp} macro into a HOL \emph{definition}, i.e. an extension
of the underlying theory context by the conservative axiom
\isa{SQRT{\isacharunderscore}UINT{\isacharunderscore}MAX\ {\isasymequiv}\ {\isadigit{6}}{\isadigit{5}}{\isadigit{5}}{\isadigit{3}}{\isadigit{6}}{\isacharcolon}{\isacharcolon}{\isacharprime}a} bound to the name
\isa{SQRT{\isacharunderscore}UINT{\isacharunderscore}MAX{\isacharunderscore}def}. This information is used in the subsequent proof
establishing a new theory context containing the lemma \isa{uint{\isacharunderscore}max{\isacharunderscore}factor}
configured to be used as rewrite rule whenever possible in future proofs. This local lemma
establishes a relation of \isa{SQRT{\isacharunderscore}UINT{\isacharunderscore}MAX} to the maximally representable number
\isa{UINT{\isacharunderscore}MAX} for an unsigned integer according to the underlying memory model.

Obviously, the scheduling of these transformations of the underlying theory contexts is
non-trivial.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupfigure*}%
[label = {C-sample3},type = {Isa_COL.figure}, args={label = {C-sample3},type = {Isa_COL.figure}, Isa_COL.figure.relative_width = {100}, Isa_COL.figure.src = {figures/A-C-Source3}, Isa_COL.figure.spawn_columns = {True}}]Advanced annotation programming%
\end{isamarkupfigure*}\isamarkuptrue%
%
\begin{isamarkupsubsection*}%
[label = {navigation},type = {scholarly_paper.technical}, args={label = {navigation},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''bu''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Navigation for Annotation Commands%
\end{isamarkupsubsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
In order to overcome the problem of syntactic ambiguity of annotations, we slightly
refine the syntax of semantic annotations by the concept of a navigation expression:
\begin{isar}
    $\mathcal{L}_\text{annot}$ $=$ $\varnothing$ | <navigation-expr> <annotation-command> $\mathcal{L}_\text{annot}$ 
\end{isar}

A {\footnotesize\texttt{<navigation-expr>}} string consists of a sequence of \isa{{\isacharplus}} symbols followed
by a sequence consisting of \isa{{\isacharat}} or \isa{{\isacharampersand}} symbols. It allows for navigating
in the syntactic context, by advancing tokens with several \isa{{\isacharplus}}, or taking an ancestor
AST node with several \isa{{\isacharat}} (or \isa{{\isacharampersand}} which only targets monadic grammar rules). This
corresponds to a combination of right-movements in the AST, and respectively parent-movements. This
way, the ``focus'' of an {\footnotesize\texttt{<annotation-command>}} can be modified to denote any C
fragment of interest.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
As a relevant example for debugging, consider \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{C-sample3}.
The annotation command \isa{\isacommand{highlight}} is a predefined Isabelle/C ML-library function that is
interpreted as C annotation. Its code is implicitly parameterized by the syntactical context,
represented by \isatt{stack{\char`\_}top} whose type is a subset of
$\text{AST}^\text{C11}$, and the lexical environment \isatt{env} containing the
lexical class of identifiers, scopes, positions and serials for markup. The navigation string before
\isa{\isacommand{highlight}} particularly influences which
\isatt{stack{\char`\_}top} value gets ultimately selected. The third screenshot in \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{C-sample3} demonstrates the influence of the static environment: an Isabelle/C
predefined command \isa{\isacommand{{\isasymsimeq}setup}} allows for ``recursively'' calling the C
environment itself. This results in the export of definitions in the surrounding logical context,
where the propagation effect may be controlled with options like
\isa{C{\isacharunderscore}starting{\isacharunderscore}env}. \isa{\isacommand{{\isasymsimeq}setup}} actually
mimics standard Isabelle \isa{\isacommand{setup}} command, but extends it by
\isatt{stack{\char`\_}top} and \isatt{env} \footnote{cf. \url{https://isabelle.in.tum.de/doc/isar-ref.pdf}}. In the
example, the first recursive call uses \isatt{env} allowing it to detect that
\isa{b} is a local parameter, while the second ignores it which results in a treatment as a
free global variable. Note that bound global variables are not green but depicted in black.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsubsection*}%
[label = {annot1},type = {scholarly_paper.technical}, args={label = {annot1},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Defining Annotation Commands%
\end{isamarkupsubsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
Extending the default configuration of commands, text and code antiquotations from the
Isabelle platform to Isabelle/C is straightforward. For example, the central Isabelle command
definition:
\begin{isar}
    Outer_Syntax.command: $K_\text{\emph{cmd}}$ -> ($\sigma$ -> $\sigma$) parser -> unit
\end{isar}
establishes the dynamic binding between a command keyword $K_\text{\emph{cmd}} =
\isa{\isacommand{definition}} \isatt{|}
\isa{\isacommand{lemma}} \isatt{|} \dots $ and a parser, whose value is
a system transition on $\sigma$. The \isatt{parser} type stems from the
aforementioned parser combinator library: \isatt{{\char`\'}a\ parser}
\isatt{=} \isatt{Token.T\ list\ {\char`\-}{\char`\>}\ {\char`\'}a\ *\ Token.T\ list}.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Analogously, Isabelle/C provides an internal late-binding table for
\emph{annotation commands}:
\begin{isar}
    C_Annotation.command : $K_\text{\emph{cmd}}$ -> ($\text{<navigation-expr>}$ -> $R_\text{\emph{cmd}}$ c_parser) -> unit
    C_Annotation.command': $K_\text{\emph{cmd}}$ -> ($\text{<navigation-expr>}$ -> $R_\text{\emph{cmd}}$ c_parser) -> $\sigma$ -> $\sigma$
    C_Token.syntax': 'a parser -> 'a c_parser
\end{isar}
where in this paper we define $R_\text{\emph{cmd}} = \sigma~\isatt{{\char`\-}{\char`\>}}~\sigma$ as
above. It represents the registration of a chain of several consecutive actions.\footnote{In
  some parallel work, we focus on running commands in native efficient speed with
  $R_\text{\emph{cmd}} = \isatt{(} K_\text{\emph{cmd}} \isatt{*}
  \isatt{(}\sigma \isatt{{\char`\-}{\char`\>}} \sigma \isatt{)}
  \isatt{)} \isatt{list}$ \cite{DBLP:journals/afp/TuongW15}. Actually, $\sigma$ has the internal Isabelle type
  \isatt{Toplevel.transition}, and
  \isatt{Toplevel.transition\ {\char`\-}{\char`\>}\ Toplevel.transition} has nothing to do with a
  hypothetical composition of commands, but only with a characterization of the backtracking effect
  for erroneous (proof) commands. This is one reason why in this definition of
  $R_\text{\emph{cmd}}$, we used the type \isatt{list} to model a collection of
  elements. (Another reason is that the use of a functional type instead of a list seems to
  complicate the underlying scheduling implementation.) Note that for presentation purposes, we
  oversimplified the definition of $K_\text{\emph{cmd}}$. Normally, the smooth execution of a list
  of commands requires to know how to optimize a given command, for mostly future-delaying
  pure-computational (proofs) execution (even if a command can always launch several computing
  threads). Such information is ``encoded in its kind''; such as \isa{thy{\isacharunderscore}decl},
  \isa{thy{\isacharunderscore}load}, \isa{thy{\isacharunderscore}defn}, etc., for example: $K_\text{\emph{cmd}} =
  \isa{\isacommand{definition}\ {\isacharcolon}{\isacharcolon}\ thy{\isacharunderscore}defn} \isatt{|}
  \isa{\isacommand{lemma}\ {\isacharcolon}{\isacharcolon}\ thy{\isacharunderscore}goal{\isacharunderscore}stmt} \isatt{|} \dots $}

Since the type \isatt{c{\char`\_}parser} is isomorphic to \isatt{parser},
but accepting C tokens, one can use \isatt{C{\char`\_}Token.syntax{\char`\'}} to translate and carry
the default Isar commands \emph{inside} the \isa{\isacommand{C}{\isacartoucheopen}\ {\isachardot}{\isachardot}\ {\isacartoucheclose}} scope, such as \isa{\isacommand{lemma}} or
\isa{\isacommand{by}}. Using \isa{\isacommand{{\isasymsimeq}setup}}, one can even
define an annotation command \isa{\isacommand{C}} taking a C code as argument, as the ML
code of \isa{\isacommand{{\isasymsimeq}setup}} has type
$\alpha^{\text{AST}}~\isatt{{\char`\-}{\char`\>}\ env\ {\char`\-}{\char`\>}}~R_\text{\emph{cmd}}$ (which is enough for
calling \isatt{C{\char`\_}Annotation.command{\char`\'}} in the ML code). Here, whereas the type
\isatt{env} is always the same, the type $\alpha^{\text{AST}} \subseteq
\text{AST}^\text{C11}$ varies depending on {\footnotesize\texttt{<navigation-expr>}} (see \csname isaDof.ref\endcsname[type={text}]{annot2}).%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Note, however, that the user experience of the IDE changes when nesting commands too
deeply. In terms of error handling and failure treatment, there are some noteworthy implementation
differences between the outermost commands and C annotation commands. Naturally, the PIDE toplevel
has been optimized to maximize the error recovery and parallel execution. Inside a command, the
possibilities to mimic this behaviour are somewhat limited. Whereas the failure of an outermost
command must always be treated as an anomaly, in $\mathcal{L}_\text{annot}$, we are supposed to be
editing in a comment space: an error should be reported but not too much interruptive, because a
comment can contain for good reasons human narrative sentences. On the other hand, an error masking
itself shyly as warning can be overlooked easily, so a form of per-case compromise has to be found
to control the locally permissive set of errors. As a workaround useful during development and
debugging, we offer a further pragma for a global annotation, namely \isa{{\isacharasterisk}}
(in complement to the violet \isa{{\isacharat}}), that controls a switch between a
strict and a permissive error handling for nested annotation commands:
\begin{isar}
    <annotation-comment> $=$ // $[$ * $|$ @ $]^*$ $\mathcal{L}_\text{annot}$
    <annotation-comment> $=$ /* $[$ * $|$ @ $]^*$ $\mathcal{L}_\text{annot}$ */
\end{isar}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsubsection*}%
[label = {annot2},type = {scholarly_paper.technical}, args={label = {annot2},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Evaluation Order%
\end{isamarkupsubsection*}\isamarkuptrue%
%
\begin{isamarkupfigure*}%
[label = {C-sample5},type = {Isa_COL.figure}, args={label = {C-sample5},type = {Isa_COL.figure}, Isa_COL.figure.relative_width = {62}, Isa_COL.figure.src = {figures/A-C-Source5}, Isa_COL.figure.spawn_columns = {True}}]Creating and nesting C annotations: the importance of evaluation order in annotations%
\end{isamarkupfigure*}\isamarkuptrue%
%
\begin{isamarkuptext}%
We will now explain why positional languages are affecting the evaluation time of
annotation commands in \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{C-sample3}. This requires a little zoom on how the
parsing is actually executed.

The LALR parsing of our implemented C11 parser can be summarized as a sequence of alternations
between Shift and Reduce actions. By definition of LALR, whereas a unique Shift action is performed
for each C token read from left to right, some unlimited number of Reduce actions are happening
between two Shifts. Internally, the parser manages a stack-like data-structure called
$\alpha^{\text{AST}}$~\isatt{list} representing all already encountered Shift and
Reduce actions (SR). A given $\alpha^{\text{AST}}$~\isatt{list} can be seen as a
\emph{forest of SR nodes}: all leafs are tagged with a Shift, and any other parent
node is a Reduce node (see for example \csname isaDof.ref\endcsname[type={text}]{forest}). After a
certain point in the parsing history, the top stack element $\alpha^{\text{AST}}$ (cast with the
right type) is returned to \isa{\isacommand{{\isasymsimeq}setup}}.

Since a SR-forest is a list of SR-trees, it is possible to go forward and backward at will in the
actually unparsed SR-history, and execute a sequence of SR parsing steps only when needed. While
every annotation command like \isa{\isacommand{{\isasymsimeq}setup}} is by default attached to
a closest previous Shift leaf, navigation expressions modify the attached node, making the
presentation of $\alpha^{\text{AST}}$ referring to another term focus.

%% \begin{wrapfigure}{r}{0.62\textwidth}
%%   \vspace{-22pt}
%%   \begin{center}
%%     \includegraphics[width=0.62\textwidth]{figures/A-C-Source5}
%%   \end{center}
%%   \vspace{-20pt}
%% \end{wrapfigure}
Instead of visiting the AST in the default bottom-up direction during parsing, it is possible to
store the intermediate results, so that it can be revisited by using another direction strategy, for
example top-down after parsing (where a parent node is executed before any of its children, and
knows how they have been parsed thanks to $\alpha^{\text{AST}}$). This enables commands to decide if
they want to be executed during parsing, or after the full AST has been built. This gives rise to
the implementation of different versions of annotation commands that are executed at different
moments, relative to the parsing process. For example in \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{C-sample5}, the
annotation command \isa{\isacommand{{\isasymsimeq}setup}} has been defined for being executed
at bottom-up time, whereas the execution of the variant
\isa{\isacommand{{\isasymsimeq}setup{\isasymDown}}} happens at top-down time. In the above example,
\isa{\isacommand{C{\isadigit{1}}}} is a new command defined by \isatt{C{\char`\_}def}, a
shorthand antiquotation for \isatt{C{\char`\_}Annotation.command{\char`\'}}. Since
\isa{\isacommand{C{\isadigit{1}}}} is meant to be executed during bottom-up time (during parsing), it
is executed before \isa{\isacommand{C{\isadigit{2}}}} is defined (which is directly after parsing).

Note that the C11 grammar has enough scoping structure for the full inference of the C environment
\isatt{env} be at bottom-up time. In terms of efficiency, we use specific
\emph{static} rule wrappers having the potential of overloading default grammar rules (see \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{architecture}), to assign a wrapper to be always executed as soon as a Shift-Reduce
rule node of interest is encountered. The advantage of this construction is that the wrappers are
statically compiled, which results in a very efficient reporting of C type information.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsection*}%
[label = {backends},type = {scholarly_paper.technical}, args={label = {backends},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''bu''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Semantic Back-Ends%
\end{isamarkupsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
In this section, we briefly present two integrations of verification back-ends for C. We
chose Clean~\footnote{stemming from recent HOL-TestGen distributions
    \url{https://www.brucker.ch/projects/hol-testgen/index.en.html}} used
for program-based test generation \cite{DBLP:conf/tap/Keller18}, and AutoCorres \cite{DBLP:conf/pldi/GreenawayLAK14}, arguably the most developed deductive verification environment
for machine-oriented C available at present.

Note that we were focusing on keeping modifications of integrated components minimal, particularly
for the case of AutoCorres. Certain functionalities like position propagation of HOL terms in
annotations, or ``automatic'' incremental declarations~\footnote{\url{https://github.com/seL4/l4v/blob/master/tools/autocorres/tests/examples/Incremental.thy}}
may require internal revisions on the back-end side. This is out of the scope of this paper.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
\begin{figure}
  \centering
  \begin{minipage}{0.53\linewidth}
  \includegraphics[width=0.96\textwidth]{figures/A-C-Source7}
  \end{minipage}
  \begin{minipage}{0.45\linewidth}
\begin{isar}
prime$_{\text{C}}$_core_def: "prime$_{\text{C}}$_core n \<equiv>
  if$_{\text{Clean}}$ \<Open> (n < 2) \<Close> then return 0 else skip;-
  \<Open> i := 2 \<Close>;-
  while$_{\text{Clean}}$ \<Open> i < SQRT_UINT_MAX \<and> i * i \<le> n\<Close>
    (if$_{\text{Clean}}$ \<Open>n mod i = 0\<Close>
      then return 0 else skip;
     \<Open>k:=k+1\<Close>; assert \<Open> k\<le>UINT_MAX \<Close>
     \<Open>i:=i+1\<Close>; assert \<Open> i\<le>UINT_MAX \<Close>) ;-
  return 1"

prime$_{\text{C}}$_def: "prime$_{\text{C}}$ n \<equiv>
  block$_{\text{Clean}}$ push_local_prime$_{\text{C}}$_state
             (is_prime_core n)
             pop_local_prime$_{\text{C}}$_state"
\end{isar}
  \end{minipage}
  \caption{Activating the Isabelle/C/Clean back-end triggers the generation of theorems}
  \label{fig:clean}
\end{figure}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupfigure*}%
[label = {C-sample10},type = {Isa_COL.figure}, args={label = {C-sample10},type = {Isa_COL.figure}, Isa_COL.figure.relative_width = {40}, Isa_COL.figure.src = {figures/A-C-Source10}, Isa_COL.figure.spawn_columns = {True}}]Registering new C annotation commands%
\end{isamarkupfigure*}\isamarkuptrue%
%
\begin{isamarkuptext}%
%% \begin{wrapfigure}{r}{0.4\textwidth}
%%   \vspace{-14pt}
%%   \includegraphics[width=0.4\textwidth]{figures/A-C-Source10}
%% \end{wrapfigure}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsubsection*}%
[label = {autocorres},type = {scholarly_paper.technical}, args={label = {autocorres},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]The Case of AutoCorres%
\end{isamarkupsubsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
The AutoCorres environment consists of a C99 parser, compiling to a deepish embedding
of a generic imperative core programming language, over a refined machine word oriented memory
model, and a translator of this presentation into a shallow language based on another Monad for
non-deterministic computations. This translator has been described in \cite{DBLP:conf/pldi/GreenawayLAK14,DBLP:conf/tphol/WinwoodKSACN09} in detail. However, the
original use of AutoCorres implies a number of protocol rules to follow (e.g., calling the command
\isa{\isacommand{install{\isacharunderscore}C{\isacharunderscore}file}} before the command
\isa{\isacommand{autocorres}}), and is only loosely integrated into the Isabelle document
model, which complicates the workflow substantially.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
%% \begin{wrapfigure}{r}{0.48\textwidth}
\begin{figure}
  \centering
\begin{minipage}{0.48\textwidth}
%% \vspace{5pt}
\includegraphics[width=\textwidth]{figures/A-C-Source80}\vspace{-3pt}\hfill\allowbreak%
\vspace{0pt}$\quad\vdots$\vspace{2pt}\hfill\allowbreak%
\includegraphics[width=\textwidth]{figures/A-C-Source8}\vspace{-3pt}\hfill\allowbreak%
\vspace{0pt}$\quad\vdots$\vspace{2pt}\hfill\allowbreak%
\end{minipage}
  \caption{Isabelle/C/AutoCorres: integrating an HOL correctness proof near its C code}
  \label{fig:autocorres-c}
\end{figure}
%% \end{wrapfigure}
Our running example \isa{prime\isactrlsub C} for Isabelle/C/AutoCorres in \autoref{fig:autocorres-c} basically differs in what
the theory is importing in its header. Similarly to Clean, AutoCorres constructs a memory model and
represents the program as a monadic operation on it. Actually, it generates even two presentations,
one on a very precise word-level memory model taking aspects of the underlying processor
architecture into account, and another one more abstract, then it automatically proves the
correspondence in our concrete example. Both representations become the definitions
\isa{prime\isactrlsub C{\isacharunderscore}def} and \isa{prime\isactrlsub C{\isacharprime}{\isacharunderscore}def}. A Hoare-calculus plus
a derived verification generator \isa{wp} from the AutoCorres package
leverage finally the correctness proof.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Note that the integration of AutoCorres crucially depends on the conversion
$\text{AST}^\text{C11}~\isa{{\isasymRightarrow}}~\text{AST}^\text{C99}$ of $C^\downarrow$
discussed in \csname isaDof.ref\endcsname[type={text}]{parser_validation}. In particular, for the overall seL4
annotations
\isa{\isacommand{INVARIANT}},
\isa{\isacommand{INV}},
\isa{\isacommand{FNSPEC}},
\isa{\isacommand{RELSPEC}},
\isa{\isacommand{MODIFIES}},
\isa{\isacommand{DONT{\isacharunderscore}TRANSLATE}},
\isa{\isacommand{AUXUPD}},
\isa{\isacommand{GHOSTUPD}},
\isa{\isacommand{SPEC}},
\isa{\isacommand{END{\isacharminus}SPEC}},
\isa{\isacommand{CALLS}}, and
\isa{\isacommand{OWNED{\isacharunderscore}BY}},
we have extended our implementation of $C^\downarrow$ in such a way that the conversion places the
information at the right position in the target AST. Obviously, this works even when navigation is
used, as in \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{C-sample3} left.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsubsection*}%
[label = {securify},type = {scholarly_paper.technical}, args={label = {securify},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Yet another C-Back-End: Securify%
\end{isamarkupsubsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
In the Securify project at the Nanyang Technological University \cite{DBLP:conf/tacas/SananZHZTL17,DBLP:conf/itp/HouSTL17}, an extension of AutoCorres is in
active development which attempts to integrate concurrency and some form of non-coherent memory into
the verification framework. This ongoing project is already profiting from the overall framework,
including the integrated parser $\text{PARSE}_{\text{\emph{report}}}^{\text{C11}}$. Note, however,
that the XtratuM micro-kernel \cite{DBLP:journals/sigbed/CarrascosaCMBC14} in study is using
certain advance features of C11 not found in seL4 (including nested functions, or particular
arrangement of assembly code). The project is actively working on developing dedicated semantic
back-ends for respective features, to be separately or concurrently loaded with the AutoCorres one
presented in \csname isaDof.ref\endcsname[type={text}]{autocorres}.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsection*}%
[label = {concl},type = {scholarly_paper.conclusion}, args={label = {concl},type = {scholarly_paper.conclusion}, scholarly_paper.text_section.main_author = {@{docitem ''bu''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}}]Conclusions%
\end{isamarkupsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
We presented Isabelle/C a novel, generic front-end for a deep integration of C11 code into the 
Isabelle/PIDE framework. Based on open-source Lex and Yacc style grammars, we presented a build process 
that constructs key components for this front-end: the lexer, the parser, and a framework for 
user-defined annotations including user-defined annotation commands. 
While the generation process is relatively long, the generated complete library can be loaded in a 
few seconds constructing an environment similar to the usual \isa{\isacommand{ML}} environment for 
Isabelle itself. 20~kLoC large  C sources can be parsed and decorated in PIDE within  seconds.

Our framework allows for the deep integration of the C source into a global document model in which 
literate programming style documentation, modelling as well as static program analysis and verification 
co-exist.  In particular, information from the different tools realized as plugin in the Isabelle 
platform  can flow freely, but based on a clean management of their semantic context and within a 
framework based on conservative theory development. This substantially increases the development agility 
of such type of sources and may be  attractive to  conventional developers, in particular when 
targeting formal certification \cite{DBLP:conf/mkm/BruckerACW18}.

Isabelle/C also forms a basis for future semantically well-understood combinations of back-ends 
based on different semantic interpretations: inside Isabelle, bridge lemmas can be derived 
that describe the precise conditions under which results from one back-end can be re-interpreted
and used in another. Future tactic processes based on these bridge lemmas may open up novel ways 
for semantically safe tool combinations.%
\end{isamarkuptext}\isamarkuptrue%
%
\paragraph*{Acknowledgments.}
\begin{isamarkuptext}%
The authors warmly thank David Sanán and Yang Liu for encouraging the development and reuse of
$C^\downarrow$, initially started in the Securify project \cite{DBLP:conf/tacas/SananZHZTL17}
(\url{http://securify.sce.ntu.edu.sg/}).
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsection*}%
[label = {appendix},type = {scholarly_paper.technical}, args={label = {appendix},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Appendix%
\end{isamarkupsection*}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{Portability of Isabelle/C's Generated Files%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
To evaluate the portability of the generated files in \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{architecture}, we recall that:

%
\begin{itemize}%
\item the generation of $\text{AST}^{\text{C11}}$ depends on Haskabelle, Citadelle and the
Isabelle code generator,

\item and the generated $\text{G}_{\text{ML}}$ depends on the two respective ASTs of Happy and
ML-Yacc.%
\end{itemize}%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
As we assume the Isabelle code generator maintained by the Isabelle developers, and a
substantial part of Citadelle already maintained in the Isabelle AFP, the discussion remains on the
other tools used for generating $\text{AST}^{\text{C11}}$ and $\text{G}_{\text{ML}}$. For the case
of Happy and ML-Yacc, their own grammar languages have not significantly evolved in the last years,
and are still maintained in \url{https://github.com/simonmar/happy} and
\url{https://github.com/MLton/mlton}. For the case of Haskabelle, it has been
dropped from the Isabelle distribution, because it is critically relying on
haskell-src-exts~\url{http://hackage.haskell.org/package/haskell-src-exts}, and the
AST of haskell-src-exts received a drastic replacement from version 1.17.1 to 1.18.0.\footnote{See \url{http://hackage.haskell.org/package/haskell-src-exts-1.17.1} and
  \url{http://hackage.haskell.org/package/haskell-src-exts-1.18.0}. Actually, the
  default AST of haskell-src-exts was duplicated and enhanced in 2009 between 1.1.1 to 1.1.3 for a
  parsed source to carry additional position information in all its parsing nodes. Ultimately, the
  two ASTs was merged together while releasing version 1.18.0.} Upgrading Haskabelle to use
the new 1.18.0 was the most heavy task we performed, when integrating Haskabelle's output with
Citadelle's input. Otherwise, we have not encountered any problems in upgrading Haskabelle from
1.18.0 to more recent versions (such as 1.20.1 which was straightforward).%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsubsection{A Gentle Zoom on Citadelle's Generator%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In more details, combining Haskabelle and Citadelle is almost direct, as Haskabelle's
output AST and Citadelle's input AST are already both subsets models of a rich Isar/HOL interface,
defined in past works~\cite{DBLP:journals/afp/TuongW15}. Note that one can configure Citadelle
for it to generate $\text{AST}^\text{C11}_{\text{HOL}}$ using
\isa{\isacommand{old{\isacharunderscore}datatype}} commands instead of
\isa{\isacommand{datatype}}, in particular to gain 10~min on the shallow-reflected
evaluation side (with the option \isa{quick{\isacharminus}and{\isacharminus}dirty} activated). This is the purpose of
the general \isa{\isacommand{Haskell{\isacharunderscore}file}} command implemented in Citadelle:~\footnote{Note that \isa{\isacommand{old{\isacharunderscore}datatype}} is a command, whereas
  \isa{\isakeyword{datatype{\isacharunderscore}old}} is an option provided to the command
  \isa{\isacommand{Haskell{\isacharunderscore}file}}.}
\begin{gather*}
\begin{tabular}{ll}
\isa{\isacommand{Haskell{\isacharunderscore}file}} & \isa{\isakeyword{datatype{\isacharunderscore}old}\ \isakeyword{try{\isacharunderscore}import}\ \isakeyword{only{\isacharunderscore}types}\ \isakeyword{concat{\isacharunderscore}modules}} \\
                & \isa{\isakeyword{base{\isacharunderscore}path}\ {\isachardoublequoteopen}{\isachardollar}HASKABELLE{\isacharunderscore}HOME{\isacharslash}ex{\isacharslash}language{\isacharminus}c{\isacharslash}src{\isachardoublequoteclose}} \\
                & \isa{{\isacharbrackleft}Prelude\ {\isasymrightharpoonup}\ C{\isacharunderscore}Model{\isacharunderscore}init{\isacharcomma}\ Int{\isacharcomma}\ String{\isacharcomma}\ Option\ {\isasymrightharpoonup}\ C{\isacharunderscore}Model{\isacharunderscore}init{\isacharbrackright}} \\
                & \isa{} \\
                & \isa{{\isachardoublequoteopen}{\isachardollar}HASKABELLE{\isacharunderscore}HOME{\isacharslash}ex{\isacharslash}language{\isacharminus}c{\isacharslash}src{\isacharslash}Language{\isacharslash}C{\isacharslash}Syntax{\isacharslash}AST{\isachardot}hs{\isachardoublequoteclose}}
\end{tabular}
\end{gather*}

The advantage of this construction is the possibility to do immediate code value transformations
obtained from Haskabelle.

Operationally, \isa{\isacommand{Haskell{\isacharunderscore}file}} makes an implicit call to Haskabelle,
translates the Haskell's output of Haskabelle to an acceptable HOL input, and lets the Citadelle
framework execute generated theorems and proofs in native concurrent speed, based on a version of
Isabelle specially modified for the purpose.\footnote{The use of a modified Isabelle is very
  optional: Citadelle can also run with the standard Isabelle version, while being in the process of
  submitting to Isabelle AFP for example.} On the one hand, the measure performance of the
\isa{\isacommand{datatype}} package is not improving when being generated and executed by
our Citadelle infrastructure, because the blocking expensive point remains located on
\emph{one} problematic mutually recursive \isa{\isacommand{datatype}}
command (which is not interacting with other commands). On the other hand, the question
of: \begin{quote}\emph{``How fast that specific \isa{\isacommand{datatype}}
  command would perform if from the 20 mutually recursive sub-definitions it were instead generating
  20 or several (sub-)commands to be executed in native concurrent speed?''}\end{quote} is
  actually opening an interesting topic of future experiments.%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkupsubsection*}%
[label = {forest},type = {scholarly_paper.technical}, args={label = {forest},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Shift-Reduce forest of a parsing execution%
\end{isamarkupsubsection*}\isamarkuptrue%
%
\begin{isamarkuptext}%
By activating a specific option in Isabelle/C, one can dump the complete Shift-Reduce
forest of a parsing execution. For example, the SR-forest associated to the left sub-window of
\csname isaDof.ref\endcsname[type={Isa_COL.figure}]{C-sample3} is provided below:
\begin{isar}
REDUCE 0 X $\house$ $\house$ start_happy1  ( ( CTranslUnit, (CExtDecl, (CStat, (CExpr, unit) either) either) either )  either) 
 SHIFT $\house$ $\house$ 
 REDUCE 4 O $\house$ $\house$ translation_unit  (CTranslUnit) 
  REDUCE 7 X $\house$ $\house$ ext_decl_list3  ( ( CExtDecl list )  Reversed) 
   REDUCE 5 X $\house$ $\house$ ext_decl_list1  ( ( CExtDecl list )  Reversed) 
   REDUCE 8 X $\house$ $\house$ external_declaration1  (CExtDecl) 
    REDUCE 15 O $\house$ $\house$ function_definition4  (CFunDef) 
     REDUCE 127 X $\house$ $\house$ type_specifier1  (CDeclSpec list) 
      REDUCE 147 X $\house$ $\house$ basic_type_specifier1  ( ( CDeclSpec list )  Reversed) 
       REDUCE 133 O $\house$ $\house$ basic_type_name4  (CTypeSpec) 
        SHIFT $\house$ $\house$ 
     REDUCE 26 X $\house$ $\house$ function_declarator  (CDeclr) 
      REDUCE 260 X $\house$ $\house$ identifier_declarator1  (CDeclrR) 
       REDUCE 262 X $\house$ $\house$ unary_identifier_declarator1  (CDeclrR) 
        REDUCE 267 X $\house$ $\house$ postfix_identifier_declarator1  (CDeclrR) 
         REDUCE 272 O $\house$ $\house$ paren_identifier_declarator1  (CDeclrR) 
          SHIFT $\house$ $\house$ 
         REDUCE 312 O $\house$ $\house$ postfixing_abstract_declarator2  ( ( CDeclrR -> CDeclrR ) ) 
          SHIFT $\house$ $\house$ 
          REDUCE 283 X $\house$ $\house$ parameter_type_list2  ( ( CDecl list * Bool ) ) 
           REDUCE 285 X $\house$ $\house$ parameter_list1  ( ( CDecl list )  Reversed) 
            REDUCE 296 O $\house$ $\house$ parameter_declaration10  (CDecl) 
             REDUCE 127 X $\house$ $\house$ type_specifier1  (CDeclSpec list) 
              REDUCE 147 X $\house$ $\house$ basic_type_specifier1  ( ( CDeclSpec list )  Reversed) 
               REDUCE 133 O $\house$ $\house$ basic_type_name4  (CTypeSpec) 
                SHIFT $\house$ $\house$ 
             REDUCE 261 X $\house$ $\house$ identifier_declarator2  (CDeclrR) 
              REDUCE 272 O $\house$ $\house$ paren_identifier_declarator1  (CDeclrR) 
               SHIFT $\house$ $\house$ 
             REDUCE 471 X $\house$ $\house$ attrs_opt1  (CAttr list) 
          SHIFT $\house$ $\house$ 
     REDUCE 38 O $\house$ $\house$ compound_statement1  (CStat) 
      SHIFT $\house$ $\house$ 
      REDUCE 40 X $\house$ $\house$ enter_scope  (unit) 
      REDUCE 43 X $\house$ $\house$ block_item_list2  ( ( CBlockItem list )  Reversed) 
       REDUCE 43 X $\house$ $\house$ block_item_list2  ( ( CBlockItem list )  Reversed) 
        REDUCE 42 X $\house$ $\house$ block_item_list1  ( ( CBlockItem list )  Reversed) 
        REDUCE 44 X $\house$ $\house$ block_item1  (CBlockItem) 
         REDUCE 31 X $\house$ $\house$ statement5  (CStat) 
          REDUCE 61 O $\house$ $\house$ iteration_statement1  (CStat) 
           SHIFT $\house$ $\house$ 
           SHIFT $\house$ $\house$ 
           REDUCE 452 X $\house$ $\house$ expression1  (CExpr) 
            REDUCE 439 X $\house$ $\house$ assignment_expression1  (CExpr) 
             REDUCE 436 X $\house$ $\house$ conditional_expression1  (CExpr) 
              REDUCE 434 X $\house$ $\house$ logical_or_expression1  (CExpr) 
               REDUCE 432 X $\house$ $\house$ logical_and_expression1  (CExpr) 
                REDUCE 430 X $\house$ $\house$ inclusive_or_expression1  (CExpr) 
                 REDUCE 428 X $\house$ $\house$ exclusive_or_expression1  (CExpr) 
                  REDUCE 426 X $\house$ $\house$ and_expression1  (CExpr) 
                   REDUCE 423 X $\house$ $\house$ equality_expression1  (CExpr) 
                    REDUCE 419 O $\house$ $\house$ relational_expression2  (CExpr) 
                     REDUCE 418 X $\house$ $\house$ relational_expression1  (CExpr) 
                      REDUCE 415 X $\house$ $\house$ shift_expression1  (CExpr) 
                       REDUCE 412 X $\house$ $\house$ additive_expression1  (CExpr) 
                        REDUCE 408 X $\house$ $\house$ multiplicative_expression1  (CExpr) 
                         REDUCE 406 X $\house$ $\house$ cast_expression1  (CExpr) 
                          REDUCE 388 X $\house$ $\house$ unary_expression1  (CExpr) 
                           REDUCE 376 X $\house$ $\house$ postfix_expression1  (CExpr) 
                            REDUCE 360 O $\house$ $\house$ primary_expression1  (CExpr) 
                             SHIFT $\house$ $\house$ 
                     SHIFT $\house$ $\house$ 
                     REDUCE 415 X $\house$ $\house$ shift_expression1  (CExpr) 
                      REDUCE 412 X $\house$ $\house$ additive_expression1  (CExpr) 
                       REDUCE 408 X $\house$ $\house$ multiplicative_expression1  (CExpr) 
                        REDUCE 406 X $\house$ $\house$ cast_expression1  (CExpr) 
                         REDUCE 388 X $\house$ $\house$ unary_expression1  (CExpr) 
                          REDUCE 376 X $\house$ $\house$ postfix_expression1  (CExpr) 
                           REDUCE 361 X $\house$ $\house$ primary_expression2  (CExpr) 
                            REDUCE 461 O $\house$ $\house$ constant1  (CConst) 
                             SHIFT $\house$ $\house$ 
           SHIFT $\house$ $\house$ 
           REDUCE 28 X $\house$ $\house$ statement2  (CStat) 
            REDUCE 38 O $\house$ $\house$ compound_statement1  (CStat) 
             SHIFT $\house$ $\house$ 
             REDUCE 40 X $\house$ $\house$ enter_scope  (unit) 
             REDUCE 43 X $\house$ $\house$ block_item_list2  ( ( CBlockItem list )  Reversed) 
              REDUCE 42 X $\house$ $\house$ block_item_list1  ( ( CBlockItem list )  Reversed) 
              REDUCE 44 X $\house$ $\house$ block_item1  (CBlockItem) 
               REDUCE 29 X $\house$ $\house$ statement3  (CStat) 
                REDUCE 57 O $\house$ $\house$ expression_statement2  (CStat) 
                 REDUCE 452 X $\house$ $\house$ expression1  (CExpr) 
                  REDUCE 440 O $\house$ $\house$ assignment_expression2  (CExpr) 
                   REDUCE 388 X $\house$ $\house$ unary_expression1  (CExpr) 
                    REDUCE 376 X $\house$ $\house$ postfix_expression1  (CExpr) 
                     REDUCE 360 O $\house$ $\house$ primary_expression1  (CExpr) 
                      SHIFT $\house$ $\house$ 
                   REDUCE 441 O $\house$ $\house$ assignment_operator1  (CAssignOp Located) 
                    SHIFT $\house$ $\house$ 
                   REDUCE 439 X $\house$ $\house$ assignment_expression1  (CExpr) 
                    REDUCE 436 X $\house$ $\house$ conditional_expression1  (CExpr) 
                     REDUCE 434 X $\house$ $\house$ logical_or_expression1  (CExpr) 
                      REDUCE 432 X $\house$ $\house$ logical_and_expression1  (CExpr) 
                       REDUCE 430 X $\house$ $\house$ inclusive_or_expression1  (CExpr) 
                        REDUCE 428 X $\house$ $\house$ exclusive_or_expression1  (CExpr) 
                         REDUCE 426 X $\house$ $\house$ and_expression1  (CExpr) 
                          REDUCE 423 X $\house$ $\house$ equality_expression1  (CExpr) 
                           REDUCE 418 X $\house$ $\house$ relational_expression1  (CExpr) 
                            REDUCE 415 X $\house$ $\house$ shift_expression1  (CExpr) 
                             REDUCE 413 O $\house$ $\house$ additive_expression2  (CExpr) 
                              REDUCE 412 X $\house$ $\house$ additive_expression1  (CExpr) 
                               REDUCE 408 X $\house$ $\house$ multiplicative_expression1  (CExpr) 
                                REDUCE 406 X $\house$ $\house$ cast_expression1  (CExpr) 
                                 REDUCE 388 X $\house$ $\house$ unary_expression1  (CExpr) 
                                  REDUCE 376 X $\house$ $\house$ postfix_expression1  (CExpr) 
                                   REDUCE 360 O $\house$ $\house$ primary_expression1  (CExpr) 
                                    SHIFT $\house$ $\house$ 
                              SHIFT $\house$ $\house$ 
                              REDUCE 408 X $\house$ $\house$ multiplicative_expression1  (CExpr) 
                               REDUCE 406 X $\house$ $\house$ cast_expression1  (CExpr) 
                                REDUCE 388 X $\house$ $\house$ unary_expression1  (CExpr) 
                                 REDUCE 376 X $\house$ $\house$ postfix_expression1  (CExpr) 
                                  REDUCE 361 X $\house$ $\house$ primary_expression2  (CExpr) 
                                   REDUCE 461 O $\house$ $\house$ constant1  (CConst) 
                                    SHIFT $\house$ $\house$ 
                 SHIFT $\house$ $\house$ 
             REDUCE 41 X $\house$ $\house$ leave_scope  (unit) 
             SHIFT $\house$ $\house$ 
       REDUCE 44 X $\house$ $\house$ block_item1  (CBlockItem) 
        REDUCE 32 X $\house$ $\house$ statement6  (CStat) 
         REDUCE 69 O $\house$ $\house$ jump_statement5  (CStat) 
          SHIFT $\house$ $\house$ 
          REDUCE 457 X $\house$ $\house$ expression_opt2  (CExpr Maybe) 
           REDUCE 452 X $\house$ $\house$ expression1  (CExpr) 
            REDUCE 439 X $\house$ $\house$ assignment_expression1  (CExpr) 
             REDUCE 436 X $\house$ $\house$ conditional_expression1  (CExpr) 
              REDUCE 434 X $\house$ $\house$ logical_or_expression1  (CExpr) 
               REDUCE 432 X $\house$ $\house$ logical_and_expression1  (CExpr) 
                REDUCE 430 X $\house$ $\house$ inclusive_or_expression1  (CExpr) 
                 REDUCE 428 X $\house$ $\house$ exclusive_or_expression1  (CExpr) 
                  REDUCE 426 X $\house$ $\house$ and_expression1  (CExpr) 
                   REDUCE 423 X $\house$ $\house$ equality_expression1  (CExpr) 
                    REDUCE 418 X $\house$ $\house$ relational_expression1  (CExpr) 
                     REDUCE 415 X $\house$ $\house$ shift_expression1  (CExpr) 
                      REDUCE 412 X $\house$ $\house$ additive_expression1  (CExpr) 
                       REDUCE 408 X $\house$ $\house$ multiplicative_expression1  (CExpr) 
                        REDUCE 406 X $\house$ $\house$ cast_expression1  (CExpr) 
                         REDUCE 388 X $\house$ $\house$ unary_expression1  (CExpr) 
                          REDUCE 376 X $\house$ $\house$ postfix_expression1  (CExpr) 
                           REDUCE 360 O $\house$ $\house$ primary_expression1  (CExpr) 
                            SHIFT $\house$ $\house$ 
          SHIFT $\house$ $\house$ 
      REDUCE 41 X $\house$ $\house$ leave_scope  (unit) 
      SHIFT $\house$ $\house$ 
VOID  
\end{isar}%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%32=54%:%
%:%36=61%:%
%:%40=67%:%
%:%41=68%:%
%:%42=69%:%
%:%43=70%:%
%:%44=71%:%
%:%45=72%:%
%:%46=73%:%
%:%47=74%:%
%:%48=75%:%
%:%49=76%:%
%:%50=77%:%
%:%51=78%:%
%:%52=79%:%
%:%53=80%:%
%:%54=81%:%
%:%55=82%:%
%:%56=83%:%
%:%57=84%:%
%:%58=85%:%
%:%62=88%:%
%:%66=90%:%
%:%67=91%:%
%:%68=92%:%
%:%69=93%:%
%:%70=94%:%
%:%71=95%:%
%:%72=96%:%
%:%73=97%:%
%:%74=98%:%
%:%75=99%:%
%:%76=100%:%
%:%77=101%:%
%:%78=102%:%
%:%79=103%:%
%:%80=104%:%
%:%81=105%:%
%:%82=106%:%
%:%83=107%:%
%:%84=108%:%
%:%85=109%:%
%:%86=110%:%
%:%87=111%:%
%:%88=112%:%
%:%89=113%:%
%:%90=114%:%
%:%91=115%:%
%:%92=116%:%
%:%93=117%:%
%:%94=118%:%
%:%95=119%:%
%:%96=120%:%
%:%97=121%:%
%:%98=122%:%
%:%99=123%:%
%:%100=124%:%
%:%101=125%:%
%:%102=126%:%
%:%103=127%:%
%:%104=128%:%
%:%105=129%:%
%:%109=147%:%
%:%113=149%:%
%:%114=150%:%
%:%115=151%:%
%:%116=152%:%
%:%117=153%:%
%:%118=154%:%
%:%119=155%:%
%:%120=156%:%
%:%121=157%:%
%:%122=158%:%
%:%126=169%:%
%:%127=170%:%
%:%128=171%:%
%:%129=172%:%
%:%130=173%:%
%:%131=174%:%
%:%132=175%:%
%:%133=176%:%
%:%137=179%:%
%:%141=181%:%
%:%142=182%:%
%:%143=183%:%
%:%144=184%:%
%:%145=185%:%
%:%146=186%:%
%:%147=187%:%
%:%148=188%:%
%:%149=189%:%
%:%153=193%:%
%:%157=196%:%
%:%161=200%:%
%:%162=201%:%
%:%163=202%:%
%:%164=203%:%
%:%165=204%:%
%:%166=205%:%
%:%167=206%:%
%:%168=207%:%
%:%169=208%:%
%:%170=209%:%
%:%171=210%:%
%:%172=211%:%
%:%173=212%:%
%:%174=213%:%
%:%175=214%:%
%:%176=215%:%
%:%177=216%:%
%:%178=217%:%
%:%179=218%:%
%:%180=219%:%
%:%189=221%:%
%:%201=223%:%
%:%202=224%:%
%:%203=225%:%
%:%204=226%:%
%:%205=227%:%
%:%206=228%:%
%:%207=229%:%
%:%208=230%:%
%:%209=231%:%
%:%210=232%:%
%:%211=233%:%
%:%212=234%:%
%:%213=235%:%
%:%214=236%:%
%:%215=237%:%
%:%216=238%:%
%:%217=239%:%
%:%218=240%:%
%:%219=241%:%
%:%220=242%:%
%:%221=243%:%
%:%222=244%:%
%:%223=245%:%
%:%224=246%:%
%:%225=247%:%
%:%226=248%:%
%:%227=249%:%
%:%228=250%:%
%:%229=251%:%
%:%230=252%:%
%:%231=253%:%
%:%232=254%:%
%:%233=255%:%
%:%234=256%:%
%:%235=257%:%
%:%236=258%:%
%:%237=259%:%
%:%238=260%:%
%:%239=261%:%
%:%240=262%:%
%:%241=263%:%
%:%242=264%:%
%:%243=265%:%
%:%244=266%:%
%:%245=267%:%
%:%246=268%:%
%:%247=269%:%
%:%248=270%:%
%:%249=271%:%
%:%250=272%:%
%:%251=273%:%
%:%252=274%:%
%:%253=275%:%
%:%254=276%:%
%:%254=277%:%
%:%255=278%:%
%:%256=279%:%
%:%257=280%:%
%:%258=281%:%
%:%259=282%:%
%:%260=283%:%
%:%261=284%:%
%:%262=285%:%
%:%263=286%:%
%:%272=291%:%
%:%284=294%:%
%:%285=295%:%
%:%286=296%:%
%:%287=297%:%
%:%288=298%:%
%:%289=299%:%
%:%290=300%:%
%:%291=301%:%
%:%292=302%:%
%:%293=303%:%
%:%294=304%:%
%:%295=305%:%
%:%296=306%:%
%:%297=307%:%
%:%298=308%:%
%:%299=309%:%
%:%300=310%:%
%:%301=311%:%
%:%302=312%:%
%:%303=313%:%
%:%304=314%:%
%:%305=315%:%
%:%306=316%:%
%:%307=317%:%
%:%311=320%:%
%:%315=323%:%
%:%316=324%:%
%:%317=325%:%
%:%318=326%:%
%:%319=327%:%
%:%320=328%:%
%:%321=329%:%
%:%322=330%:%
%:%323=331%:%
%:%324=332%:%
%:%325=333%:%
%:%326=334%:%
%:%327=335%:%
%:%328=336%:%
%:%329=337%:%
%:%330=338%:%
%:%331=339%:%
%:%332=340%:%
%:%333=341%:%
%:%334=342%:%
%:%335=343%:%
%:%339=347%:%
%:%343=363%:%
%:%347=364%:%
%:%348=365%:%
%:%350=366%:%
%:%351=367%:%
%:%356=370%:%
%:%357=371%:%
%:%358=372%:%
%:%359=373%:%
%:%360=374%:%
%:%361=375%:%
%:%365=377%:%
%:%366=378%:%
%:%367=379%:%
%:%368=380%:%
%:%369=381%:%
%:%370=382%:%
%:%371=383%:%
%:%372=384%:%
%:%373=385%:%
%:%374=386%:%
%:%375=387%:%
%:%379=390%:%
%:%380=391%:%
%:%381=392%:%
%:%382=393%:%
%:%383=394%:%
%:%387=397%:%
%:%391=399%:%
%:%392=400%:%
%:%393=401%:%
%:%394=402%:%
%:%395=403%:%
%:%399=432%:%
%:%403=433%:%
%:%404=434%:%
%:%405=435%:%
%:%406=436%:%
%:%407=437%:%
%:%408=438%:%
%:%412=440%:%
%:%413=441%:%
%:%414=442%:%
%:%415=443%:%
%:%416=444%:%
%:%420=445%:%
%:%421=446%:%
%:%423=447%:%
%:%424=448%:%
%:%426=449%:%
%:%431=456%:%
%:%432=457%:%
%:%433=458%:%
%:%433=459%:%
%:%434=460%:%
%:%435=461%:%
%:%436=462%:%
%:%437=463%:%
%:%438=464%:%
%:%439=465%:%
%:%440=466%:%
%:%449=468%:%
%:%461=470%:%
%:%462=471%:%
%:%463=472%:%
%:%464=473%:%
%:%465=474%:%
%:%466=475%:%
%:%467=476%:%
%:%468=477%:%
%:%469=478%:%
%:%469=479%:%
%:%470=480%:%
%:%471=481%:%
%:%472=482%:%
%:%473=483%:%
%:%474=484%:%
%:%483=486%:%
%:%495=488%:%
%:%496=489%:%
%:%497=490%:%
%:%498=491%:%
%:%499=492%:%
%:%500=493%:%
%:%501=494%:%
%:%510=496%:%
%:%522=498%:%
%:%523=499%:%
%:%524=500%:%
%:%525=501%:%
%:%526=502%:%
%:%527=503%:%
%:%528=504%:%
%:%529=505%:%
%:%530=506%:%
%:%531=507%:%
%:%532=508%:%
%:%533=509%:%
%:%534=510%:%
%:%535=511%:%
%:%536=512%:%
%:%537=513%:%
%:%538=514%:%
%:%539=515%:%
%:%540=516%:%
%:%541=517%:%
%:%550=524%:%
%:%562=530%:%
%:%563=531%:%
%:%564=532%:%
%:%565=533%:%
%:%566=534%:%
%:%567=535%:%
%:%568=536%:%
%:%569=537%:%
%:%570=538%:%
%:%571=539%:%
%:%572=540%:%
%:%573=541%:%
%:%574=542%:%
%:%575=543%:%
%:%576=544%:%
%:%577=545%:%
%:%586=558%:%
%:%598=560%:%
%:%599=561%:%
%:%600=562%:%
%:%604=568%:%
%:%608=570%:%
%:%609=571%:%
%:%610=572%:%
%:%611=573%:%
%:%612=574%:%
%:%613=575%:%
%:%614=576%:%
%:%618=579%:%
%:%622=585%:%
%:%623=586%:%
%:%624=587%:%
%:%625=588%:%
%:%625=589%:%
%:%626=590%:%
%:%627=591%:%
%:%628=592%:%
%:%629=593%:%
%:%630=594%:%
%:%631=595%:%
%:%632=596%:%
%:%633=597%:%
%:%634=598%:%
%:%635=599%:%
%:%636=600%:%
%:%636=601%:%
%:%637=602%:%
%:%638=603%:%
%:%639=604%:%
%:%640=605%:%
%:%641=606%:%
%:%642=607%:%
%:%643=608%:%
%:%644=609%:%
%:%645=610%:%
%:%646=611%:%
%:%647=612%:%
%:%648=613%:%
%:%649=614%:%
%:%650=615%:%
%:%651=616%:%
%:%652=617%:%
%:%653=618%:%
%:%654=619%:%
%:%655=620%:%
%:%655=621%:%
%:%656=622%:%
%:%657=623%:%
%:%658=624%:%
%:%659=625%:%
%:%660=626%:%
%:%661=627%:%
%:%662=628%:%
%:%663=629%:%
%:%664=630%:%
%:%664=631%:%
%:%665=632%:%
%:%669=636%:%
%:%673=638%:%
%:%674=639%:%
%:%675=640%:%
%:%676=641%:%
%:%677=642%:%
%:%678=643%:%
%:%679=644%:%
%:%680=645%:%
%:%681=646%:%
%:%682=647%:%
%:%683=648%:%
%:%684=649%:%
%:%685=650%:%
%:%689=652%:%
%:%693=659%:%
%:%697=661%:%
%:%697=662%:%
%:%698=663%:%
%:%699=664%:%
%:%700=665%:%
%:%701=666%:%
%:%702=667%:%
%:%703=668%:%
%:%704=669%:%
%:%705=670%:%
%:%706=671%:%
%:%707=672%:%
%:%708=673%:%
%:%709=674%:%
%:%710=675%:%
%:%711=676%:%
%:%712=677%:%
%:%713=678%:%
%:%714=679%:%
%:%715=680%:%
%:%716=681%:%
%:%717=682%:%
%:%717=683%:%
%:%718=684%:%
%:%719=685%:%
%:%728=687%:%
%:%740=689%:%
%:%741=690%:%
%:%742=691%:%
%:%743=692%:%
%:%744=693%:%
%:%745=694%:%
%:%749=696%:%
%:%750=697%:%
%:%751=698%:%
%:%753=700%:%
%:%754=701%:%
%:%755=702%:%
%:%756=703%:%
%:%758=705%:%
%:%759=706%:%
%:%760=707%:%
%:%761=708%:%
%:%762=709%:%
%:%762=710%:%
%:%763=711%:%
%:%768=715%:%
%:%769=716%:%
%:%770=717%:%
%:%771=718%:%
%:%772=719%:%
%:%776=765%:%
%:%780=767%:%
%:%780=768%:%
%:%781=769%:%
%:%782=770%:%
%:%783=771%:%
%:%784=772%:%
%:%788=774%:%
%:%789=775%:%
%:%790=776%:%
%:%791=777%:%
%:%792=778%:%
%:%793=779%:%
%:%794=780%:%
%:%795=781%:%
%:%796=782%:%
%:%797=783%:%
%:%798=784%:%
%:%799=785%:%
%:%800=786%:%
%:%801=787%:%
%:%802=788%:%
%:%803=789%:%
%:%807=791%:%
%:%808=792%:%
%:%809=793%:%
%:%810=794%:%
%:%811=795%:%
%:%812=796%:%
%:%813=797%:%
%:%814=798%:%
%:%815=799%:%
%:%816=800%:%
%:%817=801%:%
%:%818=802%:%
%:%819=803%:%
%:%820=804%:%
%:%821=805%:%
%:%825=815%:%
%:%829=817%:%
%:%830=818%:%
%:%834=819%:%
%:%835=820%:%
%:%837=821%:%
%:%838=822%:%
%:%843=824%:%
%:%844=825%:%
%:%845=826%:%
%:%846=827%:%
%:%847=828%:%
%:%848=829%:%
%:%849=830%:%
%:%850=831%:%
%:%851=832%:%
%:%851=833%:%
%:%851=834%:%
%:%852=835%:%
%:%853=836%:%
%:%854=837%:%
%:%855=838%:%
%:%856=839%:%
%:%865=841%:%
%:%877=845%:%
%:%881=847%:%
%:%882=848%:%
%:%883=849%:%
%:%884=850%:%
%:%885=851%:%
%:%886=852%:%
%:%887=853%:%
%:%888=854%:%
%:%889=855%:%
%:%890=856%:%
%:%891=857%:%
%:%892=858%:%
%:%893=859%:%
%:%894=860%:%
%:%895=861%:%
%:%896=862%:%
%:%897=863%:%
%:%898=864%:%
%:%899=865%:%
%:%900=866%:%
%:%901=867%:%
%:%902=868%:%
%:%903=869%:%
%:%904=870%:%
%:%905=871%:%
%:%906=872%:%
%:%907=873%:%
%:%907=874%:%
%:%908=875%:%
%:%909=876%:%
%:%910=877%:%
%:%911=878%:%
%:%912=879%:%
%:%913=880%:%
%:%914=881%:%
%:%915=882%:%
%:%916=883%:%
%:%917=884%:%
%:%918=885%:%
%:%922=888%:%
%:%926=891%:%
%:%930=893%:%
%:%931=894%:%
%:%932=895%:%
%:%933=896%:%
%:%934=897%:%
%:%935=898%:%
%:%936=899%:%
%:%937=900%:%
%:%938=901%:%
%:%939=902%:%
%:%940=903%:%
%:%941=904%:%
%:%942=905%:%
%:%946=907%:%
%:%947=908%:%
%:%948=909%:%
%:%949=910%:%
%:%950=911%:%
%:%951=912%:%
%:%952=913%:%
%:%953=914%:%
%:%953=915%:%
%:%954=916%:%
%:%955=917%:%
%:%956=918%:%
%:%957=919%:%
%:%958=920%:%
%:%959=921%:%
%:%959=922%:%
%:%960=923%:%
%:%961=924%:%
%:%962=925%:%
%:%966=928%:%
%:%970=930%:%
%:%971=931%:%
%:%972=932%:%
%:%973=933%:%
%:%974=934%:%
%:%975=935%:%
%:%976=936%:%
%:%977=937%:%
%:%978=938%:%
%:%979=939%:%
%:%980=940%:%
%:%981=941%:%
%:%985=943%:%
%:%986=944%:%
%:%987=945%:%
%:%988=946%:%
%:%989=947%:%
%:%990=948%:%
%:%991=949%:%
%:%992=950%:%
%:%993=951%:%
%:%994=952%:%
%:%995=953%:%
%:%996=954%:%
%:%997=955%:%
%:%997=956%:%
%:%998=957%:%
%:%999=958%:%
%:%1000=959%:%
%:%1001=960%:%
%:%1002=961%:%
%:%1003=962%:%
%:%1004=963%:%
%:%1005=964%:%
%:%1006=965%:%
%:%1007=966%:%
%:%1008=967%:%
%:%1009=968%:%
%:%1010=969%:%
%:%1011=970%:%
%:%1012=971%:%
%:%1013=972%:%
%:%1014=973%:%
%:%1015=974%:%
%:%1015=975%:%
%:%1016=976%:%
%:%1017=977%:%
%:%1018=978%:%
%:%1019=979%:%
%:%1020=980%:%
%:%1021=981%:%
%:%1022=982%:%
%:%1022=983%:%
%:%1026=985%:%
%:%1027=986%:%
%:%1028=987%:%
%:%1029=988%:%
%:%1030=989%:%
%:%1031=990%:%
%:%1032=991%:%
%:%1033=992%:%
%:%1034=993%:%
%:%1035=994%:%
%:%1036=995%:%
%:%1037=996%:%
%:%1038=997%:%
%:%1039=998%:%
%:%1040=999%:%
%:%1041=1000%:%
%:%1042=1001%:%
%:%1046=1005%:%
%:%1050=1009%:%
%:%1054=1015%:%
%:%1055=1016%:%
%:%1056=1017%:%
%:%1057=1018%:%
%:%1058=1019%:%
%:%1059=1020%:%
%:%1060=1021%:%
%:%1061=1022%:%
%:%1062=1023%:%
%:%1063=1024%:%
%:%1064=1025%:%
%:%1065=1026%:%
%:%1066=1027%:%
%:%1067=1028%:%
%:%1068=1029%:%
%:%1069=1030%:%
%:%1070=1031%:%
%:%1071=1032%:%
%:%1072=1033%:%
%:%1073=1034%:%
%:%1074=1035%:%
%:%1075=1036%:%
%:%1076=1037%:%
%:%1077=1038%:%
%:%1078=1039%:%
%:%1079=1040%:%
%:%1080=1041%:%
%:%1081=1042%:%
%:%1082=1043%:%
%:%1083=1044%:%
%:%1084=1045%:%
%:%1085=1046%:%
%:%1086=1047%:%
%:%1087=1048%:%
%:%1088=1049%:%
%:%1089=1050%:%
%:%1090=1051%:%
%:%1091=1052%:%
%:%1092=1053%:%
%:%1093=1054%:%
%:%1094=1055%:%
%:%1095=1056%:%
%:%1096=1057%:%
%:%1097=1058%:%
%:%1098=1059%:%
%:%1099=1060%:%
%:%1099=1061%:%
%:%1100=1062%:%
%:%1101=1063%:%
%:%1105=1092%:%
%:%1109=1093%:%
%:%1110=1094%:%
%:%1111=1095%:%
%:%1112=1096%:%
%:%1112=1097%:%
%:%1113=1098%:%
%:%1114=1099%:%
%:%1115=1100%:%
%:%1116=1101%:%
%:%1117=1102%:%
%:%1117=1103%:%
%:%1118=1104%:%
%:%1122=1108%:%
%:%1123=1109%:%
%:%1124=1110%:%
%:%1125=1111%:%
%:%1126=1112%:%
%:%1127=1113%:%
%:%1128=1114%:%
%:%1129=1115%:%
%:%1130=1116%:%
%:%1131=1117%:%
%:%1132=1118%:%
%:%1133=1119%:%
%:%1134=1120%:%
%:%1135=1121%:%
%:%1136=1122%:%
%:%1137=1123%:%
%:%1138=1124%:%
%:%1139=1125%:%
%:%1140=1126%:%
%:%1141=1127%:%
%:%1142=1128%:%
%:%1143=1129%:%
%:%1144=1130%:%
%:%1145=1131%:%
%:%1146=1132%:%
%:%1147=1133%:%
%:%1151=1138%:%
%:%1155=1141%:%
%:%1156=1142%:%
%:%1157=1143%:%
%:%1158=1144%:%
%:%1162=1148%:%
%:%1166=1150%:%
%:%1167=1151%:%
%:%1168=1152%:%
%:%1169=1153%:%
%:%1169=1154%:%
%:%1170=1155%:%
%:%1171=1156%:%
%:%1172=1157%:%
%:%1173=1158%:%
%:%1177=1161%:%
%:%1178=1162%:%
%:%1179=1163%:%
%:%1180=1164%:%
%:%1181=1165%:%
%:%1182=1166%:%
%:%1183=1167%:%
%:%1184=1168%:%
%:%1185=1169%:%
%:%1186=1170%:%
%:%1187=1171%:%
%:%1188=1172%:%
%:%1189=1173%:%
%:%1190=1174%:%
%:%1191=1175%:%
%:%1192=1176%:%
%:%1193=1177%:%
%:%1194=1178%:%
%:%1195=1179%:%
%:%1196=1180%:%
%:%1197=1181%:%
%:%1198=1182%:%
%:%1199=1183%:%
%:%1203=1185%:%
%:%1204=1186%:%
%:%1205=1187%:%
%:%1206=1188%:%
%:%1207=1189%:%
%:%1208=1190%:%
%:%1209=1191%:%
%:%1210=1192%:%
%:%1211=1193%:%
%:%1212=1194%:%
%:%1213=1195%:%
%:%1214=1196%:%
%:%1215=1197%:%
%:%1216=1198%:%
%:%1217=1199%:%
%:%1218=1200%:%
%:%1219=1201%:%
%:%1220=1202%:%
%:%1221=1203%:%
%:%1225=1206%:%
%:%1229=1208%:%
%:%1229=1209%:%
%:%1230=1210%:%
%:%1231=1211%:%
%:%1232=1212%:%
%:%1233=1213%:%
%:%1234=1214%:%
%:%1235=1215%:%
%:%1236=1216%:%
%:%1237=1217%:%
%:%1241=1219%:%
%:%1245=1220%:%
%:%1246=1221%:%
%:%1247=1222%:%
%:%1248=1223%:%
%:%1249=1224%:%
%:%1250=1225%:%
%:%1251=1226%:%
%:%1252=1227%:%
%:%1253=1228%:%
%:%1254=1229%:%
%:%1255=1230%:%
%:%1256=1231%:%
%:%1257=1232%:%
%:%1258=1233%:%
%:%1259=1234%:%
%:%1260=1235%:%
%:%1261=1236%:%
%:%1262=1237%:%
%:%1263=1238%:%
%:%1264=1239%:%
%:%1265=1240%:%
%:%1268=1243%:%
%:%1269=1244%:%
%:%1270=1245%:%
%:%1271=1246%:%
%:%1272=1247%:%
%:%1273=1248%:%
%:%1276=1259%:%
%:%1285=1261%:%
%:%1297=1263%:%
%:%1297=1264%:%
%:%1301=1265%:%
%:%1302=1266%:%
%:%1304=1267%:%
%:%1305=1268%:%
%:%1310=1271%:%
%:%1311=1272%:%
%:%1312=1273%:%
%:%1313=1274%:%
%:%1314=1275%:%
%:%1315=1276%:%
%:%1316=1277%:%
%:%1317=1278%:%
%:%1318=1279%:%
%:%1318=1280%:%
%:%1319=1281%:%
%:%1320=1282%:%
%:%1321=1283%:%
%:%1322=1284%:%
%:%1323=1285%:%
%:%1324=1286%:%
%:%1325=1287%:%
%:%1334=1289%:%
%:%1346=1291%:%
%:%1347=1292%:%
%:%1348=1293%:%
%:%1349=1294%:%
%:%1350=1295%:%
%:%1351=1296%:%
%:%1352=1297%:%
%:%1353=1298%:%
%:%1353=1299%:%
%:%1354=1300%:%
%:%1355=1301%:%
%:%1356=1302%:%
%:%1357=1303%:%
%:%1358=1304%:%
%:%1359=1305%:%
%:%1360=1306%:%
%:%1361=1307%:%
%:%1362=1308%:%
%:%1363=1309%:%
%:%1364=1310%:%
%:%1365=1311%:%
%:%1366=1312%:%
%:%1367=1313%:%
%:%1368=1314%:%
%:%1369=1315%:%
%:%1370=1316%:%
%:%1371=1317%:%
%:%1372=1318%:%
%:%1373=1319%:%
%:%1374=1320%:%
%:%1375=1321%:%
%:%1376=1322%:%
%:%1377=1323%:%
%:%1378=1324%:%
%:%1379=1325%:%
%:%1380=1326%:%
%:%1381=1327%:%
%:%1382=1328%:%
%:%1386=1331%:%
%:%1390=1333%:%
%:%1391=1334%:%
%:%1392=1335%:%
%:%1393=1336%:%
%:%1394=1337%:%
%:%1395=1338%:%
%:%1396=1339%:%
%:%1397=1340%:%
%:%1398=1341%:%
%:%1399=1342%:%
%:%1400=1343%:%
%:%1401=1344%:%
%:%1402=1345%:%
%:%1403=1346%:%
%:%1404=1347%:%
%:%1405=1348%:%
%:%1406=1349%:%
%:%1407=1350%:%
%:%1408=1351%:%
%:%1409=1352%:%
%:%1410=1353%:%
%:%1411=1354%:%
%:%1412=1355%:%
%:%1413=1356%:%
%:%1414=1357%:%
%:%1415=1358%:%
%:%1416=1359%:%
%:%1417=1360%:%
%:%1418=1361%:%
%:%1419=1362%:%
%:%1420=1363%:%
%:%1421=1364%:%
%:%1422=1365%:%
%:%1423=1366%:%
%:%1424=1367%:%
%:%1425=1368%:%
%:%1426=1369%:%
%:%1427=1370%:%
%:%1428=1371%:%
%:%1429=1372%:%
%:%1430=1373%:%
%:%1431=1374%:%
%:%1432=1375%:%
%:%1433=1376%:%
%:%1434=1377%:%
%:%1435=1378%:%
%:%1436=1379%:%
%:%1437=1380%:%
%:%1438=1381%:%
%:%1439=1382%:%
%:%1440=1383%:%
%:%1441=1384%:%
%:%1442=1385%:%
%:%1443=1386%:%
%:%1444=1387%:%
%:%1445=1388%:%
%:%1446=1389%:%
%:%1447=1390%:%
%:%1448=1391%:%
%:%1449=1392%:%
%:%1450=1393%:%
%:%1451=1394%:%
%:%1452=1395%:%
%:%1453=1396%:%
%:%1454=1397%:%
%:%1455=1398%:%
%:%1456=1399%:%
%:%1457=1400%:%
%:%1458=1401%:%
%:%1459=1402%:%
%:%1460=1403%:%
%:%1461=1404%:%
%:%1462=1405%:%
%:%1463=1406%:%
%:%1464=1407%:%
%:%1465=1408%:%
%:%1466=1409%:%
%:%1467=1410%:%
%:%1468=1411%:%
%:%1469=1412%:%
%:%1470=1413%:%
%:%1471=1414%:%
%:%1472=1415%:%
%:%1473=1416%:%
%:%1474=1417%:%
%:%1475=1418%:%
%:%1476=1419%:%
%:%1477=1420%:%
%:%1478=1421%:%
%:%1479=1422%:%
%:%1480=1423%:%
%:%1481=1424%:%
%:%1482=1425%:%
%:%1483=1426%:%
%:%1484=1427%:%
%:%1485=1428%:%
%:%1486=1429%:%
%:%1487=1430%:%
%:%1488=1431%:%
%:%1489=1432%:%
%:%1490=1433%:%
%:%1491=1434%:%
%:%1492=1435%:%
%:%1493=1436%:%
%:%1494=1437%:%
%:%1495=1438%:%
%:%1496=1439%:%
%:%1497=1440%:%
%:%1498=1441%:%
%:%1499=1442%:%
%:%1500=1443%:%
%:%1501=1444%:%
%:%1502=1445%:%
%:%1503=1446%:%
%:%1504=1447%:%
%:%1505=1448%:%
%:%1506=1449%:%
%:%1507=1450%:%
%:%1508=1451%:%
%:%1509=1452%:%
%:%1510=1453%:%
%:%1511=1454%:%
%:%1512=1455%:%
%:%1513=1456%:%
%:%1514=1457%:%
%:%1515=1458%:%
%:%1516=1459%:%
%:%1517=1460%:%
%:%1518=1461%:%
%:%1519=1462%:%
%:%1520=1463%:%
%:%1521=1464%:%
%:%1522=1465%:%
%:%1523=1466%:%
%:%1524=1467%:%
%:%1525=1468%:%
%:%1526=1469%:%
%:%1527=1470%:%
%:%1528=1471%:%
%:%1529=1472%:%
%:%1530=1473%:%
%:%1531=1474%:%
%:%1532=1475%:%
%:%1533=1476%:%
%:%1534=1477%:%
%:%1535=1478%:%
%:%1536=1479%:%
%:%1537=1480%:%
%:%1538=1481%:%
%:%1539=1482%:%

### 2019-10-14 C11-FrontEnd/document/preamble.tex
synchronize with fortesse revision 5360

%e% This is a placeholder for user-specific configuration and packages.
\usepackage{lmodern}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{paralist}
\usepackage[en-US]{datetime2}      % For \DTMdate, etc.
\usepackage{amssymb}
\usepackage{listings}
\usepackage{lstisadof}
\usepackage{xspace}
\usepackage[draft]{fixme}
\usepackage{wrapfig}

\title{Deeply Integrating C11 Code Support into Isabelle/PIDE} % should be auto-generated
\addauthor{Frédéric Tuong\inst {1}} % should be auto-generated

\newcommand{\house}{\mathrel{\substack{\wedge\\[-.2em]\sqcup}}}

### 2019-10-15 C11-FrontEnd/document/generated/paper.tex
synchronize with fortesse revision 5366

@@
 \begin{isamarkuptitle*}%
-[label = {tit},type = {scholarly_paper.title}, args={label = {tit},type = {scholarly_paper.title}, scholarly_paper.title.short_title = {}}]Deeply Integrating C11 Code Support into Isabelle/PIDE%
+[label = {tit},type = {scholarly_paper.title}, args={label = {tit},type = {scholarly_paper.title}, scholarly_paper.title.short_title = {}}]Isabelle/C%
 \end{isamarkuptitle*}\isamarkuptrue%
-%
-\begin{isamarkuptext*}%
-[label = {bu},type = {scholarly_paper.author}, args={label = {bu},type = {scholarly_paper.author}, scholarly_paper.author.email = {wolff@lri.fr}, scholarly_paper.author.affiliation = {LRI, Univ.
-Paris-Sud, CNRS, Université Paris-Saclay}, scholarly_paper.author.http_site = {https://www.lri.fr/~wolff/}, scholarly_paper.author.orcid = {}}]Burkhart Wolff%
-\end{isamarkuptext*}\isamarkuptrue%
 %
@@
 \end{isabellebody}%
-\endinput
-%:%32=54%:%
-%:%36=61%:%
-%:%40=67%:%
-%:%41=68%:%
-%:%42=69%:%
-%:%43=70%:%
-%:%44=71%:%
-%:%45=72%:%
-%:%46=73%:%
-%:%47=74%:%
-%:%48=75%:%
-%:%49=76%:%
-%:%50=77%:%
-%:%51=78%:%
-%:%52=79%:%
-%:%53=80%:%
-%:%54=81%:%
-%:%55=82%:%
-%:%56=83%:%
-%:%57=84%:%
-%:%58=85%:%
-%:%62=88%:%
-%:%66=90%:%
-%:%67=91%:%
-%:%68=92%:%
-%:%69=93%:%
-%:%70=94%:%
-%:%71=95%:%
-%:%72=96%:%
-%:%73=97%:%
-%:%74=98%:%
-%:%75=99%:%
-%:%76=100%:%
-%:%77=101%:%
-%:%78=102%:%
-%:%79=103%:%
-%:%80=104%:%
-%:%81=105%:%
-%:%82=106%:%
-%:%83=107%:%
-%:%84=108%:%
-%:%85=109%:%
-%:%86=110%:%
-%:%87=111%:%
-%:%88=112%:%
-%:%89=113%:%
-%:%90=114%:%
-%:%91=115%:%
-%:%92=116%:%
-%:%93=117%:%
-%:%94=118%:%
-%:%95=119%:%
-%:%96=120%:%
-%:%97=121%:%
-%:%98=122%:%
-%:%99=123%:%
-%:%100=124%:%
-%:%101=125%:%
-%:%102=126%:%
-%:%103=127%:%
-%:%104=128%:%
-%:%105=129%:%
-%:%109=147%:%
-%:%113=149%:%
-%:%114=150%:%
-%:%115=151%:%
-%:%116=152%:%
-%:%117=153%:%
-%:%118=154%:%
-%:%119=155%:%
-%:%120=156%:%
-%:%121=157%:%
-%:%122=158%:%
-%:%126=169%:%
-%:%127=170%:%
-%:%128=171%:%
-%:%129=172%:%
-%:%130=173%:%
-%:%131=174%:%
-%:%132=175%:%
-%:%133=176%:%
-%:%137=179%:%
-%:%141=181%:%
-%:%142=182%:%
-%:%143=183%:%
-%:%144=184%:%
-%:%145=185%:%
-%:%146=186%:%
-%:%147=187%:%
-%:%148=188%:%
-%:%149=189%:%
-%:%153=193%:%
-%:%157=196%:%
-%:%161=200%:%
-%:%162=201%:%
-%:%163=202%:%
-%:%164=203%:%
-%:%165=204%:%
-%:%166=205%:%
-%:%167=206%:%
-%:%168=207%:%
-%:%169=208%:%
-%:%170=209%:%
-%:%171=210%:%
-%:%172=211%:%
-%:%173=212%:%
-%:%174=213%:%
-%:%175=214%:%
-%:%176=215%:%
-%:%177=216%:%
-%:%178=217%:%
-%:%179=218%:%
-%:%180=219%:%
-%:%189=221%:%
-%:%201=223%:%
-%:%202=224%:%
-%:%203=225%:%
-%:%204=226%:%
-%:%205=227%:%
-%:%206=228%:%
-%:%207=229%:%
-%:%208=230%:%
-%:%209=231%:%
-%:%210=232%:%
-%:%211=233%:%
-%:%212=234%:%
-%:%213=235%:%
-%:%214=236%:%
-%:%215=237%:%
-%:%216=238%:%
-%:%217=239%:%
-%:%218=240%:%
-%:%219=241%:%
-%:%220=242%:%
-%:%221=243%:%
-%:%222=244%:%
-%:%223=245%:%
-%:%224=246%:%
-%:%225=247%:%
-%:%226=248%:%
-%:%227=249%:%
-%:%228=250%:%
-%:%229=251%:%
-%:%230=252%:%
-%:%231=253%:%
-%:%232=254%:%
-%:%233=255%:%
-%:%234=256%:%
-%:%235=257%:%
-%:%236=258%:%
-%:%237=259%:%
-%:%238=260%:%
-%:%239=261%:%
-%:%240=262%:%
-%:%241=263%:%
-%:%242=264%:%
-%:%243=265%:%
-%:%244=266%:%
-%:%245=267%:%
-%:%246=268%:%
-%:%247=269%:%
-%:%248=270%:%
-%:%249=271%:%
-%:%250=272%:%
-%:%251=273%:%
-%:%252=274%:%
-%:%253=275%:%
-%:%254=276%:%
-%:%254=277%:%
-%:%255=278%:%
-%:%256=279%:%
-%:%257=280%:%
-%:%258=281%:%
-%:%259=282%:%
-%:%260=283%:%
-%:%261=284%:%
-%:%262=285%:%
-%:%263=286%:%
-%:%272=291%:%
-%:%284=294%:%
-%:%285=295%:%
-%:%286=296%:%
-%:%287=297%:%
-%:%288=298%:%
-%:%289=299%:%
-%:%290=300%:%
-%:%291=301%:%
-%:%292=302%:%
-%:%293=303%:%
-%:%294=304%:%
-%:%295=305%:%
-%:%296=306%:%
-%:%297=307%:%
-%:%298=308%:%
-%:%299=309%:%
-%:%300=310%:%
-%:%301=311%:%
-%:%302=312%:%
-%:%303=313%:%
-%:%304=314%:%
-%:%305=315%:%
-%:%306=316%:%
-%:%307=317%:%
-%:%311=320%:%
-%:%315=323%:%
-%:%316=324%:%
-%:%317=325%:%
-%:%318=326%:%
-%:%319=327%:%
-%:%320=328%:%
-%:%321=329%:%
-%:%322=330%:%
-%:%323=331%:%
-%:%324=332%:%
-%:%325=333%:%
-%:%326=334%:%
-%:%327=335%:%
-%:%328=336%:%
-%:%329=337%:%
-%:%330=338%:%
-%:%331=339%:%
-%:%332=340%:%
-%:%333=341%:%
-%:%334=342%:%
-%:%335=343%:%
-%:%339=347%:%
-%:%343=363%:%
-%:%347=364%:%
-%:%348=365%:%
-%:%350=366%:%
-%:%351=367%:%
-%:%356=370%:%
-%:%357=371%:%
-%:%358=372%:%
-%:%359=373%:%
-%:%360=374%:%
-%:%361=375%:%
-%:%365=377%:%
-%:%366=378%:%
-%:%367=379%:%
-%:%368=380%:%
-%:%369=381%:%
-%:%370=382%:%
-%:%371=383%:%
-%:%372=384%:%
-%:%373=385%:%
-%:%374=386%:%
-%:%375=387%:%
-%:%379=390%:%
-%:%380=391%:%
-%:%381=392%:%
-%:%382=393%:%
-%:%383=394%:%
-%:%387=397%:%
-%:%391=399%:%
-%:%392=400%:%
-%:%393=401%:%
-%:%394=402%:%
-%:%395=403%:%
-%:%399=432%:%
-%:%403=433%:%
-%:%404=434%:%
-%:%405=435%:%
-%:%406=436%:%
-%:%407=437%:%
-%:%408=438%:%
-%:%412=440%:%
-%:%413=441%:%
-%:%414=442%:%
-%:%415=443%:%
-%:%416=444%:%
-%:%420=445%:%
-%:%421=446%:%
-%:%423=447%:%
-%:%424=448%:%
-%:%426=449%:%
-%:%431=456%:%
-%:%432=457%:%
-%:%433=458%:%
-%:%433=459%:%
-%:%434=460%:%
-%:%435=461%:%
-%:%436=462%:%
-%:%437=463%:%
-%:%438=464%:%
-%:%439=465%:%
-%:%440=466%:%
-%:%449=468%:%
-%:%461=470%:%
-%:%462=471%:%
-%:%463=472%:%
-%:%464=473%:%
-%:%465=474%:%
-%:%466=475%:%
-%:%467=476%:%
-%:%468=477%:%
-%:%469=478%:%
-%:%469=479%:%
-%:%470=480%:%
-%:%471=481%:%
-%:%472=482%:%
-%:%473=483%:%
-%:%474=484%:%
-%:%483=486%:%
-%:%495=488%:%
-%:%496=489%:%
-%:%497=490%:%
-%:%498=491%:%
-%:%499=492%:%
-%:%500=493%:%
-%:%501=494%:%
-%:%510=496%:%
-%:%522=498%:%
-%:%523=499%:%
-%:%524=500%:%
-%:%525=501%:%
-%:%526=502%:%
-%:%527=503%:%
-%:%528=504%:%
-%:%529=505%:%
-%:%530=506%:%
-%:%531=507%:%
-%:%532=508%:%
-%:%533=509%:%
-%:%534=510%:%
-%:%535=511%:%
-%:%536=512%:%
-%:%537=513%:%
-%:%538=514%:%
-%:%539=515%:%
-%:%540=516%:%
-%:%541=517%:%
-%:%550=524%:%
-%:%562=530%:%
-%:%563=531%:%
-%:%564=532%:%
-%:%565=533%:%
-%:%566=534%:%
-%:%567=535%:%
-%:%568=536%:%
-%:%569=537%:%
-%:%570=538%:%
-%:%571=539%:%
-%:%572=540%:%
-%:%573=541%:%
-%:%574=542%:%
-%:%575=543%:%
-%:%576=544%:%
-%:%577=545%:%
-%:%586=558%:%
-%:%598=560%:%
-%:%599=561%:%
-%:%600=562%:%
-%:%604=568%:%
-%:%608=570%:%
-%:%609=571%:%
-%:%610=572%:%
-%:%611=573%:%
-%:%612=574%:%
-%:%613=575%:%
-%:%614=576%:%
-%:%618=579%:%
-%:%622=585%:%
-%:%623=586%:%
-%:%624=587%:%
-%:%625=588%:%
-%:%625=589%:%
-%:%626=590%:%
-%:%627=591%:%
-%:%628=592%:%
-%:%629=593%:%
-%:%630=594%:%
-%:%631=595%:%
-%:%632=596%:%
-%:%633=597%:%
-%:%634=598%:%
-%:%635=599%:%
-%:%636=600%:%
-%:%636=601%:%
-%:%637=602%:%
-%:%638=603%:%
-%:%639=604%:%
-%:%640=605%:%
-%:%641=606%:%
-%:%642=607%:%
-%:%643=608%:%
-%:%644=609%:%
-%:%645=610%:%
-%:%646=611%:%
-%:%647=612%:%
-%:%648=613%:%
-%:%649=614%:%
-%:%650=615%:%
-%:%651=616%:%
-%:%652=617%:%
-%:%653=618%:%
-%:%654=619%:%
-%:%655=620%:%
-%:%655=621%:%
-%:%656=622%:%
-%:%657=623%:%
-%:%658=624%:%
-%:%659=625%:%
-%:%660=626%:%
-%:%661=627%:%
-%:%662=628%:%
-%:%663=629%:%
-%:%664=630%:%
-%:%664=631%:%
-%:%665=632%:%
-%:%669=636%:%
-%:%673=638%:%
-%:%674=639%:%
-%:%675=640%:%
-%:%676=641%:%
-%:%677=642%:%
-%:%678=643%:%
-%:%679=644%:%
-%:%680=645%:%
-%:%681=646%:%
-%:%682=647%:%
-%:%683=648%:%
-%:%684=649%:%
-%:%685=650%:%
-%:%689=652%:%
-%:%693=659%:%
-%:%697=661%:%
-%:%697=662%:%
-%:%698=663%:%
-%:%699=664%:%
-%:%700=665%:%
-%:%701=666%:%
-%:%702=667%:%
-%:%703=668%:%
-%:%704=669%:%
-%:%705=670%:%
-%:%706=671%:%
-%:%707=672%:%
-%:%708=673%:%
-%:%709=674%:%
-%:%710=675%:%
-%:%711=676%:%
-%:%712=677%:%
-%:%713=678%:%
-%:%714=679%:%
-%:%715=680%:%
-%:%716=681%:%
-%:%717=682%:%
-%:%717=683%:%
-%:%718=684%:%
-%:%719=685%:%
-%:%728=687%:%
-%:%740=689%:%
-%:%741=690%:%
-%:%742=691%:%
-%:%743=692%:%
-%:%744=693%:%
-%:%745=694%:%
-%:%749=696%:%
-%:%750=697%:%
-%:%751=698%:%
-%:%753=700%:%
-%:%754=701%:%
-%:%755=702%:%
-%:%756=703%:%
-%:%758=705%:%
-%:%759=706%:%
-%:%760=707%:%
-%:%761=708%:%
-%:%762=709%:%
-%:%762=710%:%
-%:%763=711%:%
-%:%768=715%:%
-%:%769=716%:%
-%:%770=717%:%
-%:%771=718%:%
-%:%772=719%:%
-%:%776=765%:%
-%:%780=767%:%
-%:%780=768%:%
-%:%781=769%:%
-%:%782=770%:%
-%:%783=771%:%
-%:%784=772%:%
-%:%788=774%:%
-%:%789=775%:%
-%:%790=776%:%
-%:%791=777%:%
-%:%792=778%:%
-%:%793=779%:%
-%:%794=780%:%
-%:%795=781%:%
-%:%796=782%:%
-%:%797=783%:%
-%:%798=784%:%
-%:%799=785%:%
-%:%800=786%:%
-%:%801=787%:%
-%:%802=788%:%
-%:%803=789%:%
-%:%807=791%:%
-%:%808=792%:%
-%:%809=793%:%
-%:%810=794%:%
-%:%811=795%:%
-%:%812=796%:%
-%:%813=797%:%
-%:%814=798%:%
-%:%815=799%:%
-%:%816=800%:%
-%:%817=801%:%
-%:%818=802%:%
-%:%819=803%:%
-%:%820=804%:%
-%:%821=805%:%
-%:%825=815%:%
-%:%829=817%:%
-%:%830=818%:%
-%:%834=819%:%
-%:%835=820%:%
-%:%837=821%:%
-%:%838=822%:%
-%:%843=824%:%
-%:%844=825%:%
-%:%845=826%:%
-%:%846=827%:%
-%:%847=828%:%
-%:%848=829%:%
-%:%849=830%:%
-%:%850=831%:%
-%:%851=832%:%
-%:%851=833%:%
-%:%851=834%:%
-%:%852=835%:%
-%:%853=836%:%
-%:%854=837%:%
-%:%855=838%:%
-%:%856=839%:%
-%:%865=841%:%
-%:%877=845%:%
-%:%881=847%:%
-%:%882=848%:%
-%:%883=849%:%
-%:%884=850%:%
-%:%885=851%:%
-%:%886=852%:%
-%:%887=853%:%
-%:%888=854%:%
-%:%889=855%:%
-%:%890=856%:%
-%:%891=857%:%
-%:%892=858%:%
-%:%893=859%:%
-%:%894=860%:%
-%:%895=861%:%
-%:%896=862%:%
-%:%897=863%:%
-%:%898=864%:%
-%:%899=865%:%
-%:%900=866%:%
-%:%901=867%:%
-%:%902=868%:%
-%:%903=869%:%
-%:%904=870%:%
-%:%905=871%:%
-%:%906=872%:%
-%:%907=873%:%
-%:%907=874%:%
-%:%908=875%:%
-%:%909=876%:%
-%:%910=877%:%
-%:%911=878%:%
-%:%912=879%:%
-%:%913=880%:%
-%:%914=881%:%
-%:%915=882%:%
-%:%916=883%:%
-%:%917=884%:%
-%:%918=885%:%
-%:%922=888%:%
-%:%926=891%:%
-%:%930=893%:%
-%:%931=894%:%
-%:%932=895%:%
-%:%933=896%:%
-%:%934=897%:%
-%:%935=898%:%
-%:%936=899%:%
-%:%937=900%:%
-%:%938=901%:%
-%:%939=902%:%
-%:%940=903%:%
-%:%941=904%:%
-%:%942=905%:%
-%:%946=907%:%
-%:%947=908%:%
-%:%948=909%:%
-%:%949=910%:%
-%:%950=911%:%
-%:%951=912%:%
-%:%952=913%:%
-%:%953=914%:%
-%:%953=915%:%
-%:%954=916%:%
-%:%955=917%:%
-%:%956=918%:%
-%:%957=919%:%
-%:%958=920%:%
-%:%959=921%:%
-%:%959=922%:%
-%:%960=923%:%
-%:%961=924%:%
-%:%962=925%:%
-%:%966=928%:%
-%:%970=930%:%
-%:%971=931%:%
-%:%972=932%:%
-%:%973=933%:%
-%:%974=934%:%
-%:%975=935%:%
-%:%976=936%:%
-%:%977=937%:%
-%:%978=938%:%
-%:%979=939%:%
-%:%980=940%:%
-%:%981=941%:%
-%:%985=943%:%
-%:%986=944%:%
-%:%987=945%:%
-%:%988=946%:%
-%:%989=947%:%
-%:%990=948%:%
-%:%991=949%:%
-%:%992=950%:%
-%:%993=951%:%
-%:%994=952%:%
-%:%995=953%:%
-%:%996=954%:%
-%:%997=955%:%
-%:%997=956%:%
-%:%998=957%:%
-%:%999=958%:%
-%:%1000=959%:%
-%:%1001=960%:%
-%:%1002=961%:%
-%:%1003=962%:%
-%:%1004=963%:%
-%:%1005=964%:%
-%:%1006=965%:%
-%:%1007=966%:%
-%:%1008=967%:%
-%:%1009=968%:%
-%:%1010=969%:%
-%:%1011=970%:%
-%:%1012=971%:%
-%:%1013=972%:%
-%:%1014=973%:%
-%:%1015=974%:%
-%:%1015=975%:%
-%:%1016=976%:%
-%:%1017=977%:%
-%:%1018=978%:%
-%:%1019=979%:%
-%:%1020=980%:%
-%:%1021=981%:%
-%:%1022=982%:%
-%:%1022=983%:%
-%:%1026=985%:%
-%:%1027=986%:%
-%:%1028=987%:%
-%:%1029=988%:%
-%:%1030=989%:%
-%:%1031=990%:%
-%:%1032=991%:%
-%:%1033=992%:%
-%:%1034=993%:%
-%:%1035=994%:%
-%:%1036=995%:%
-%:%1037=996%:%
-%:%1038=997%:%
-%:%1039=998%:%
-%:%1040=999%:%
-%:%1041=1000%:%
-%:%1042=1001%:%
-%:%1046=1005%:%
-%:%1050=1009%:%
-%:%1054=1015%:%
-%:%1055=1016%:%
-%:%1056=1017%:%
-%:%1057=1018%:%
-%:%1058=1019%:%
-%:%1059=1020%:%
-%:%1060=1021%:%
-%:%1061=1022%:%
-%:%1062=1023%:%
-%:%1063=1024%:%
-%:%1064=1025%:%
-%:%1065=1026%:%
-%:%1066=1027%:%
-%:%1067=1028%:%
-%:%1068=1029%:%
-%:%1069=1030%:%
-%:%1070=1031%:%
-%:%1071=1032%:%
-%:%1072=1033%:%
-%:%1073=1034%:%
-%:%1074=1035%:%
-%:%1075=1036%:%
-%:%1076=1037%:%
-%:%1077=1038%:%
-%:%1078=1039%:%
-%:%1079=1040%:%
-%:%1080=1041%:%
-%:%1081=1042%:%
-%:%1082=1043%:%
-%:%1083=1044%:%
-%:%1084=1045%:%
-%:%1085=1046%:%
-%:%1086=1047%:%
-%:%1087=1048%:%
-%:%1088=1049%:%
-%:%1089=1050%:%
-%:%1090=1051%:%
-%:%1091=1052%:%
-%:%1092=1053%:%
-%:%1093=1054%:%
-%:%1094=1055%:%
-%:%1095=1056%:%
-%:%1096=1057%:%
-%:%1097=1058%:%
-%:%1098=1059%:%
-%:%1099=1060%:%
-%:%1099=1061%:%
-%:%1100=1062%:%
-%:%1101=1063%:%
-%:%1105=1092%:%
-%:%1109=1093%:%
-%:%1110=1094%:%
-%:%1111=1095%:%
-%:%1112=1096%:%
-%:%1112=1097%:%
-%:%1113=1098%:%
-%:%1114=1099%:%
-%:%1115=1100%:%
-%:%1116=1101%:%
-%:%1117=1102%:%
-%:%1117=1103%:%
-%:%1118=1104%:%
-%:%1122=1108%:%
-%:%1123=1109%:%
-%:%1124=1110%:%
-%:%1125=1111%:%
-%:%1126=1112%:%
-%:%1127=1113%:%
-%:%1128=1114%:%
-%:%1129=1115%:%
-%:%1130=1116%:%
-%:%1131=1117%:%
-%:%1132=1118%:%
-%:%1133=1119%:%
-%:%1134=1120%:%
-%:%1135=1121%:%
-%:%1136=1122%:%
-%:%1137=1123%:%
-%:%1138=1124%:%
-%:%1139=1125%:%
-%:%1140=1126%:%
-%:%1141=1127%:%
-%:%1142=1128%:%
-%:%1143=1129%:%
-%:%1144=1130%:%
-%:%1145=1131%:%
-%:%1146=1132%:%
-%:%1147=1133%:%
-%:%1151=1138%:%
-%:%1155=1141%:%
-%:%1156=1142%:%
-%:%1157=1143%:%
-%:%1158=1144%:%
-%:%1162=1148%:%
-%:%1166=1150%:%
-%:%1167=1151%:%
-%:%1168=1152%:%
-%:%1169=1153%:%
-%:%1169=1154%:%
-%:%1170=1155%:%
-%:%1171=1156%:%
-%:%1172=1157%:%
-%:%1173=1158%:%
-%:%1177=1161%:%
-%:%1178=1162%:%
-%:%1179=1163%:%
-%:%1180=1164%:%
-%:%1181=1165%:%
-%:%1182=1166%:%
-%:%1183=1167%:%
-%:%1184=1168%:%
-%:%1185=1169%:%
-%:%1186=1170%:%
-%:%1187=1171%:%
-%:%1188=1172%:%
-%:%1189=1173%:%
-%:%1190=1174%:%
-%:%1191=1175%:%
-%:%1192=1176%:%
-%:%1193=1177%:%
-%:%1194=1178%:%
-%:%1195=1179%:%
-%:%1196=1180%:%
-%:%1197=1181%:%
-%:%1198=1182%:%
-%:%1199=1183%:%
-%:%1203=1185%:%
-%:%1204=1186%:%
-%:%1205=1187%:%
-%:%1206=1188%:%
-%:%1207=1189%:%
-%:%1208=1190%:%
-%:%1209=1191%:%
-%:%1210=1192%:%
-%:%1211=1193%:%
-%:%1212=1194%:%
-%:%1213=1195%:%
-%:%1214=1196%:%
-%:%1215=1197%:%
-%:%1216=1198%:%
-%:%1217=1199%:%
-%:%1218=1200%:%
-%:%1219=1201%:%
-%:%1220=1202%:%
-%:%1221=1203%:%
-%:%1225=1206%:%
-%:%1229=1208%:%
-%:%1229=1209%:%
-%:%1230=1210%:%
-%:%1231=1211%:%
-%:%1232=1212%:%
-%:%1233=1213%:%
-%:%1234=1214%:%
-%:%1235=1215%:%
-%:%1236=1216%:%
-%:%1237=1217%:%
-%:%1241=1219%:%
-%:%1245=1220%:%
-%:%1246=1221%:%
-%:%1247=1222%:%
-%:%1248=1223%:%
-%:%1249=1224%:%
-%:%1250=1225%:%
-%:%1251=1226%:%
-%:%1252=1227%:%
-%:%1253=1228%:%
-%:%1254=1229%:%
-%:%1255=1230%:%
-%:%1256=1231%:%
-%:%1257=1232%:%
-%:%1258=1233%:%
-%:%1259=1234%:%
-%:%1260=1235%:%
-%:%1261=1236%:%
-%:%1262=1237%:%
-%:%1263=1238%:%
-%:%1264=1239%:%
-%:%1265=1240%:%
-%:%1268=1243%:%
-%:%1269=1244%:%
-%:%1270=1245%:%
-%:%1271=1246%:%
-%:%1272=1247%:%
-%:%1273=1248%:%
-%:%1276=1259%:%
-%:%1285=1261%:%
-%:%1297=1263%:%
-%:%1297=1264%:%
-%:%1301=1265%:%
-%:%1302=1266%:%
-%:%1304=1267%:%
-%:%1305=1268%:%
-%:%1310=1271%:%
-%:%1311=1272%:%
-%:%1312=1273%:%
-%:%1313=1274%:%
-%:%1314=1275%:%
-%:%1315=1276%:%
-%:%1316=1277%:%
-%:%1317=1278%:%
-%:%1318=1279%:%
-%:%1318=1280%:%
-%:%1319=1281%:%
-%:%1320=1282%:%
-%:%1321=1283%:%
-%:%1322=1284%:%
-%:%1323=1285%:%
-%:%1324=1286%:%
-%:%1325=1287%:%
-%:%1334=1289%:%
-%:%1346=1291%:%
-%:%1347=1292%:%
-%:%1348=1293%:%
-%:%1349=1294%:%
-%:%1350=1295%:%
-%:%1351=1296%:%
-%:%1352=1297%:%
-%:%1353=1298%:%
-%:%1353=1299%:%
-%:%1354=1300%:%
-%:%1355=1301%:%
-%:%1356=1302%:%
-%:%1357=1303%:%
-%:%1358=1304%:%
-%:%1359=1305%:%
-%:%1360=1306%:%
-%:%1361=1307%:%
-%:%1362=1308%:%
-%:%1363=1309%:%
-%:%1364=1310%:%
-%:%1365=1311%:%
-%:%1366=1312%:%
-%:%1367=1313%:%
-%:%1368=1314%:%
-%:%1369=1315%:%
-%:%1370=1316%:%
-%:%1371=1317%:%
-%:%1372=1318%:%
-%:%1373=1319%:%
-%:%1374=1320%:%
-%:%1375=1321%:%
-%:%1376=1322%:%
-%:%1377=1323%:%
-%:%1378=1324%:%
-%:%1379=1325%:%
-%:%1380=1326%:%
-%:%1381=1327%:%
-%:%1382=1328%:%
-%:%1386=1331%:%
-%:%1390=1333%:%
-%:%1391=1334%:%
-%:%1392=1335%:%
-%:%1393=1336%:%
-%:%1394=1337%:%
-%:%1395=1338%:%
-%:%1396=1339%:%
-%:%1397=1340%:%
-%:%1398=1341%:%
-%:%1399=1342%:%
-%:%1400=1343%:%
-%:%1401=1344%:%
-%:%1402=1345%:%
-%:%1403=1346%:%
-%:%1404=1347%:%
-%:%1405=1348%:%
-%:%1406=1349%:%
-%:%1407=1350%:%
-%:%1408=1351%:%
-%:%1409=1352%:%
-%:%1410=1353%:%
-%:%1411=1354%:%
-%:%1412=1355%:%
-%:%1413=1356%:%
-%:%1414=1357%:%
-%:%1415=1358%:%
-%:%1416=1359%:%
-%:%1417=1360%:%
-%:%1418=1361%:%
-%:%1419=1362%:%
-%:%1420=1363%:%
-%:%1421=1364%:%
-%:%1422=1365%:%
-%:%1423=1366%:%
-%:%1424=1367%:%
-%:%1425=1368%:%
-%:%1426=1369%:%
-%:%1427=1370%:%
-%:%1428=1371%:%
-%:%1429=1372%:%
-%:%1430=1373%:%
-%:%1431=1374%:%
-%:%1432=1375%:%
-%:%1433=1376%:%
-%:%1434=1377%:%
-%:%1435=1378%:%
-%:%1436=1379%:%
-%:%1437=1380%:%
-%:%1438=1381%:%
-%:%1439=1382%:%
-%:%1440=1383%:%
-%:%1441=1384%:%
-%:%1442=1385%:%
-%:%1443=1386%:%
-%:%1444=1387%:%
-%:%1445=1388%:%
-%:%1446=1389%:%
-%:%1447=1390%:%
-%:%1448=1391%:%
-%:%1449=1392%:%
-%:%1450=1393%:%
-%:%1451=1394%:%
-%:%1452=1395%:%
-%:%1453=1396%:%
-%:%1454=1397%:%
-%:%1455=1398%:%
-%:%1456=1399%:%
-%:%1457=1400%:%
-%:%1458=1401%:%
-%:%1459=1402%:%
-%:%1460=1403%:%
-%:%1461=1404%:%
-%:%1462=1405%:%
-%:%1463=1406%:%
-%:%1464=1407%:%
-%:%1465=1408%:%
-%:%1466=1409%:%
-%:%1467=1410%:%
-%:%1468=1411%:%
-%:%1469=1412%:%
-%:%1470=1413%:%
-%:%1471=1414%:%
-%:%1472=1415%:%
-%:%1473=1416%:%
-%:%1474=1417%:%
-%:%1475=1418%:%
-%:%1476=1419%:%
-%:%1477=1420%:%
-%:%1478=1421%:%
-%:%1479=1422%:%
-%:%1480=1423%:%
-%:%1481=1424%:%
-%:%1482=1425%:%
-%:%1483=1426%:%
-%:%1484=1427%:%
-%:%1485=1428%:%
-%:%1486=1429%:%
-%:%1487=1430%:%
-%:%1488=1431%:%
-%:%1489=1432%:%
-%:%1490=1433%:%
-%:%1491=1434%:%
-%:%1492=1435%:%
-%:%1493=1436%:%
-%:%1494=1437%:%
-%:%1495=1438%:%
-%:%1496=1439%:%
-%:%1497=1440%:%
-%:%1498=1441%:%
-%:%1499=1442%:%
-%:%1500=1443%:%
-%:%1501=1444%:%
-%:%1502=1445%:%
-%:%1503=1446%:%
-%:%1504=1447%:%
-%:%1505=1448%:%
-%:%1506=1449%:%
-%:%1507=1450%:%
-%:%1508=1451%:%
-%:%1509=1452%:%
-%:%1510=1453%:%
-%:%1511=1454%:%
-%:%1512=1455%:%
-%:%1513=1456%:%
-%:%1514=1457%:%
-%:%1515=1458%:%
-%:%1516=1459%:%
-%:%1517=1460%:%
-%:%1518=1461%:%
-%:%1519=1462%:%
-%:%1520=1463%:%
-%:%1521=1464%:%
-%:%1522=1465%:%
-%:%1523=1466%:%
-%:%1524=1467%:%
-%:%1525=1468%:%
-%:%1526=1469%:%
-%:%1527=1470%:%
-%:%1528=1471%:%
-%:%1529=1472%:%
-%:%1530=1473%:%
-%:%1531=1474%:%
-%:%1532=1475%:%
-%:%1533=1476%:%
-%:%1534=1477%:%
-%:%1535=1478%:%
-%:%1536=1479%:%
-%:%1537=1480%:%
-%:%1538=1481%:%
-%:%1539=1482%:%

### 2019-10-15 C11-FrontEnd/document/preamble.tex
simplify
synchronize with fortesse revision 5366

@@
 %e% This is a placeholder for user-specific configuration and packages.
-\usepackage{lmodern}
 \usepackage{textcomp}
@@
 
-\title{Deeply Integrating C11 Code Support into Isabelle/PIDE} % should be auto-generated
-\addauthor{Frédéric Tuong\inst {1}} % should be auto-generated
+\title{} % should be auto-generated
+\addauthor{\href{https://www.lri.fr/~ftuong/}{Frédéric Tuong}\inst{1} \and \href{https://www.lri.fr/~wolff/}{Burkhart Wolff}\inst{1}} % should be auto-generated
 

### 2019-10-17 C11-FrontEnd/document/generated/paper.tex
synchronize with fortesse
synchronize with fortesse revision 5374

@@
 \endisadelimML
-%
-\begin{isamarkuptitle*}%
-[label = {tit},type = {scholarly_paper.title}, args={label = {tit},type = {scholarly_paper.title}, scholarly_paper.title.short_title = {}}]Isabelle/C%
-\end{isamarkuptitle*}\isamarkuptrue%
 %
@@
 \cite{DBLP:conf/pldi/GreenawayLAK14}, IMP2 \cite{DBLP:journals/afp/LammichW19},
-Orca \cite{bockenek:hal-02069705}, or Clean (discussed in this paper). A particular advantage of
+Orca \cite{bockenek:hal-02069705}, or Clean \cite{journals/afp/TuongW19}. A particular advantage of
 the overall approach compared to systems like Frama-C or VCC is that all these semantic
@@
 In this section, we briefly present two integrations of verification back-ends for C. We
-chose Clean~\footnote{stemming from recent HOL-TestGen distributions
+chose Clean \cite{journals/afp/TuongW19}~\footnote{stemming from recent HOL-TestGen distributions
     \url{https://www.brucker.ch/projects/hol-testgen/index.en.html}} used
@@
 %
-\begin{isamarkuptext}%
+\begin{isamarkupsubsection*}%
+[label = {clean},type = {scholarly_paper.technical}, args={label = {clean},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''bu''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]A Simple Typed Memory Model: Clean%
+\end{isamarkupsubsection*}\isamarkuptrue%
+%
+\begin{isamarkuptext}%
+Clean (pronounced as: ``C lean'' or ``Céline'' [selin]) is based on a simple,
+shallow-style execution model for an imperative target language.
+Importing Clean into a theory with its activated back-end proceeds as in \autoref{fig:clean}.
+For a deep presentation of Clean, the reader is referred to the published AFP document \cite{journals/afp/TuongW19}.
+
 \begin{figure}
@@
 %%   \includegraphics[width=0.4\textwidth]{figures/A-C-Source10}
-%% \end{wrapfigure}%
+%% \end{wrapfigure}
+Finally, we will have a glance at the code for the registration of the annotation commands presented
+in \csname isaDof.ref\endcsname[type={Isa_COL.figure}]{C-sample10}, and used in the example of \autoref{fig:clean}. Thanks to
+Isabelle/C's function \isatt{C{\char`\_}Annotation.command{\char`\'}}, the registration of
+user-defined annotations is very similar to the registration of ordinary commands in the Isabelle
+platform.%
 \end{isamarkuptext}\isamarkuptrue%

### 2019-10-18 l4v/src/camkes/glue-proofs/DataIn.c
remove from the AFP branch

@@ -1,708 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the GNU General Public License version 2. Note that NO WARRANTY is provided.
- * See "LICENSE_GPLv2.txt" for details.
- *
- * @TAG(NICTA_GPL)
- */
-typedef
-signed
-char
-int8_t
-;
-typedef
-short
-int16_t
-;
-typedef
-int
-int32_t
-;
-typedef
-long
-long
-int64_t
-;
-typedef
-unsigned
-char
-uint8_t
-;
-typedef
-unsigned
-short
-uint16_t
-;
-typedef
-unsigned
-int
-uint32_t
-;
-typedef
-unsigned
-long
-long
-uint64_t
-;
-typedef
-int8_t
-int_fast8_t
-;
-typedef
-int
-int_fast16_t
-;
-typedef
-int
-int_fast32_t
-;
-typedef
-int64_t
-int_fast64_t
-;
-typedef
-unsigned
-char
-uint_fast8_t
-;
-typedef
-unsigned
-int
-uint_fast16_t
-;
-typedef
-unsigned
-int
-uint_fast32_t
-;
-typedef
-uint64_t
-uint_fast64_t
-;
-typedef
-long
-intptr_t
-;
-typedef
-unsigned
-long
-uintptr_t
-;
-typedef
-int8_t
-int_least8_t
-;
-typedef
-int16_t
-int_least16_t
-;
-typedef
-int32_t
-int_least32_t
-;
-typedef
-int64_t
-int_least64_t
-;
-typedef
-uint8_t
-uint_least8_t
-;
-typedef
-uint16_t
-uint_least16_t
-;
-typedef
-uint32_t
-uint_least32_t
-;
-typedef
-uint64_t
-uint_least64_t
-;
-typedef
-long
-long
-intmax_t
-;
-typedef
-unsigned
-long
-long
-uintmax_t
-;
-typedef
-unsigned
-size_t
-;
-typedef
-int
-ssize_t
-;
-typedef
-unsigned
-short
-__uint16_t
-;
-typedef
[…]

### 2019-10-18 l4v/src/camkes/glue-proofs/RPCFrom.c

@@ -1,4019 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the GNU General Public License version 2. Note that NO WARRANTY is provided.
- * See "LICENSE_GPLv2.txt" for details.
- *
- * @TAG(NICTA_GPL)
- */
-void abort(void);
-typedef
-unsigned
-size_t
-;
-typedef
-int
-ptrdiff_t
-;
-typedef
-unsigned
-wchar_t
-;
-typedef
-signed
-char
-int8_t
-;
-typedef
-short
-int16_t
-;
-typedef
-int
-int32_t
-;
-typedef
-long
-long
-int64_t
-;
-typedef
-unsigned
-char
-uint8_t
-;
-typedef
-unsigned
-short
-uint16_t
-;
-typedef
-unsigned
-int
-uint32_t
-;
-typedef
-unsigned
-long
-long
-uint64_t
-;
-typedef
-int8_t
-int_fast8_t
-;
-typedef
-int
-int_fast16_t
-;
-typedef
-int
-int_fast32_t
-;
-typedef
-int64_t
-int_fast64_t
-;
-typedef
-unsigned
-char
-uint_fast8_t
-;
-typedef
-unsigned
-int
-uint_fast16_t
-;
-typedef
-unsigned
-int
-uint_fast32_t
-;
-typedef
-uint64_t
-uint_fast64_t
-;
-typedef
-long
-intptr_t
-;
-typedef
-unsigned
-long
-uintptr_t
-;
-typedef
-int8_t
-int_least8_t
-;
-typedef
-int16_t
-int_least16_t
-;
-typedef
-int32_t
-int_least32_t
-;
-typedef
-int64_t
-int_least64_t
-;
-typedef
-uint8_t
-uint_least8_t
-;
-typedef
-uint16_t
-uint_least16_t
-;
-typedef
-uint32_t
-uint_least32_t
-;
-typedef
-uint64_t
-uint_least64_t
-;
-typedef
-long
-long
-intmax_t
-;
[…]

### 2019-10-18 l4v/src/camkes/glue-proofs/document/from-echo-int.c

@@ -1,33 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int RPCFrom_echo_int(int i) {
-    unsigned int _camkes_mr_index_12 = 0;
-
-    /* Marshal the method index */
-    seL4_SetMR(_camkes_mr_index_12, 0);
-    _camkes_mr_index_12 += 1;
-
-    /* Marshal all the parameters */
-    seL4_SetMR(_camkes_mr_index_12, (seL4_Word) i);
-    _camkes_mr_index_12 += 1;
-
-    /* Call the endpoint */
-    seL4_MessageInfo_t _camkes_info_13 =
-        seL4_MessageInfo_new(0, 0, 0, _camkes_mr_index_12);
-    (void)seL4_Call(6, _camkes_info_13);
-
-    /* Unmarshal the response */
-    _camkes_mr_index_12 = 0;
-    int _camkes_ret_14 = (int)seL4_GetMR(_camkes_mr_index_12);
-    _camkes_mr_index_12 += 1;
-
-    return _camkes_ret_14;
-}

### 2019-10-18 l4v/src/misc/benchmark/speedstep.sh

@@ -1,38 +1,0 @@
-#
-# Copyright 2014, NICTA
-#
-# This software may be distributed and modified according to the terms of
-# the BSD 2-Clause license. Note that NO WARRANTY is provided.
-# See "LICENSE_BSD2.txt" for details.
-#
-# @TAG(NICTA_BSD)
-#
-
-FREQ_AVAIL=/sys/devices/system/cpu/cpu0/cpufreq/scaling_available_frequencies
-FREQ_CONTROL=/sys/devices/system/cpu/cpu0/cpufreq/scaling_setspeed
-FREQ_GOV=/sys/devices/system/cpu/cpu0/cpufreq/scaling_governor
-FREQ_CUR=/sys/devices/system/cpu/cpu0/cpufreq/scaling_cur_freq
-
-FREQ_LIST=`cat ${FREQ_AVAIL}`
-
-OLD_GOV=`cat ${FREQ_GOV}`
-OLD_SPEED=`cat ${FREQ_CUR}`
-
-echo userspace > ${FREQ_GOV}
-echo -n "cpufreq governor is now "
-cat ${FREQ_GOV}
-
-for f in ${FREQ_LIST}
-do
-    echo $f > ${FREQ_CONTROL}
-    echo -n "CPU frequency is now "
-    cat ${FREQ_CUR}
-    sleep 1
-done
-
-echo ${OLD_SPEED} > ${FREQ_CONTROL}
-echo ${OLD_GOV} > ${FREQ_GOV}
-echo -n "Restored CPU frequency to "
-cat ${FREQ_CUR}
-echo -n "Restored cpufreq governor to "
-cat ${FREQ_GOV}

### 2019-10-18 l4v/src/misc/filemerge/faster/make_tables.py

@@ -1,52 +1,0 @@
-#!/usr/bin/env python
-
-#
-# Copyright 2015, NICTA
-#
-# This software may be distributed and modified according to the terms of
-# the BSD 2-Clause license. Note that NO WARRANTY is provided.
-# See "LICENSE_BSD2.txt" for details.
-#
-# @TAG(NICTA_BSD)
-#
-
-import argparse, os, sys
-
-MY_DIR = os.path.dirname(os.path.abspath(__file__))
-
-sys.path.append(os.path.join(MY_DIR, '../../../internal/misc/pysymbols'))
-import isasymbols
-
-def main(argv):
-    parser = argparse.ArgumentParser(
-        description='generate unicode-ascii translation tables')
-    parser.add_argument('--output', '-o', type=argparse.FileType('w'),
-        default=sys.stdout, help='output file')
-    options = parser.parse_args(argv[1:])
-
-    with open(os.path.join(MY_DIR, '../../../isabelle/etc/symbols')) as f:
-        t = isasymbols.Translator(f.read())
-
-    # Write an ASCII-to-unicode table.
-    options.output.write('static map<wstring, wchar_t> ascii_to_unicode = {\n')
-    for sym in t.symbols:
-        options.output.write('    { L"%s", L\'\\x%x\' },\n' %
-            (sym.ascii_text.replace('\\', '\\\\'), sym.code_point))
-    options.output.write('};\n\n')
-
-    # Write a unicode-to-ASCII table.
-    options.output.write('static map<wchar_t, wstring> unicode_to_ascii = {\n')
-    for s in t.symbols:
-        options.output.write('    { L\'\\x%x\', L"%s" },\n' %
-            (s.code_point, s.ascii_text.replace('\\', '\\\\')))
-    options.output.write('};\n\n')
-
-    # Work out the maximum length of an ASCII sequence.
-    ascii_seq_max = max(len(s.ascii_text) for s in t.symbols)
-    options.output.write('static const unsigned int ASCII_SEQ_MAX = %u;\n\n' %
-        ascii_seq_max)
-
-    return 0
-
-if __name__ == '__main__':
-    sys.exit(main(sys.argv))

### 2019-10-18 l4v/src/spec/cspec/mk_umm_types.py

@@ -1,89 +1,0 @@
-#!/usr/bin/env python
-#
-# Copyright 2014, NICTA
-#
-# This software may be distributed and modified according to the terms of
-# the BSD 2-Clause license. Note that NO WARRANTY is provided.
-# See "LICENSE_BSD2.txt" for details.
-#
-# @TAG(NICTA_BSD)
-#
-
-#
-# Generate the file "umm_types.txt", required for generating theory files used
-# in Isabelle sessions "CSpec" and beyond.
-#
-
-import subprocess
-import argparse
-import os
-import sys
-import tempfile
-import shutil
-
-# Create a temporary directory
-class TempDir(object):
-    def __enter__(self, cleanup=True):
-        self.filename = tempfile.mkdtemp()
-        self.cleanup = cleanup
-        return self.filename
-
-    def __exit__(self, type, value, traceback):
-        if self.cleanup:
-            shutil.rmtree(self.filename)
-        return False
-
-parser = argparse.ArgumentParser(
-        description="Generate a 'umm_types.txt' file from the C parser, required by the bitfield generator.")
-parser.add_argument('input', metavar='INPUT', type=str,
-        help="C file to parse")
-parser.add_argument('output', metavar='OUTPUT', type=str,
-        help="output filename")
-parser.add_argument('--root', metavar='ROOT', type=str,
-        help="add Isabelle ROOT or ROOTS file path", action='append')
-args = parser.parse_args()
-
-if "ISABELLE_PROCESS" not in os.environ or "ISABELLE_TOOL" not in os.environ:
-    print "Run this from within 'isabelle env'."
-    sys.exit(1)
-
-THY_DATA = """
-theory UmmTypesFile
-  imports CParser.CTranslation
-begin
-declare [[allow_underscore_idents = true]]
-external_file "%(input)s"
-setup {* IsarInstall.gen_umm_types_file "%(input)s" "%(output)s" *}
-end
-"""
-
-ROOT_DATA = """
-session UmmTypes = CParser +
-  theories UmmTypesFile
-"""
-
-# Create a new theory file and ROOT file in a temporary directory.
-with TempDir() as tmp_dir:
-    filenames = {
-            "input": os.path.abspath(args.input),
-            "output": os.path.abspath(args.output),
-            }
-    with open(os.path.join(tmp_dir, "UmmTypesFile.thy"), "w") as f:
-        f.write(THY_DATA % filenames)
[…]

### 2019-10-18 l4v/src/spec/haskell/include/mptimer.h

@@ -1,18 +1,0 @@
-/*
- * Copyright 2014, General Dynamics C4 Systems
- *
- * This software may be distributed and modified according to the terms of
- * the GNU General Public License version 2. Note that NO WARRANTY is provided.
- * See "LICENSE_GPLv2.txt" for details.
- *
- * @TAG(GD_GPL)
- */
-
-#include <stdint.h>
-/* Memory map for MCT */
-typedef struct mp_priv_timer {
-    uint32_t load;
-    uint32_t count;
-    uint32_t ctrl;
-    uint32_t ints;
-}priv_timer;

### 2019-10-18 l4v/src/spec/haskell/src/SEL4/API/Failures/RISCV64.hs

@@ -1,24 +1,0 @@
--- Copyright 2018, Data61, CSIRO
---
--- This software may be distributed and modified according to the terms of
--- the GNU General Public License version 2. Note that NO WARRANTY is provided.
--- See "LICENSE_GPLv2.txt" for details.
---
--- @TAG(DATA61_GPL)
-
--- This module defines the encoding of arch-specific faults.
-
-module SEL4.API.Failures.RISCV64 where
-
-import Prelude hiding (Word)
-import SEL4.Machine
-
--- note that typically the first word of vmFaultArchData corresponds to
--- "instructionFault", while the second to "FSR", in opposite order to C, where
--- "instructionFault" is the second, boolean, argument
-
-data ArchFault
-    = VMFault {
-            vmFaultAddress :: VPtr,
-            vmFaultArchData :: [Word] }
-    deriving Show

### 2019-10-18 l4v/src/spec/haskell/src/SEL4/API/Faults/RISCV64.hs

@@ -1,24 +1,0 @@
--- Copyright 2018, Data61, CSIRO
---
--- This software may be distributed and modified according to the terms of
--- the GNU General Public License version 2. Note that NO WARRANTY is provided.
--- See "LICENSE_GPLv2.txt" for details.
---
--- @TAG(DATA61_GPL)
-
-module SEL4.API.Faults.RISCV64 where
-
-import Prelude hiding (Word)
-import SEL4.Machine
-import SEL4.Model
-import SEL4.Object.Structures
-import SEL4.Object.TCB(asUser)
-import SEL4.API.Failures.RISCV64
-
-makeArchFaultMessage :: ArchFault -> PPtr TCB -> Kernel (Word, [Word])
-makeArchFaultMessage (VMFault vptr archData) thread = do
-    pc <- asUser thread getRestartPC
-    return (5, pc:fromVPtr vptr:archData)
-
-handleArchFaultReply :: ArchFault -> PPtr TCB -> Word -> [Word] -> Kernel Bool
-handleArchFaultReply (VMFault {}) _ _ _ = return True

### 2019-10-18 l4v/src/spec/haskell/src/SEL4/API/Invocation/RISCV64.hs

@@ -1,89 +1,0 @@
--- Copyright 2018, Data61, CSIRO
---
--- This software may be distributed and modified according to the terms of
--- the GNU General Public License version 2. Note that NO WARRANTY is provided.
--- See "LICENSE_GPLv2.txt" for details.
---
--- @TAG(DATA61_GPL)
-
--- This module defines the machine-specific invocations for RISC-V.
-
-{-# LANGUAGE EmptyDataDecls #-}
-
-module SEL4.API.Invocation.RISCV64 where
-
-import Prelude hiding (Word)
-import SEL4.Machine
-import SEL4.Machine.Hardware.RISCV64 as Arch hiding (PAddr, IRQ)
-import SEL4.Object.Structures
-import Data.Word (Word8, Word16, Word32)
-
-{- RISC-V-Specific Objects -}
-
--- This data type enumerates the object invocations that are possible.
--- These are invocations on the page table structures, on pages, and on
--- ASID pool structures.
-
-data Invocation
-    = InvokePageTable PageTableInvocation
-    | InvokePage PageInvocation
-    | InvokeASIDControl ASIDControlInvocation
-    | InvokeASIDPool ASIDPoolInvocation
-    deriving Show
-
-data PageTableInvocation
-    = PageTableUnmap {
-        ptUnmapCap :: ArchCapability,
-        ptUnmapCapSlot :: PPtr CTE }
-    | PageTableMap {
-        ptMapCap :: Capability,
-        ptMapCTSlot :: PPtr CTE,
-        ptMapPTE :: PTE,
-        ptMapPTSlot :: PPtr PTE }
-    deriving Show
-
-data PageInvocation
-    = PageGetAddr {
-        pageGetBasePtr :: PPtr Word }
-    | PageRemap {
-        pageRemapEntries :: (PTE, PPtr PTE) }
-    | PageMap {
-        pageMapCap :: Capability,
-        pageMapCTSlot :: PPtr CTE,
-        pageMapEntries :: (PTE, PPtr PTE) }
-    | PageUnmap {
-        pageUnmapCap :: ArchCapability,
-        pageUnmapCapSlot :: PPtr CTE }
-    deriving Show
-
-data ASIDControlInvocation
-    = MakePool {
-        makePoolFrame :: PPtr (),
-        makePoolSlot :: PPtr CTE,
-        makePoolParent :: PPtr CTE,
-        makePoolBase :: ASID }
-    deriving Show
-
-data ASIDPoolInvocation
-    = Assign {
[…]

### 2019-10-18 l4v/src/spec/haskell/src/SEL4/Machine/Hardware/ARM/KZM.hs

@@ -1,179 +1,0 @@
---
--- Copyright 2014, General Dynamics C4 Systems
---
--- This software may be distributed and modified according to the terms of
--- the GNU General Public License version 2. Note that NO WARRANTY is provided.
--- See "LICENSE_GPLv2.txt" for details.
---
--- @TAG(GD_GPL)
---
-
-{-# LANGUAGE EmptyDataDecls, ForeignFunctionInterface, GeneralizedNewtypeDeriving #-}
-
-module SEL4.Machine.Hardware.ARM.KZM where
-
-import Prelude hiding (Word)
-import SEL4.Machine.RegisterSet
-import Foreign.Ptr
-import Data.Bits
-import Data.Word(Word8)
-import Data.Ix
-import SEL4.Machine.Hardware.ARM.Callbacks
-
-
-newtype IRQ = IRQ Word8
-    deriving (Enum, Ord, Ix, Eq, Show)
-
-instance Bounded IRQ where
-    minBound = IRQ 0
-    maxBound = IRQ 31
-
-kernelBase :: VPtr
-kernelBase = VPtr 0xf0000000
-
-physBase = 0x80000000
-physMappingOffset = 0xf0000000 - physBase
-
-ptrFromPAddr :: PAddr -> PPtr a
-ptrFromPAddr (PAddr addr) = PPtr $ addr + physMappingOffset
-
-addrFromPPtr :: PPtr a -> PAddr
-addrFromPPtr (PPtr ptr) = PAddr $ ptr - physMappingOffset
-
-pageColourBits :: Int
-pageColourBits = 0 -- qemu has no cache
-
-getMemoryRegions :: Ptr CallbackData -> IO [(PAddr, PAddr)]
-getMemoryRegions _ = return [(0x80000000, 0x80000000 + (0x8 `shiftL` 24))]
-
-getDeviceRegions :: Ptr CallbackData -> IO [(PAddr, PAddr)]
-getDeviceRegions _ = return devices
-    where devices = [
-            (0x53f98000, 0x53f99000) -- second SP804; kernel uses first
-            ]
-
-timerPPtr = PPtr 0xfff00000
-timerAddr = PAddr 0x53f94000
-timerIRQ = IRQ 28
-
-avicPPtr = PPtr 0xfff01000
-avicAddr = PAddr 0x68000000
-
-getKernelDevices :: Ptr CallbackData -> IO [(PAddr, PPtr Word)]
-getKernelDevices _ = return devices
-    where devices = [
[…]

### 2019-10-18 l4v/src/spec/haskell/src/SEL4/Machine/Hardware/RISCV64.hs

@@ -1,315 +1,0 @@
--- Copyright 2018, Data61, CSIRO
---
--- This software may be distributed and modified according to the terms of
--- the GNU General Public License version 2. Note that NO WARRANTY is provided.
--- See "LICENSE_GPLv2.txt" for details.
---
--- @TAG(DATA61_GPL)
-
-{-# LANGUAGE CPP, GeneralizedNewtypeDeriving, EmptyDataDecls #-}
-
--- This module defines the low-level RISC-V hardware interface.
-
-module SEL4.Machine.Hardware.RISCV64 where
-
-import Prelude hiding (Word)
-import SEL4.Machine.RegisterSet
-
-import Foreign.Ptr
-import Control.Monad.Reader
-import Data.Bits
-import Data.Word(Word8, Word16, Word32, Word64)
-
--- The RISC-V 64bit-specific register set definitions are qualified with the
--- "RISCV" prefix, and the platform-specific hardware access functions are
--- qualified with the "Platform" prefix.
-
-import qualified SEL4.Machine.RegisterSet.RISCV64 as RISCV64
-import qualified SEL4.Machine.Hardware.RISCV64.PLATFORM as Platform
-
-{- Data Types -}
-
--- The machine monad contains a platform-specific opaque pointer, used by the
--- external simulator interface.
-
-type MachineMonad = ReaderT MachineData IO
-
-type MachineData = Ptr Platform.CallbackData
-
-type IRQ = Platform.IRQ
-
-toPAddr = Platform.PAddr
-
-{- Virtual Memory -}
-
--- these correspond to 4K, Mega and Giga pages in C
-
-data VMPageSize
-    = RISCVSmallPage
-    | RISCVLargePage
-    | RISCVHugePage
-    deriving (Show, Eq, Ord, Enum, Bounded)
-
-data VMFaultType
-    = RISCVInstructionMisaligned
-    | RISCVInstructionAccessFault
-    | RISCVInstructionIllegal
-    | RISCVBreakpoint
-    | RISCVLoadAccessFault
-    | RISCVAddressMisaligned
-    | RISCVStoreAccessFault
-    | RISCVEnvCall
-    | RISCVInstructionPageFault
-    | RISCVLoadPageFault
-    | RISCVStorePageFault
-    deriving Show
-
--- incomplete enumeration of VMFaultType, used only in handleVMFault, hence Word
[…]

### 2019-10-18 l4v/src/spec/haskell/src/SEL4/Machine/Hardware/RISCV64/Spike.hs

@@ -1,91 +1,0 @@
--- Copyright 2018, Data61, CSIRO
---
--- This software may be distributed and modified according to the terms of
--- the GNU General Public License version 2. Note that NO WARRANTY is provided.
--- See "LICENSE_GPLv2.txt" for details.
---
--- @TAG(DATA61_GPL)
-
-{-# LANGUAGE EmptyDataDecls, ForeignFunctionInterface, GeneralizedNewtypeDeriving #-}
-
-module SEL4.Machine.Hardware.RISCV64.Spike where
-
-import Prelude hiding (Word)
-import SEL4.Machine.RegisterSet
-import Foreign.Ptr
-import Data.Bits
-import Data.Word(Word8, Word16, Word32)
-import Data.Ix
-
-data CallbackData
-
-newtype IRQ = IRQ Word32
-    deriving (Enum, Ord, Ix, Eq, Show)
-
-instance Bounded IRQ where
-    minBound = IRQ 0
-    maxBound = IRQ 5 -- no external interrupts supported yet on spike
-
-newtype PAddr = PAddr { fromPAddr :: Word }
-    deriving (Integral, Real, Show, Eq, Num, Bits, FiniteBits, Ord, Enum, Bounded)
-
-kernelBase :: VPtr
-kernelBase = VPtr 0xFFFFFFFF80000000
-
-physBase = 0x0 -- called PADDR_BASE in C
-physMappingOffset = fromVPtr pptrBase - physBase -- called BASE_OFFSET in C
-paddrLoad = 0xC0000000
-kernelBaseOffset = fromVPtr kernelBase - paddrLoad
-
-ptrFromPAddr :: PAddr -> PPtr a
-ptrFromPAddr (PAddr addr) = PPtr $ addr + physMappingOffset
-
-addrFromPPtr :: PPtr a -> PAddr
-addrFromPPtr (PPtr ptr) = PAddr $ ptr - physMappingOffset
-
-addrFromKPPtr :: PPtr a -> PAddr
-addrFromKPPtr (PPtr ptr) = PAddr $ ptr - kernelBaseOffset
-
-pageColourBits :: Int
-pageColourBits = error "unused on this architecture"
-
-{- stubs -}
-
-pptrBase :: VPtr
-pptrBase = VPtr 0xFFFFFFC000000000
-
-pptrUserTop :: VPtr
-pptrUserTop = pptrBase
-
-{- simulator callback stubs - we do not plan to support the simulator on this
[…]

### 2019-10-18 l4v/src/spec/haskell/src/SEL4/Object/TCB/RISCV64.hs

@@ -1,48 +1,0 @@
--- Copyright 2018, Data61, CSIRO
---
--- This software may be distributed and modified according to the terms of
--- the GNU General Public License version 2. Note that NO WARRANTY is provided.
--- See "LICENSE_GPLv2.txt" for details.
---
--- @TAG(DATA61_GPL)
-
--- This module contains architecture-specific TCB management functions.
--- Specifically, these functions are used by the "CopyRegisters" operation to
--- transfer architecture-specific subsets of the register set.
-
--- There are presently no RISC-V-specific register subsets defined, but in
--- future this may be extended to transfer floating point registers and other
--- coprocessor state.
-
-module SEL4.Object.TCB.RISCV64 where
-
-import Prelude hiding (Word)
-import SEL4.Machine(PPtr)
-import SEL4.Model
-import SEL4.Object.Structures
-import SEL4.API.Failures
-import SEL4.API.Invocation.RISCV64
-import SEL4.Machine.RegisterSet(setRegister, UserMonad, VPtr(..))
-import qualified SEL4.Machine.RegisterSet as RegisterSet(Register(..))
-import SEL4.Machine.RegisterSet.RISCV64(Register(..), Word)
-import Data.Bits
-
-import Data.Word(Word8)
-
-decodeTransfer :: Word8 -> KernelF SyscallError CopyRegisterSets
-decodeTransfer _ = return RISCVNoExtraRegisters
-
-performTransfer :: CopyRegisterSets -> PPtr TCB -> PPtr TCB -> Kernel ()
-performTransfer _ _ _ = return ()
-
-sanitiseRegister :: Bool -> Register -> Word -> Word
-sanitiseRegister _ _ v = v
-
-getSanitiseRegisterInfo :: PPtr TCB -> Kernel Bool
-getSanitiseRegisterInfo _ = return False
-
-setTCBIPCBuffer :: VPtr -> UserMonad ()
-setTCBIPCBuffer ptr = setRegister (RegisterSet.Register TP) $ fromVPtr ptr
-
-postModifyRegisters :: PPtr TCB -> PPtr TCB -> UserMonad ()
-postModifyRegisters _ _ = return ()

### 2019-10-18 l4v/src/tools/autocorres/experiments/alloc-proof/alloc_lite.h

@@ -1,61 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-#ifndef _ALLOC_H_
-#define _ALLOC_H_
-
-#ifndef NULL
-#define NULL ((void *)0)
-#endif
-
-/* System word size. */
-typedef unsigned long word_t;
-
-/*
- * Allocator memory node.
- *
- * Used as a node in a linked list tracking free memory regions.
- */
-struct mem_node {
-    word_t size;
-    struct mem_node *next;
-};
-
-/*
- * Heap object.
- *
- * Contains a pointer to the first node in the chain, and also keeps
- * track of the number of allocations performed, so we know when the
- * entire heap is free.
- */
-struct heap {
-    word_t num_allocs;
-    struct mem_node *head;
-};
-
-/* Minimum granuality of the allocator (log2 of number of bytes). */
-#define ALLOC_CHUNK_SIZE_BITS 3
-
-/* Minimum alignment that the allocator will return. */
-#define DEFAULT_ALIGNMENT_BITS 3
-
-void *ualloc(struct heap* heap, word_t size);
-
-void *alloc(struct heap *heap, word_t size);
-
-void udealloc(struct heap* heap, void* ptr);
-
-void dealloc(struct heap *heap, void *ptr, word_t size);
-
-void add_mem_pool(struct heap *heap, void *ptr, word_t size);
-
-void init_allocator(struct heap *init_heap, struct mem_node *init_mem_node);
-
-#endif /* _ALLOC_H_ */

### 2019-10-18 l4v/src/tools/autocorres/experiments/alloc-proof/alloc_simp.c

@@ -1,91 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-// #define VERIFIED 1
-
-#ifndef VERIFIED
-#include <stdlib.h>
-#include <stdio.h>
-#endif
-
-#ifndef NULL
-#define NULL ((void *)0)
-#endif
-
-typedef unsigned long word_t;
-
-struct heap {
-    word_t max;
-    word_t curr;
-};
-
-void
-init_heap (struct heap* heap, word_t max){
-    heap->curr = (word_t) malloc(max);
-    //printf("%lu\n", heap->curr);
-    heap->max  = heap->curr + max;
-}
-
-void*
-alloc(struct heap* heap, word_t bytes){
-    if(heap->curr + bytes > heap->max)
-        return NULL;
-    heap->curr += bytes;
-    return (void*) heap->curr - bytes;
-}
-
-#ifndef VERIFIED
-int
-main(void){
-    struct heap* h = malloc(sizeof(struct heap));
-    init_heap(h, 1024);
-
-    int i, j;
-    int* ptr;
-
-    for (i = 0; i < 1024; i++) {
-        printf("%p\n", alloc(h, 1));
-    }
-
-    return 0;
-
-
-    int *x = alloc(h, 0x10);
-    printf("%p\n", x);
-    int *y = alloc(h, 0xffffffff);
-    printf("%p\n", y);
-    return 0;
-
-    /* allocate and write 128 ints to the heap */
-    for (i = 0; i < 1024; i += 4){
-        ptr = alloc(h, 4);
-        *ptr = i;
-    }
-
-    /* check written ints correct */
-    for (i = 1020; i > 0; i -= 4){
-        j = *ptr;
-        if(i != j){
-            printf("%d != %d\n",  i, j);
-        }
-        ptr--;
-    }
-
-    /* check heap is full */
-    void* null = alloc(h, 1);
-    if(null != NULL){
-        printf("null != NULL\n");
-    }
-
-
-
-    return 0;
-}
-#endif

### 2019-10-18 l4v/src/tools/autocorres/tests/examples/factorial.c

@@ -1,18 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-unsigned factorial(unsigned n) {
-  if(n == 0) return 1;
-  return n * factorial(n-1);
-}
-
-unsigned call_factorial(void) {
-  return factorial(42);
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/examples/fib.c

@@ -1,30 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-unsigned fib(unsigned n) {
-  if(n == 0) return 0;
-  if(n == 1) return 1;
-  return fib(n-1) + fib(n-2);
-}
-
-unsigned fib_linear(unsigned n) {
-  unsigned a = 0, b = 1;
-  while(n) {
-    unsigned t = b;
-    b += a;
-    a = t;
-    n -= 1;
-  }
-  return a;
-}
-
-void call_fib(void) {
-  fib(42);
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/examples/function_info.c

@@ -1,21 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-/*
- * The exact behaviour of these functions is unimportant for our example.
- */
-
-void rec() {
-  rec();
-}
-
-void f() {
-  rec();
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/examples/heap_wrap.c

@@ -1,59 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-/*
- * Simple test cases for heap_abs_syntax feature.
- * JIRA issue ID: VER-356
- */
-
-struct thing {
-  int x;
-  int *p;
-  struct thing *left;
-  struct thing *right;
-};
-
-struct list {
-  int x;
-  struct list *p;
-};
-
-void f1(struct thing *t) {
-  *t->p = 42;
-}
-
-void f2(struct thing *t) {
-  t->x = 42;
-}
-
-void f3(struct thing *t) {
-  t->right = t->left + 1;
-}
-
-void f4(struct thing *t) {
-  t->left = t;
-}
-
-void f5(struct thing *p, struct thing t) {
-  *p = t;
-}
-
-/* Signed word updates are still not translated correctly. */
-void f6(long long *p) {
-  *p = 42;
-}
-
-void f7(unsigned long long *p) {
-  *p = 42;
-}
-
-int f8(struct list *l, struct thing *t) {
-  return l->p->x && t->left->right->x;
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/examples/is_prime.c

@@ -1,58 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-#define SQRT_UINT_MAX 65536
-
-/*
- * Determine if the given number 'n' is prime.
- *
- * We return 0 if 'n' is composite, or non-zero if 'n' is prime.
- */
-unsigned is_prime_linear(unsigned n)
-{
-    /* Numbers less than 2 are not prime. */
-    if (n < 2)
-        return 0;
-
-    /* Find the first non-trivial factor of 'n'. */
-    for (unsigned i = 2; i < n; i++) {
-        if (n % i == 0)
-            return 0;
-    }
-
-    /* No factors. */
-    return 1;
-}
-
-/*
- * Determine if the given number 'n' is prime.
- *
- * We return 0 if 'n' is composite, or non-zero if 'n' is prime.
- *
- * Faster version that 'is_prime'; runs in O(sqrt(n)).
- */
-unsigned int is_prime(unsigned int n)
-{
-    /* Numbers less than 2 are not primes. */
-    if (n < 2)
-        return 0;
-
-    /* Find the first non-trivial factor of 'n' or sqrt(UINT_MAX), whichever
-     * comes first. */
-    /* Find the first non-trivial factor of 'n' less than sqrt(n). */
-    for (unsigned i = 2; i < SQRT_UINT_MAX && i * i <= n; i++) {
-        if (n % i == 0)
-            return 0;
-    }
-
-    /* No factors. */
-    return 1;
-}
-

### 2019-10-18 l4v/src/tools/autocorres/tests/examples/list.c

@@ -1,61 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-struct node {
-  int data;
-  struct node *next;
-};
-
-struct node *insert(struct node *x, struct node *list) {
-  x->next = list;
-  return x;
-}
-
-struct node *sorted_insert(struct node *x, struct node *list) {
-  struct node *prev = 0, *cur = list;
-  while (cur) {
-    if (cur->data >= x->data) {
-      if (prev) {
-        prev->next = x;
-        x->next = cur;
-        return list;
-      } else {
-        x->next = list;
-        return x;
-      }
-      prev = cur;
-      cur = cur->next;
-    }
-  }
-  x->next = 0;
-  prev->next = x;
-  return list;
-}
-
-struct node *reverse(struct node *list) {
-  struct node *rev = 0;
-  while (list) {
-    struct node *next = list->next;
-    list->next = rev;
-    rev = list;
-    list = next;
-  }
-  return rev;
-}
-
-struct node *revappend(struct node *list, struct node *dest) {
-  while (list) {
-    struct node *next = list->next;
-    list->next = dest;
-    dest = list;
-    list = next;
-  }
-  return dest;
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/examples/list_rev.c

@@ -1,26 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-#define NULL ((void *)0)
-
-struct node {
-  struct node *next;
-  int data;
-};
-
-struct node *reverse(struct node *list) {
-    struct node *rev = NULL;
-    while (list) {
-        struct node *next = list->next;
-        list->next = rev; rev = list; list = next;
-    }
-    return rev;
-}
-

### 2019-10-18 l4v/src/tools/autocorres/tests/examples/memcpy.c

@@ -1,33 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-void *memcpy(void *dest, void *src, unsigned long size) {
-    unsigned long i;
-    char *d = (char*)dest, *s = (char*)src;
-    for (i = 0; i < size; i++) {
-        d[i] = s[i];
-    }
-    return dest;
-}
-
-int *memcpy_int(int *dest, int *src) {
-    return memcpy(dest, src, sizeof(*dest));
-}
-
-struct my_structure {
-    char a;
-    int i;
-    long j;
-};
-
-struct my_structure *memcpy_struct(struct my_structure *dest,
-        struct my_structure *src) {
-    return memcpy(dest, src, sizeof(*dest));
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/examples/schorr_waite.c

@@ -1,117 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-#ifndef COMPILE
-#define NULL ((void*)0)
-#endif
-
-struct node {
-  struct node *l, *r;
-  unsigned m, c;
-};
-
-/* This is Mehta & Nipkow's version of the algorithm (HOL/Hoare/SchorrWaite.thy). */
-void schorr_waite(struct node *root) {
-  struct node *t = root, *p = NULL, *q;
-  while (p != NULL || (t != NULL && !t->m)) {
-    if (t == NULL || t->m) {
-      if (p->c) {
-        q = t; t = p; p = p->r; t->r = q;
-      } else {
-        q = t; t = p->r; p->r = p->l; p->l = q; p->c = 1;
-      }
-    } else {
-      q = p; p = t; t = t->l; p->l = q; p->m = 1; p->c = 0;
-    }
-  }
-}
-
-
-/*
- * An executable specification for graph traversal.
- */
-void simple_traverse(struct node *n) {
-  if (n == NULL || n->m) {
-    return;
-  }
-
-  n->m = 1;
-  simple_traverse(n->l);
-  simple_traverse(n->r);
-}
-
-#ifdef COMPILE
-#include <stdlib.h>
-#include <assert.h>
-#include <sys/time.h>
-#include <time.h>
-
-void make_graph(unsigned size, unsigned graph[size][2], struct node n[size]) {
-  for (unsigned i = 0; i < size; ++i) {
-    if (graph[i][0] == size) {
-      n[i].l = NULL;
-    } else {
-      n[i].l = &n[0] + graph[i][0];
-    }
-    if (graph[i][1] == size) {
-      n[i].r = NULL;
-    } else {
-      n[i].r = &n[0] + graph[i][1];
-    }
-    n[i].c = n[i].m = 0;
-  }
-}
-
-int main(void) {
-  const unsigned max_size = 1000;
-  unsigned graph[max_size][2];
-
-  struct timeval tv;
-  if (gettimeofday(&tv, NULL)) {
-    return 1;
-  }
[…]

### 2019-10-18 l4v/src/tools/autocorres/tests/examples/swap.c

@@ -1,17 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-void swap(unsigned *a, unsigned *b)
-{
-    unsigned t = *a;
-    *a = *b;
-    *b = t;
-}
-

### 2019-10-18 l4v/src/tools/autocorres/tests/examples/trace_demo.c

@@ -1,16 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-/*
- * Just a trivial function that exercises both heap_lift and word_abs.
- */
-void incr(int *p) {
-  (*p)++;
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/parse-tests/big_bit_ops.c

@@ -1,57 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-/*
- * Triggers a bug relating to combinations of complex bit operations
- * and bodiless functions.
- */
-
-void fr(unsigned long a, unsigned long b, unsigned long *c)
-        __attribute__((externally_visible))
-        __attribute__((__noreturn__));
-
-unsigned long global;
-
-struct word_struct {
-        unsigned long words[2];
-};
-
-static inline struct word_struct
-gen_struct(unsigned long a, unsigned long b, unsigned long c, unsigned long d) {
-    struct word_struct w;
-
-    w.words[0] = 0;
-    w.words[1] = 0;
-    w.words[1] |= (a & 0xfffffff8) >> 0;
-    w.words[1] |= (b & 0x1) << 1;
-    w.words[1] |= (c & 0x1) << 0;
-    w.words[0] |= (d & 0xfffffff8) >> 0;
-
-    return w;
-}
-
-void
-frw(int x)
-{
-    if (x) {
-        fr(3, 4, &global);
-        gen_struct(32, 53, 23, 543);
-    } else {
-        fr(1, 2, (void *)0);
-        gen_struct(1, 2, 3, 4);
-    }
-}
-
-void call_fr(void)
-{
-    fr(3, 4, &global);
-    fr(3, 4, &global);
-}
-

### 2019-10-18 l4v/src/tools/autocorres/tests/parse-tests/heap_lift_array.c

@@ -1,35 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-/*
- * Heap lifting for arrays.
- * Regression: JIRA VER-423.
- *
- * Unlike {read,write}_to_global_array.c, this takes the address of foo,
- * forcing C-parser to place it in symbol_table and not the globals record.
- * This tests the ability of AutoCorres to translate to the correct
- * heap access constructs on the lifted heap.
- */
-
-unsigned int foo[10];
-
-unsigned int bar(void) {
-    foo[1] = 42;
-    return foo[1];
-}
-
-unsigned int baz(void) {
-    unsigned int *qux = foo;
-    return qux[1];
-}
-
-unsigned int fuzz(unsigned int bizz[][10]) {
-    return bizz[1][1];
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/parse-tests/loop_test2.c

@@ -1,24 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int moocow(void)
-{
-    int a;
-    a = 3;
-    while (a < 3)
-        a++;
-    if (a % 54 == 0) {
-        a++;
-    } else {
-        a--;
-    }
-}
-
-

### 2019-10-18 l4v/src/tools/autocorres/tests/parse-tests/mutual_recursion.c

@@ -1,28 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int y(int z);
-
-int x(int a, int b)
-{
-    return y(a + b);
-}
-
-int y(int z)
-{
-    return x(z, z + 1) + x(z, z + 2);
-}
-
-
-int call_recursive(void)
-{
-    return y(3) + x(5, 9);
-}
-

### 2019-10-18 l4v/src/tools/autocorres/tests/parse-tests/read_global_array.c

@@ -1,36 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-typedef unsigned long word_t;
-typedef unsigned long tcb_t;
-word_t msgRegisters[] = {0, 1, 2, 3, 4, 5};
-
-void setRegister(tcb_t *receiver, word_t reg, word_t val)
-{
-}
-
-static inline unsigned int
-setMR(tcb_t *receiver, word_t* receiveIPCBuffer,
-        unsigned int offset, word_t reg)
-{
-    if (offset >= 42) {
-        if (receiveIPCBuffer) {
-            receiveIPCBuffer[offset + 1] = reg;
-            return offset + 1;
-        } else {
-            return 55;
-        }
-    } else {
-        setRegister(receiver, msgRegisters[offset], reg);
-        return offset + 1;
-    }
-}
-
-

### 2019-10-18 l4v/src/tools/autocorres/tests/parse-tests/signed_ptr_ptr.c

@@ -1,19 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-static int *arr_ptr_1;
-static int arr_1[120];
-
-static int **foo(void)
-{
-    arr_ptr_1 = arr_1;
-    return &arr_ptr_1;
-}
-

### 2019-10-18 l4v/src/tools/autocorres/tests/parse-tests/simple.c

@@ -1,15 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-unsigned add(unsigned a, unsigned b, unsigned c)
-{
-    return a + b + c;
-}
-

### 2019-10-18 l4v/src/tools/autocorres/tests/parse-tests/unliftable_call.c

@@ -1,38 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-/* Heap-unliftable functions calling liftable ones and vice versa. */
-
-int f(int x) {
-  return x + 1;
-}
-int g(int x) {
-  return g(x + 1);
-}
-
-int *call_f(void *mem) {
-  /** AUXUPD: "(True, ptr_retyp (ptr_coerce \<acute>mem :: word32 ptr))" */
-  *(int*)mem = f(g(*(int*)mem));
-}
-
-void rec_untyp(int*);
-void rec_typ(void *mem) {
-  /** AUXUPD: "(True, ptr_retyp (ptr_coerce \<acute>mem :: word32 ptr))" */
-  rec_untyp(mem);
-}
-void rec_untyp(int *ptr) {
-  *ptr = f(g(*ptr));
-  /** AUXUPD: "(True, ptr_retyp (ptr_coerce \<acute>ptr :: unit ptr))" */
-  rec_typ(ptr);
-}
-
-void call_all(void) {
-  rec_untyp(call_f(0));
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/parse-tests/voidptrptr.c

@@ -1,19 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int a;
-void *b;
-void **c;
-
-int main(void) {
-    b = &a;
-    c = &b;
-    return 3;
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/parse-tests/while_loop_no_vars.c

@@ -1,14 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int foo(int a, int b)
-{
-    return a + b;
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/parse-tests/word_abs_exn.c

@@ -1,27 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-/*
- * Regression test: word_abstract on L2_catch/L2_call.
- */
-
-int bad(int i) {
-  return i == 0;
-}
-
-int bads(unsigned n) {
-  unsigned i;
-  for (i = 0; i < n; i++) {
-    if (bad(i)) {
-      return 1;
-    }
-  }
-  return 0;
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/proof-tests/array_indirect_update.c

@@ -1,25 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-/*
- * Regression for VER-320 and other array-related bugs.
- */
-
-int array[10];
-
-void foo(int *a)
-{
-    *a = 3;
-}
-
-void bar(void)
-{
-    foo(&array[4]);
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/proof-tests/custom_word_abs.c

@@ -1,24 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int a(int x, int y)
-{
-    return x ^ ((x ^ y) & -(x < y));
-}
-
-unsigned b(unsigned x, unsigned y)
-{
-    return x & ((1U << y) - 1U);
-}
-
-unsigned c(unsigned x, unsigned y)
-{
-    return x > x + y;
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/proof-tests/global_array_update.c

@@ -1,23 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-
-static int foo[1024];
-
-void bar(void)
-{
-    /* Index 3 is thrown away. */
-    foo[3] = 42;
-}
-int * bar2(void)
-{
-    return &foo[3];
-}
-

### 2019-10-18 l4v/src/tools/autocorres/tests/proof-tests/skip_heap_abs.c

@@ -1,19 +1,0 @@
-/*
- * Copyright 2016, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-/*
- * Simple test for skip_heap_abs.
- */
-
-int f(int *p) {
-  int n = *p;
-  *p = n + 1;
-  return n;
-}

### 2019-10-18 l4v/src/tools/autocorres/tests/proof-tests/struct2.c

@@ -1,95 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-struct s {
-    unsigned long x;
-};
-
-struct word_struct {
-        unsigned long words[2];
-};
-
-struct sc {
-    struct s cap;
-    struct word_struct ws;
-};
-
-static inline unsigned __attribute__((__const__))
-    bb(struct word_struct word_struct) {
-        return (word_struct.words[0] & 0xfffffff8) << 0;
-    }
-
-static inline struct s __attribute__((__const__))
-    cncn(void) {
-        struct s x;
-        x.x = 0;
-        return x;
-    }
-
-static inline unsigned __attribute__((__const__))
-    aa(struct word_struct word_struct) {
-            return (word_struct.words[1] & 0xfffffff8) << 0;
-    }
-
-static inline void
-ff(struct word_struct *mdb_node_ptr, unsigned v) {
-        mdb_node_ptr->words[1] &= ~0xfffffff8;
-            mdb_node_ptr->words[1] |= (v >> 0) & 0xfffffff8;
-}
-
-static inline struct word_struct __attribute__((__const__))
-    cc(struct word_struct word_struct, unsigned v) {
-            word_struct.words[0] &= ~0xfffffff8;
-                word_struct.words[0] |= (v >> 0) & 0xfffffff8;
-                    return word_struct;
-    }
-
-static inline void
-ee(struct word_struct *mdb_node_ptr, unsigned v) {
-        mdb_node_ptr->words[0] &= ~0xfffffff8;
-            mdb_node_ptr->words[0] |= (v >> 0) & 0xfffffff8;
-}
-
-static inline struct word_struct
-mk_word_struct(unsigned long a, unsigned long b, unsigned long c, unsigned long d) {
-    struct word_struct w;
-
-    w.words[0] = 0;
-    w.words[1] = 0;
-    w.words[1] |= (a & 0xfffffff8);
-    w.words[1] |= (b & 0x1) << 1;
-    w.words[1] |= (c & 0x1);
-    w.words[0] |= (d & 0xfffffff8);
-
-    return w;
-}
-
-
-void
[…]

### 2019-10-18 l4v/src/tools/autocorres/tests/proof-tests/while_loop_vars_preserved.c

@@ -1,32 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-unsigned loop(unsigned dog, unsigned cat, unsigned mouse, unsigned horse)
-{
-    unsigned iterations = 0;
-    while (dog > 0 || cat > 0 || mouse > 0 || horse > 0) {
-        if (dog > horse) {
-            dog--;
-        } else if (horse > mouse) {
-            horse--;
-        } else if (cat > 0) {
-            cat--;
-        } else if (mouse > 0) {
-            mouse--;
-        } else if (dog > 0) {
-            dog--;
-        } else {
-            horse--;
-        }
-        iterations++;
-    }
-    return iterations;
-}
-

### 2019-10-18 l4v/src/tools/autocorres/tests/proof-tests/word_abs_fn_call.c

@@ -1,94 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-typedef unsigned char uint8_t;
-typedef unsigned int uint32_t;
-
-uint8_t foo(int a, uint32_t b, uint8_t c)
-{
-            return a + b + c;
-}
-
-uint8_t bar(int a, uint32_t b, uint8_t c)
-{
-            return foo(1, 2, foo(1, 2, 3));
-}
-
-uint32_t foo2(int a, uint32_t b, uint8_t c)
-{
-            return a + b + c;
-}
-
-uint32_t bar2(int a, uint32_t b, uint8_t c)
-{
-            return foo2(a, b, foo2(1, 2, 3));
-}
-
-uint8_t foo3(int a, uint32_t b, uint8_t c)
-{
-            return a + b + c;
-}
-
-uint8_t bar3(int a, uint32_t b, uint8_t c)
-{
-            return foo3(1, 2, foo3(1, 2, 3));
-}
-
-uint32_t foo4(int a, uint32_t b, uint8_t c)
-{
-            return a + b + c;
-}
-
-uint32_t bar4(int a, uint32_t b, uint8_t c)
-{
-            return foo4(a, b, foo2(1, 2, 3));
-}
-
-uint8_t foo5(int a, uint32_t b, uint8_t c)
-{
-            return a + b + c;
-}
-
-uint8_t bar5(int a, uint32_t b, uint8_t c)
-{
-            return foo(1, 2, foo(1, 2, 3));
-}
-
-uint32_t foo6(int a, uint32_t b, uint8_t c)
-{
-            return a + b + c;
-}
-
-uint32_t bar6(int a, uint32_t b, uint8_t c)
-{
-            return foo2(a, b, foo2(1, 2, 3));
-}
-
-uint8_t foo7(int a, uint32_t b, uint8_t c)
-{
-            return a + b + c;
-}
-
-uint8_t bar7(int a, uint32_t b, uint8_t c)
-{
-            return foo3(1, 2, foo3(1, 2, 3));
-}
-
-uint32_t foo8(int a, uint32_t b, uint8_t c)
-{
-            return a + b + c;
-}
-
[…]

### 2019-10-18 l4v/src/tools/autocorres/tools/stats/schorr_waite.c

@@ -1,34 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-
-#define NULL ((void *)0)
-
-struct node {
-  struct node *l, *r;
-  unsigned m, c;
-};
-
-/* This is Mehta & Nipkow's version of the algorithm (HOL/Hoare/SchorrWaite.thy). */
-void schorr_waite(struct node *root) {
-  struct node *t = root, *p = NULL, *q;
-  while (p != NULL || (t != NULL && !t->m)) {
-    if (t == NULL || t->m) {
-      if (p->c) {
-        q = t; t = p; p = p->r; t->r = q;
-      } else {
-        q = t; t = p->r; p->r = p->l; p->l = q; p->c = 1;
-      }
-    } else {
-      q = p; p = t; t = t->l; p->l = q; p->m = 1; p->c = 0;
-    }
-  }
-}
-

### 2019-10-18 l4v/src/tools/c-parser/testfiles/analsignedoverflow.c

@@ -1,17 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-signed char c;
-
-int f(void)
-{
-  c += 10;
-  return c;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/array_of_ptr.c

@@ -1,18 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int *a[4];
-
-struct s {
-  int *b[4];
-};
-
-
-

### 2019-10-18 l4v/src/tools/c-parser/testfiles/automatic_modifies.c

@@ -1,70 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int x, y;
-
-int array1[10], array2[20];
-
-int *ptr;
-
-int f(void)
-{
-  x = 3;
-  return y;
-}
-
-void g1(int i)
-{
-  array1[i] = f();
-}
-
-void g2(int j)
-{
-  *ptr = f();
-}
-
-void h(int i)
-{
-  g1(i);
-}
-
-void ifn(int *p, int i)
-{
-  *p = i;
-}
-
-void jfn(void)
-{
-  ifn(array2 + 3);
-}
-
-void k(void)
-{
-  y = f();
-}
-
-void mrec2(void);
-void mrec1(void)
-{
-  int tmp = mrec2();
-  array1[f()] = tmp;
-}
-
-void mrec2(void)
-{
-  if (x > 4) mrec1();
-  else y = 10;
-}
-
-int a(void)
-{
-  mrec2();
-  return 3;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/basic_char.c

@@ -1,19 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int f (int i)
-{
-  return i + 1;
-}
-
-int g(char c)
-{
-  return f(c + 3);
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/bug20060707.c

@@ -1,19 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-unsigned int x;
-
-void f(unsigned int n)
-{
-  while (x < n)
-    /** INV: "\<lbrace> (x_addr::32 word ptr) = c \<rbrace>" */
-    x = x + n;
-}
-

### 2019-10-18 l4v/src/tools/c-parser/testfiles/bugzilla182.c

@@ -1,34 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-struct small {
-  int fld;
-};
-
-struct moderate {
-  struct small many[10][10];
-};
-
-struct small array[10][10];
-
-int f(int i, int j, struct moderate *mptr)
-{
-  return mptr->many[i][j].fld;
-}
-
-void g(int *ptr, int val)
-{
-  *ptr = val;
-}
-
-void h(int i, int j)
-{
-  g(&array[i][j].fld, 3);
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/builtins.c

@@ -1,25 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int g(int);
-int f(int i)
-{
-  if (__builtin_expect(i < 0, 0)) return g(-i);
-  else return i + 3;
-}
-
-int g(int i)
-{
-  int acc = i < 0 ? i : 0;
-  while (acc < i) /** INV: "\<lbrace> \<acute>acc <=s \<acute>i \<rbrace>" */ {
-    acc++;
-  }
-  return acc;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/dont_translate.c

@@ -1,54 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int x;
-
-/** DONT_TRANSLATE
-    MODIFIES: [*]
-*/
-void scary(void)
-{
-  volatile int *x = 0xdeadbeef;
-  *x = 10;
-}
-
-/**
-   MODIFIES:
- */
-void not_scary(void);
-
-/**
-   DONT_TRANSLATE
-*/
-void not_scary(void)
-{
-  volatile int *x = 0xdeadbeef;
-  *x = 10;
-}
-
-void somewhat_scary(void);
-
-/**
-   DONT_TRANSLATE
-   MODIFIES:
-*/
-void somewhat_scary(void)
-{
-  volatile int *x = 0xdeadbeef;
-  *x = 10;
-}
-
-int f(void)
-{
-  scary();
-  not_scary();
-  somewhat_scary();
-  return 3;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/dupthms.c

@@ -1,33 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int array1[10];
-int array2[10];
-char array3[10];
-
-struct s {
-  int fld1;
-  int array[1];
-};
-
-struct t {
-  struct s v1, v2;
-};
-
-struct u {
-  char carray[3];
-  int iarray[3];
-  struct s v;
-};
-
-int f(struct u uval)
-{
-  return uval.carray[0] + uval.iarray[1] + uval.v.fld1;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/errors/bad_fldref.c

@@ -1,18 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-/* references to non-existent fields are caught */
-
-struct s {
-  int x;
-  int y;
-};
-
-int f (struct s r) { return r.z; }

### 2019-10-18 l4v/src/tools/c-parser/testfiles/errors/unterminated_comment.c

@@ -1,12 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int f /* hellow this is a comment
-

### 2019-10-18 l4v/src/tools/c-parser/testfiles/gcc_attribs.c

@@ -1,22 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int array1[10][20] __attribute__((foo)) __attribute__((bar));
-
-void f(int pos1, int pos2, int val)
-{
-  array1[pos1][pos2] = val;
-}
-
-__attribute__((noreturn))
-int myexit(int);
-
-int myexit2(int, int) __attribute__((noreturn));
-

### 2019-10-18 l4v/src/tools/c-parser/testfiles/globsall_addressed.c

@@ -1,29 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int glob1;
-const int wannabe_constant = 3;
-int really_addressed;
-
-int deref(int *p)
-{
-  return *p;
-}
-
-
-int f(void)
-{
-  int y = deref(&really_addressed);
-  glob1++;
-  y += glob1;
-  return y + wannabe_constant;
-}
-
-

### 2019-10-18 l4v/src/tools/c-parser/testfiles/guard_while.c

@@ -1,18 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int f(int x)
-{
-  int i = 10;
-  unsigned *ptr;
-  while (i / x + 1) x--;
-  for (*ptr = 3; i / *ptr > 4; ptr++);
-  return x + 1;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/hexliteral.c

@@ -1,20 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-unsigned int f(void)
-{
-  return 0xffffffff;
-}
-
-char g(void)
-{
-  unsigned i = 0xffffffff;
-  return i & 0xca;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/includes/accentéd1.h

@@ -1,13 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-#define FOO 1
-
-int included_f(int);

### 2019-10-18 l4v/src/tools/c-parser/testfiles/includes/test_include2.h

@@ -1,13 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int included_fn(int);
-
-int included_global;

### 2019-10-18 l4v/src/tools/c-parser/testfiles/inner_fncalls.c

@@ -1,46 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-/* this proto is for a function not defined in this translation unit */
-int h(unsigned long);
-int global;
-
-
-
-int f(int x, int y)
-{
-  return global + h(6 * x) * y;
-}
-
-void e(int x)
-{
-  global = 3;
-  global = f(x,2);
-}
-
-int g(int y)
-{
-  int local = global * (f(y - 2, y) + h(y));
-  while (h(local)) {
-    local += 10;
-  }
-  return f(local,h(7));
-}
-
-
-int f2(int x)
-{
-  return f(g(x + 1),g(6));
-}
-
-char function(int c) { return c + 1; }
-
-int function2(int x) { return g(function(x)); }
-

### 2019-10-18 l4v/src/tools/c-parser/testfiles/int_promotion.c

@@ -1,15 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int f(void)
-{
-  unsigned char c = 200;
-  return (c == 200);
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/isa2014.c

@@ -1,27 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int x, y;
-
-int f(int i)
-{
-  return i + 1;
-}
-
-int g(int *iptr)
-{
-  return iptr ? *iptr : 0;
-}
-
-/** MODIFIES: x */
-void ff(int i)
-{
-  x += i * g(&y);
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/jiraver110.c

@@ -1,30 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int g (int n) {
-  return n;
-}
-
-int
-f (int n) {
-  switch (n) {
-    case 0:
-      n++;
-      if (n == 1)
-        break;
-      return 3;
-    case 1:
-      return 0;
-    default:
-      break;
-  };
-  return g (n);
-}
-

### 2019-10-18 l4v/src/tools/c-parser/testfiles/jiraver315.c

@@ -1,22 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-typedef struct {
-  int x;
-  char y;
-} s_t;
-
-s_t *s;
-
-int f(void)
-{
-  int * const p = &(s->x);
-  return *p;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/jiraver384.c

@@ -1,21 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int global;
-void foo(void)
-{
-  void bar(void);
-  bar();
-}
-
-/** FNSPEC
-      some_external_spec: "\<Gamma> \<turnstile> {} Call some_external_'proc {}"
-*/
-int some_external(void);

### 2019-10-18 l4v/src/tools/c-parser/testfiles/jiraver429.c

@@ -1,18 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-
-
-unsigned int foo(unsigned int *bar) {
-  if (bar != 0) {
-    return *bar;
-  }
-  return 0;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/jiraver432.c

@@ -1,25 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-struct {
-  int fld1;
-  char fld2;
-  _Bool fld3;
-} global1;
-
-struct {
-  int fld;
-} global2;
-
-char f(void)
-{
-  global1.fld1++;
-  return global1.fld2;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/jiraver434.c

@@ -1,19 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-typedef struct {
-  int r2, r3;
-} seL4_UserContext;
-
-int
-useContext(seL4_UserContext *ucptr)
-{
-  return ucptr->r2 + ucptr->r3;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/jiraver440.c

@@ -1,22 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int x;
-
-int f(int i)
-{
-  extern int x;
-  return x + i;
-}
-
-int g(int i)
-{
-  return x + i;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/jiraver443a.c

@@ -1,33 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-struct foo {
-  int x, thread_index;
-} glob;
-struct foo* camkes_get_tls(void)
-{
-  return &glob;
-}
-_Noreturn void abort(void);
-
-static int a1;
-static int a2;
-static int *get(void) __attribute__((__unused__));
-static int *get(void) {
-  switch (camkes_get_tls()->thread_index) {
-  case 1:
-    return &a1;
-  case 2:
-    return &a2;
-  default:
-    (void)0;
-    abort();
-  }
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/jiraver456.c

@@ -1,29 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-struct div_t {
-  unsigned q;
-};
-
-unsigned f0(unsigned n, unsigned d)
-{
-  return n/d;
-}
-
-struct div_t f1(unsigned n, unsigned d)
-{
-  struct div_t r = { n / d };
-  return r;
-}
-
-struct div_t f2(unsigned n, unsigned d)
-{
-  return (struct div_t){n/d};
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/kmalloc.c

@@ -1,232 +1,0 @@
-/* this is a -*- c -*- file */
-/*
- * @TAG(OTHER_BSD)
- */
-
-/* ********************************************************************
- *
- * Copyright (C) 2002, 2003-2004,  Karlsruhe University
- *   Original authors
- *
- * Copyright (C) 2009-2012, NICTA
- *   Translation to C for verification experiments.
- *
- * Description:   very simple kernel memory allocator
- *
- * Redistribution and use in source and binary forms, with or without
- * modification, are permitted provided that the following conditions
- * are met:
- * 1. Redistributions of source code must retain the above copyright
- *    notice, this list of conditions and the following disclaimer.
- * 2. Redistributions in binary form must reproduce the above copyright
- *    notice, this list of conditions and the following disclaimer in the
- *    documentation and/or other materials provided with the distribution.
- *
- * THIS SOFTWARE IS PROVIDED BY THE AUTHOR AND CONTRIBUTORS ``AS IS'' AND
- * ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE
- * IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE
- * ARE DISCLAIMED.  IN NO EVENT SHALL THE AUTHOR OR CONTRIBUTORS BE LIABLE
- * FOR ANY DIRECT, INDIRECT, INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL
- * DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS
- * OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
- * HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT
- * LIABILITY, OR TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY
- * OUT OF THE USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF
- * SUCH DAMAGE.
- *
- ******************************************************************* */
-
-typedef unsigned int u64_t;
-typedef unsigned int u32_t;
-typedef unsigned short u16_t;
-typedef unsigned char u8_t;
-
-typedef signed int s64_t;
-typedef signed int s32_t;
-typedef signed short s16_t;
[…]

### 2019-10-18 l4v/src/tools/c-parser/testfiles/longlong.c

@@ -1,41 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int f(long long x)
-{
-  return x % (1 << 31);
-}
-
-int g(long long x)
-{
-  return (x == 0);
-}
-
-int callg(void)
-{
-  long long n = ~0u;
-  return g(n + 1);
-}
-
-long long shifts1(long long x, int i)
-{
-  return ((x << i) + (x >> i));
-}
-
-int shifts2(long long x, int i)
-{
-  return ((x << i) + (x >> i));
-}
-
-int literals(void)
-{
-  int x = 30LL;
-  return x + 1;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/many_local_vars.c

@@ -1,470 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int test(void) {
-    int var101 = 0;
-
-    /*
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    */
-
-    /*
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    */
-
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-    var101 = var101 + 1;
-}
-
-int blah2a(void) {
-int var101 = 0;
-int var102 = 0;
-int var103 = 0;
-int var104 = 0;
-int var105 = 0;
-int var106 = 0;
-int var107 = 0;
-int var108 = 0;
-int var109 = 0;
-int var110 = 0;
-int var111 = 0;
-int var112 = 0;
-int var113 = 0;
-int var114 = 0;
-int var115 = 0;
-int var116 = 0;
-int var117 = 0;
-int var118 = 0;
-int var119 = 0;
-int var120 = 0;
-int var121 = 0;
-int var122 = 0;
-int var123 = 0;
-int var124 = 0;
-int var125 = 0;
[…]

### 2019-10-18 l4v/src/tools/c-parser/testfiles/parse_auxupd.c

@@ -1,17 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int f(int x)
-{
-  for (int i = 0; i < 10; i++ /** AUXUPD: foo */) {
-    x = x + i;
-  }
-  return x;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/parse_include.c

@@ -1,27 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-#include "test_include2.h"
-/* above defines included_fn, and included_global */
-
-int g(int m)
-{
-  return m + included_global;
-}
-
-int h(char c)
-{
-  return included_fn(2 * c);
-}
-
-int included_fn(int param)
-{
-  return param * 3;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/parse_struct_array.c

@@ -1,77 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-#define MAX_SIZE 1024
-
-int globint1, globint2, globintarray[3];
-
-struct s {
-  int sz;
-  char data[MAX_SIZE];
-};
-
-struct s_dataptr {
-  int sz;
-  char *dataptr;
-};
-
-int f(struct s* ptr)
-{
-  return ptr ? 0 : ptr->sz;
-}
-
-struct t {
-  int x, y;
-};
-
-struct u {
-  struct t array[10];
-};
-
-struct k {
-  unsigned short b;
-  char c[1];
-};
-
-int g(struct u* uptr, int n, struct k *kptr)
-{
-  return uptr->array[n].x + (kptr ? kptr->b : 0);
-}
-
-struct u globu;
-struct k globk1, globk2, globkarray[10];
-
-int h(int *i)
-{
-  globk2.b++;
-  return *i + g(&globu, *i * 2, &globk1);
-}
-
-int h1(void)
-{
-  return g(&globu, 2, globkarray + 6);
-}
-
-int j(void)
-{
-  int i = h(&globint1), j = h(globintarray + 2);
-  return i + j;
-}
-
-int ts20110511_1(struct s *sptr, int i, int shift)
-{
-  return ((sptr->data[i]) >> shift);
-}
-
-int ts20110511_2(struct s *sptr, int shift)
-{
-  return ((sptr->sz) >> shift);
-}
-

### 2019-10-18 l4v/src/tools/c-parser/testfiles/parse_switch.c

@@ -1,70 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int f(int x, int y)
-{
-  switch (x) {
-  case 0:
-    x += y;
-    break;
-  case 1: case 2:
-    x -= y * 2;
-    return y;
-  default:
-    x -= y;
-  }
-  return x;
-}
-
-
-enum {foo = 101,bar};
-
-int g(int y)
-{
-  int x;
-  switch (y) {
-  case foo:
-    return f(y + 1, 0);
-  case bar:
-    x = y + 2;
-    break;
-  default:
-    x = 4;
-  }
-  return x * 2;
-}
-
-int h(int z)
-{
-  switch (z) {
-  case foo: case 2: default:
-    return 3;
-  case bar:
-    return 4;
-  }
-}
-
-int j(int z)
-{
-  switch (z) {
-  case 1: return 3;
-  case 2: return 4;
-  }
-  return 5;
-}
-
-int k(int z, int *array)
-{
-  switch (array[z]) {
-  case 0: return 3;
-  case 1: return 4;
-  default: return 5;
-  }
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/postfixOps.c

@@ -1,35 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-unsigned char uc;
-signed char sc;
-unsigned int ui;
-int si;
-unsigned long ul;
-long sl;
-
-signed char *retptr(void)
-{
-  return &sc;
-}
-
-void doit(void)
-{
-  uc++;
-  sc++;
-  ui++;
-  si++;
-  ul++;
-  sl++;
-  (*retptr())++;
-  sl--;
-  uc--;
-}
-

### 2019-10-18 l4v/src/tools/c-parser/testfiles/ptr_globals.c

@@ -1,13 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int x;
-
-int *ptr;

### 2019-10-18 l4v/src/tools/c-parser/testfiles/ptr_locals.c

@@ -1,21 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int x;
-
-int *ptr;
-
-int array[10];
-
-int *f(int **p)
-{
-  int *ptrarray[10];
-  return *p;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/selection_sort.c

@@ -1,46 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-unsigned len(unsigned *x)
-{
-  unsigned i;
-  for (i = 0; x[i]; i++);
-  return i;
-}
-
-/* lmin returns the index of the minimum element in the array, stopping when
-   the array element is zero (this one doesn't count) */
-unsigned lmin(unsigned *x)
-{
-  unsigned minsofar = x[0], mini = 0, i = 0;
-  while (x[i]) {
-    if (x[i] < minsofar) { minsofar = x[i]; mini = i; }
-    i++;
-  }
-  return mini;
-}
-
-unsigned* ssort(unsigned* x)
-{
-  unsigned sidx,i,t,lo;
-  unsigned ln;
-  unsigned mini;
-  ln = len(x);
-  if (ln < 2) return x;
-
-  for (sidx = 0 ; sidx < ln ; sidx++) {
-    mini = lmin(x + sidx);
-    lo = sidx + mini;
-    t = x[sidx];
-    x[sidx] = x[lo];
-    x[lo] = t;
-  }
-  return x;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/signed_div.c

@@ -1,30 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int f(int a, int b)
-{
-  return a / b;
-}
-
-int g(int a, int b)
-{
-  return a % b;
-}
-
-int h(unsigned int a, int b)
-{
-  return a / b;
-}
-
-char i(char a, char b)
-{
-  return a / b;
-}
-

### 2019-10-18 l4v/src/tools/c-parser/testfiles/sizeof_typedef.c

@@ -1,22 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-typedef struct s {
-  int x,y;
-  char c;
-} s;
-
-int f(void)
-{
-  unsigned char array[sizeof(s)];
-  struct s var1;
-  for (int i = 0; i < sizeof(s); i++) array[i] = 1;
-  return sizeof (s);
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/spec_annotated_voidfn.c

@@ -1,24 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int x;
-
-/* this spec is bogus, but at least it parses */
-
-/** FNSPEC
-     f_spec: "\<forall> \<sigma> n.
-               \<Gamma> \<turnstile> {\<sigma>} CALL f(n)
-                  \<lbrace> x_' (globals \<sigma>) + scast n = \<acute>x\<rbrace>"
-*/
-void f(char n)
-{
-  x = x + n;
-}
-

### 2019-10-18 l4v/src/tools/c-parser/testfiles/struct_ptr_fn.c

@@ -1,23 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-struct list {
-  int contents;
-  struct list *next;
-};
-
-int last(struct list *nodeptr)
-{
-  if (!nodeptr) { return 0; }
-  while (!nodeptr->next) {
-    nodeptr = nodeptr->next;
-  }
-  return nodeptr->contents;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/struct_ptr_globals.c

@@ -1,25 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-struct s {
-  int fld1;
-  int *fld2;
-  char x;
-};
-
-struct s svar;
-
-struct t {
-  int fld1;
-  struct t* next;
-};
-
-struct t tvar;
-

### 2019-10-18 l4v/src/tools/c-parser/testfiles/test_include.c

@@ -1,16 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-#include "test_include.h"
-
-int f(int x)
-{
-  return x + 3;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/test_include.h

@@ -1,12 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int f(int);
-int g(char, char *);

### 2019-10-18 l4v/src/tools/c-parser/testfiles/untouched_globals.c

@@ -1,26 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-int x, y = 1;
-
-struct s { char c; int array[4]; };
-
-struct s glob1, glob2 = { '3', 1,2 };
-
-int f(int n)
-{
-  y++;
-  return n + 1;
-}
-
-int g(int n)
-{
-  return n*n;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/variable_munge.c

@@ -1,53 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-unsigned int g(unsigned int x) { return x + 3; }
-
-int f(int * x) { return *x + 1; }
-
-int h(int x, int *y)
-{
-  return g(x) + f(y);
-}
-
-int j(int x)
-{
-  if (x > 4) {
-    char c = x + 1;
-    return c;
-  } else {
-    int c = x * 2;
-    return c;
-  }
-}
-
-unsigned long foo(unsigned int depth);
-
-int bar(unsigned long baz)
-{
-    unsigned long depth;
-    depth = bar(1);
-}
-
-struct b {
-    struct b *x;
-    int y;
-};
-
-int qux(int bbb)
-{
-    struct b *d, *baz;
-    for(baz = (struct b *) 0; baz; baz = d)
-    {
-        d = baz->x;
-    }
-    return 1;
-}
-

### 2019-10-18 l4v/src/tools/c-parser/testfiles/varinit.c

@@ -1,19 +1,0 @@
-/*
- * Copyright 2014, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-/* parsing test for local variable initialisation */
-
-int f(int n)
-{
-  int m = n + 3, j = 1;
-  unsigned i = 0;
-  while (n < m) { m = m + 1; n = n + 2; }
-  return m;
-}

### 2019-10-18 l4v/src/tools/c-parser/testfiles/void_ptr_init.c

@@ -1,21 +1,0 @@
-/*
- * Copyright 2015, NICTA
- *
- * This software may be distributed and modified according to the terms of
- * the BSD 2-Clause license. Note that NO WARRANTY is provided.
- * See "LICENSE_BSD2.txt" for details.
- *
- * @TAG(NICTA_BSD)
- */
-
-/*
- * Initialiser for void*; fixed in git-aa162a0.
- */
-
-struct A {
-  void *p;
-};
-
-void f(void) {
-  struct A a = { 0 };
-}

### 2019-10-18 l4v/src/tools/haskell-translator/braces.py

@@ -1,228 +1,0 @@
-#
-# Copyright 2014, NICTA
-#
-# This software may be distributed and modified according to the terms of
-# the BSD 2-Clause license. Note that NO WARRANTY is provided.
-# See "LICENSE_BSD2.txt" for details.
-#
-# @TAG(NICTA_BSD)
-#
-
-from __future__ import print_function
-
-
-class BracedString:
-    """A string split into components based on delimiters (usually braces).
-
-    When l occurs in the string, create a new component whose contents are
-    the rest of the string until the matching r.
-
-    When l = ( and r = ), this has the approximate behavior of splitting
-    the string into the components of a Haskell function application,
-    where each individual component, if not containing the delimiters, can
-    be split on white space to determine the arguments of the function.
-
-    This behaves exactly like a str, except for split, map, and
-    discard_enclosing_braces.
-
-    Invariant: a component either has no delimiters, or is surrounded by
-    delimiters.
-    """
-
-    def __init__(self, s, l, r, bits=None):
-        if bits is None:
-            bits = self._get_bits(s, l, r)
-        self.bits = bits
-        self.s = s
-        self.l = l
-        self.r = r
-
-    def _get_bits(self, s, l, r):
-        nesting_depth = 0
-        bits = ['']
-        for c in s:
-            if c == l:
-                if nesting_depth == 0:
-                    if bits[-1]:
-                        bits.append('')
-                nesting_depth = nesting_depth + 1
-            bits[-1] = bits[-1] + c
-            if c == r:
-                nesting_depth = nesting_depth - 1
-                if nesting_depth == 0:
-                    if bits[-1]:
-                        bits.append('')
-        if not bits[-1]:
-            bits.pop(-1)
-        return bits
-
-    def __str__(self):
-        return self.s
-
-    def __repr__(self):
-        check = BracedString(self.s, self.l, self.r)
-        if check.bits == self.bits:
-            return 'B%s%s: %r' % (self.l, self.r, self.s)
-        else:
-            return 'Broken Braced: %r, %r, %r' % (self.s, self.bits,
-                                                  check.bits)
-
-    def __add__(self, other):
-        if isinstance(other, BracedString):
-            if self.bits[-1].startswith(self.l):
-                bits = self.bits + other.bits
-            elif other.bits[0].startswith(self.l):
-                bits = self.bits + other.bits
-            else:
-                bits = self.bits[:-1] + \
-                    [self.bits[-1] + other.bits[0]] + \
-                    other.bits[1:]
[…]

### 2019-10-18 l4v/src/tools/haskell-translator/lhs_pars.py

@@ -1,2813 +1,0 @@
-#
-# Copyright 2014, NICTA
-#
-# This software may be distributed and modified according to the terms of
-# the BSD 2-Clause license. Note that NO WARRANTY is provided.
-# See "LICENSE_BSD2.txt" for details.
-#
-# @TAG(NICTA_BSD)
-#
-
-from __future__ import print_function
-from __future__ import absolute_import
-import braces
-import re
-import sys
-import os
-import six
-from six.moves import map
-from six.moves import range
-from six.moves import zip
-from functools import reduce
-
-
-class Call(object):
-
-    def __init__(self):
-        self.restr = None
-        self.decls_only = False
-        self.instanceproofs = False
-        self.bodies_only = False
-        self.bad_type_assignment = False
-        self.body = False
-        self.current_context = []
-
-
-class Def(object):
-
-    def __init__(self):
-        self.type = None
-        self.defined = None
-        self.body = None
-        self.line = None
-        self.sig = None
-        self.instance_proofs = []
-        self.instance_extras = []
-        self.comments = []
-        self.primrec = None
-        self.deriving = []
-        self.instance_defs = {}
-
-
-def parse(call):
-    """Parses a file."""
-    set_global(call)
-
-    defs = get_defs(call.filename)
-
-    lines = get_lines(defs, call)
-
-    lines = perform_module_redirects(lines, call)
-
-    return ['%s\n' % line for line in lines]
-
-def settings_line(l):
-    """Adjusts some global settings."""
-    bits = l.split (',')
-    for bit in bits:
-        bit = bit.strip ()
-        (kind, setting) = bit.split ('=')
-        kind = kind.strip ()
-        if kind == 'keep_constructor':
-            [cons] = setting.split ()
-            keep_conss[cons] = 1
-        else:
-            assert not "setting kind understood", bit
-
-def set_global(_call):
-    global call
-    call = _call
-    global filename
-    filename = _call.filename
-
-
-file_defs = {}
-
-
-def splitList(list, pred):
-    """Splits a list according to pred."""
-    result = []
-    el = []
-    for l in list:
-        if pred(l):
-            if el != []:
-                result.append(el)
-                el = []
-        else:
-            el.append(l)
-    if el != []:
-        result.append(el)
-    return result
-
-
-def takeWhile(list, pred):
-    """Returns the initial portion of the list where each
-element matches pred"""
-    limit = 0
-
-    for l in list:
-        if pred(l):
-            limit = limit + 1
-        else:
[…]

### 2019-10-18 l4v/src/tools/haskell-translator/make_spec.sh

@@ -1,157 +1,0 @@
-#!/bin/bash
-#
-# Copyright 2014, NICTA
-#
-# This software may be distributed and modified according to the terms of
-# the BSD 2-Clause license. Note that NO WARRANTY is provided.
-# See "LICENSE_BSD2.txt" for details.
-#
-# @TAG(NICTA_BSD)
-#
-
-set -e
-
-ORIG_PWD="$PWD"
-
-function find_dir () {
-    cd $ORIG_PWD
-    while [[ "/$PWD" != '//' ]]
-    do
-        if [[ -d "./$1" ]]
-        then
-            FOUND_PWD="$(pwd)/$1"
-            if [[ ! -z "$V" ]]
-            then echo "Found $FOUND_PWD" 1>&2
-            fi
-            echo "$FOUND_PWD"
-            return 0
-        fi
-        cd ..
-    done
-    echo "Could not find a directory containing $1" 1>&2
-    echo "  in any parent directory." 1>&2
-    exit 1
-}
-
-TRANSLATOR=$(find_dir "tools/haskell-translator")
-
-SPEC=$(find_dir "spec/design")
-
-if [[ -z $L4CAP ]]
-then
-    L4CAP=$(find_dir "spec/haskell")
-    export L4CAP
-fi
-
-if [[ ! -d $L4CAP/src/SEL4 ]]
-then
-    echo "This script is using L4CAP == $L4CAP"
-    echo Set the L4CAP environment variable to the location
-    echo of the haskell kernel source.
-    exit 1
-fi
-
-SKEL="$SPEC/skel"
-MSKEL="$SPEC/m-skel"
-
-MACH="$SPEC/../machine"
-
-if [[ ! -d $SKEL ]]
-then
-    echo Error: $SKEL is not a directory.
-    echo "(this script may have found the wrong spec $SPEC)"
-    exit
-fi
-
-# which architectures to process
-ARCHES=("ARM" "RISCV64" "X64" "ARM_HYP")
-
-# Match the CPP configuration used by SEL4.cabal and Setup.hs for Haskell build
-# Note: these should be in sync with both the Haskell .cabal and Setup.hs,
-#       If these are not in sync, expect the unexpected.
-#       spec_check.sh has a copy of these, which should be updated in tandem.
[…]

### 2019-10-21 C11-FrontEnd/document/generated/paper.tex
synchronize with fortesse revision 5377

@@
 \begin{isamarkupsection*}%
-[label = {background},type = {scholarly_paper.technical}, args={label = {background},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''bu''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Background: PIDE and the Isabelle Document Model%
+[label = {background},type = {scholarly_paper.technical}, args={label = {background},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Background: PIDE and the Isabelle Document Model%
 \end{isamarkupsection*}\isamarkuptrue%
@@
 \begin{isamarkupsection*}%
-[label = {frontend_arch},type = {scholarly_paper.technical}, args={label = {frontend_arch},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''bu''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]The C11 Parser Generation Process and Architecture%
+[label = {frontend_arch},type = {scholarly_paper.technical}, args={label = {frontend_arch},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]The C11 Parser Generation Process and Architecture%
 \end{isamarkupsection*}\isamarkuptrue%
@@
   experiments, files generated with a version $i$ of Isabelle natively work when loaded with a more
-  recent version $j$, for any versions $i$ and $j$ satisfying $2016 \leq i \leq j \leq 2019$ (at the
-  time of writing).}%
+  recent version $j$, for at least any versions $i$ and $j$ satisfying $2016 \leq i \leq j \leq
+  2019$ (at the time of writing).}%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkupsubsection*}%
-[label = {arch1},type = {scholarly_paper.technical}, args={label = {arch1},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''bu''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Generating the AST%
+[label = {arch1},type = {scholarly_paper.technical}, args={label = {arch1},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Generating the AST%
 \end{isamarkupsubsection*}\isamarkuptrue%
@@
 \begin{isamarkupsubsection*}%
-[label = {lexer},type = {scholarly_paper.technical}, args={label = {lexer},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Constructing a Lexer for C11%
+[label = {lexer},type = {scholarly_paper.technical}, args={label = {lexer},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Constructing a Lexer for C11%
 \end{isamarkupsubsection*}\isamarkuptrue%
@@
 \begin{isamarkupsubsection*}%
-[label = {parser},type = {scholarly_paper.technical}, args={label = {parser},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Generating the Shift-Reduce Parser from the Grammar%
+[label = {parser},type = {scholarly_paper.technical}, args={label = {parser},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Generating the Shift-Reduce Parser from the Grammar%
 \end{isamarkupsubsection*}\isamarkuptrue%
@@
 \begin{isamarkupsection*}%
-[label = {ctests},type = {scholarly_paper.technical}, args={label = {ctests},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Isabelle/C: Syntax Tests and Experimental Results%
+[label = {ctests},type = {scholarly_paper.technical}, args={label = {ctests},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Isabelle/C: Syntax Tests and Experimental Results%
 \end{isamarkupsection*}\isamarkuptrue%
@@
 \begin{isamarkupsection*}%
-[label = {annotations},type = {scholarly_paper.technical}, args={label = {annotations},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Generic Semantic Annotations for C%
+[label = {annotations},type = {scholarly_paper.technical}, args={label = {annotations},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Generic Semantic Annotations for C%
 \end{isamarkupsection*}\isamarkuptrue%
@@
 \begin{isamarkupsubsection*}%
-[label = {navigation},type = {scholarly_paper.technical}, args={label = {navigation},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''bu''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Navigation for Annotation Commands%
+[label = {navigation},type = {scholarly_paper.technical}, args={label = {navigation},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Navigation for Annotation Commands%
 \end{isamarkupsubsection*}\isamarkuptrue%
@@
 \begin{isamarkupsubsection*}%
-[label = {annot1},type = {scholarly_paper.technical}, args={label = {annot1},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Defining Annotation Commands%
+[label = {annot1},type = {scholarly_paper.technical}, args={label = {annot1},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Defining Annotation Commands%
 \end{isamarkupsubsection*}\isamarkuptrue%
@@
   threads). Such information is ``encoded in its kind''; such as \isa{thy{\isacharunderscore}decl},
-  \isa{thy{\isacharunderscore}load}, \isa{thy{\isacharunderscore}defn}, etc., for example: $K_\text{\emph{cmd}} =
-  \isa{\isacommand{definition}\ {\isacharcolon}{\isacharcolon}\ thy{\isacharunderscore}defn} \isatt{|}
-  \isa{\isacommand{lemma}\ {\isacharcolon}{\isacharcolon}\ thy{\isacharunderscore}goal{\isacharunderscore}stmt} \isatt{|} \dots $}
+  \isa{thy{\isacharunderscore}load}, \isa{thy{\isacharunderscore}defn}, etc., for example we should have defined
+  $K_\text{\emph{cmd}}$ as : $K_\text{\emph{cmd}} = \isa{\isacommand{definition}\ {\isacharcolon}{\isacharcolon}\ thy{\isacharunderscore}defn} \isatt{|} \isa{\isacommand{lemma}\ {\isacharcolon}{\isacharcolon}\ thy{\isacharunderscore}goal{\isacharunderscore}stmt}
+  \isatt{|} \dots $}
 
@@
 \begin{isamarkupsubsection*}%
-[label = {annot2},type = {scholarly_paper.technical}, args={label = {annot2},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Evaluation Order%
+[label = {annot2},type = {scholarly_paper.technical}, args={label = {annot2},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Evaluation Order%
 \end{isamarkupsubsection*}\isamarkuptrue%
@@
 \begin{isamarkupsection*}%
-[label = {backends},type = {scholarly_paper.technical}, args={label = {backends},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''bu''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Semantic Back-Ends%
+[label = {backends},type = {scholarly_paper.technical}, args={label = {backends},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Semantic Back-Ends%
 \end{isamarkupsection*}\isamarkuptrue%
@@
 In this section, we briefly present two integrations of verification back-ends for C. We
-chose Clean \cite{journals/afp/TuongW19}~\footnote{stemming from recent HOL-TestGen distributions
+chose Clean \cite{journals/afp/TuongW19}~\footnote{Stemming from recent HOL-TestGen distributions:
     \url{https://www.brucker.ch/projects/hol-testgen/index.en.html}} used
@@
 \begin{isamarkupsubsection*}%
-[label = {clean},type = {scholarly_paper.technical}, args={label = {clean},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''bu''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]A Simple Typed Memory Model: Clean%
+[label = {clean},type = {scholarly_paper.technical}, args={label = {clean},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]A Simple Typed Memory Model: Clean%
 \end{isamarkupsubsection*}\isamarkuptrue%
@@
 \begin{isamarkupsubsection*}%
-[label = {autocorres},type = {scholarly_paper.technical}, args={label = {autocorres},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]The Case of AutoCorres%
+[label = {autocorres},type = {scholarly_paper.technical}, args={label = {autocorres},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]The Case of AutoCorres%
 \end{isamarkupsubsection*}\isamarkuptrue%
@@
 \begin{isamarkupsubsection*}%
-[label = {securify},type = {scholarly_paper.technical}, args={label = {securify},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Yet another C-Back-End: Securify%
+[label = {securify},type = {scholarly_paper.technical}, args={label = {securify},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Yet Another C Back-End: Securify%
 \end{isamarkupsubsection*}\isamarkuptrue%
@@
 \begin{isamarkuptext}%
-In the Securify project at the Nanyang Technological University \cite{DBLP:conf/tacas/SananZHZTL17,DBLP:conf/itp/HouSTL17}, an extension of AutoCorres is in
+In the Securify project at the Nanyang Technological University \cite{DBLP:conf/tacas/SananZHZTL17,DBLP:conf/itp/HouSTL17}, an extension of L4.verified is in
 active development which attempts to integrate concurrency and some form of non-coherent memory into
-the verification framework. This ongoing project is already profiting from the overall framework,
-including the integrated parser $\text{PARSE}_{\text{\emph{report}}}^{\text{C11}}$. Note, however,
-that the XtratuM micro-kernel \cite{DBLP:journals/sigbed/CarrascosaCMBC14} in study is using
-certain advance features of C11 not found in seL4 (including nested functions, or particular
+the verification framework. This ongoing project is already profiting from the overall Isabelle/C
+framework, including the integrated parser $\text{PARSE}_{\text{\emph{report}}}^{\text{C11}}$. Note,
+however, that the XtratuM micro-kernel \cite{DBLP:journals/sigbed/CarrascosaCMBC14} in study is
+using certain advance features of C11 not found in seL4 (including nested functions, or particular
 arrangement of assembly code). The project is actively working on developing dedicated semantic
@@
 \begin{isamarkupsection*}%
-[label = {concl},type = {scholarly_paper.conclusion}, args={label = {concl},type = {scholarly_paper.conclusion}, scholarly_paper.text_section.main_author = {@{docitem ''bu''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}}]Conclusions%
+[label = {concl},type = {scholarly_paper.conclusion}, args={label = {concl},type = {scholarly_paper.conclusion}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.text_section.main_author = {}}]Conclusions%
 \end{isamarkupsection*}\isamarkuptrue%
@@
 \begin{isamarkupsection*}%
-[label = {appendix},type = {scholarly_paper.technical}, args={label = {appendix},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Appendix%
+[label = {appendix},type = {scholarly_paper.technical}, args={label = {appendix},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Appendix%
 \end{isamarkupsection*}\isamarkuptrue%
@@
   parsed source to carry additional position information in all its parsing nodes. Ultimately, the
-  two ASTs was merged together while releasing version 1.18.0.} Upgrading Haskabelle to use
-the new 1.18.0 was the most heavy task we performed, when integrating Haskabelle's output with
-Citadelle's input. Otherwise, we have not encountered any problems in upgrading Haskabelle from
-1.18.0 to more recent versions (such as 1.20.1 which was straightforward).%
+  two ASTs was merged together while releasing version 1.18.0.} Consequently, upgrading
+Haskabelle to use the new 1.18.0 represents an entire challenge. Hopefully, it is a task we already
+completed while integrating Haskabelle's output with Citadelle's input. Otherwise, we have not
+encountered any problems in upgrading Haskabelle from 1.18.0 to more recent versions (such as 1.20.1
+which was straightforward).%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \isa{\isacommand{datatype}}, in particular to gain 10~min on the shallow-reflected
-evaluation side (with the option \isa{quick{\isacharminus}and{\isacharminus}dirty} activated). This is the purpose of
-the general \isa{\isacommand{Haskell{\isacharunderscore}file}} command implemented in Citadelle:~\footnote{Note that \isa{\isacommand{old{\isacharunderscore}datatype}} is a command, whereas
-  \isa{\isakeyword{datatype{\isacharunderscore}old}} is an option provided to the command
+evaluation side (with the option \isa{quick{\isacharminus}and{\isacharminus}dirty} activated). In a nutshell, our new
+implemented \isa{\isacommand{Haskell{\isacharunderscore}file}} command accepts other various
+options:~\footnote{Note that \isa{\isacommand{old{\isacharunderscore}datatype}} is a command,
+  whereas \isa{\isakeyword{datatype{\isacharunderscore}old}} is an option provided to the command
   \isa{\isacommand{Haskell{\isacharunderscore}file}}.}
@@
 The advantage of this construction is the possibility to do immediate code value transformations
-obtained from Haskabelle.
-
-Operationally, \isa{\isacommand{Haskell{\isacharunderscore}file}} makes an implicit call to Haskabelle,
-translates the Haskell's output of Haskabelle to an acceptable HOL input, and lets the Citadelle
-framework execute generated theorems and proofs in native concurrent speed, based on a version of
-Isabelle specially modified for the purpose.\footnote{The use of a modified Isabelle is very
-  optional: Citadelle can also run with the standard Isabelle version, while being in the process of
-  submitting to Isabelle AFP for example.} On the one hand, the measure performance of the
-\isa{\isacommand{datatype}} package is not improving when being generated and executed by
-our Citadelle infrastructure, because the blocking expensive point remains located on
+obtained from Haskabelle: operationally, \isa{\isacommand{Haskell{\isacharunderscore}file}} makes an
+implicit call to Haskabelle, translates the Haskell's output of Haskabelle to an acceptable HOL
+input, and lets the Citadelle framework execute generated theorems and proofs in native concurrent
+speed, based on a version of Isabelle specially modified for the purpose.\footnote{The use
+  of a modified Isabelle is just optional: the whole Citadelle framework can also be configured to
+  run with the standard version of Isabelle, i.e., at run-time the difference only relies on the
+  performance treatment of consecutive commands.} On the one hand, the measure performance
+of the \isa{\isacommand{datatype}} package is not improving when being generated and
+executed by our Citadelle infrastructure, because the blocking expensive point remains located on
 \emph{one} problematic mutually recursive \isa{\isacommand{datatype}}
@@
 \begin{isamarkupsubsection*}%
-[label = {forest},type = {scholarly_paper.technical}, args={label = {forest},type = {scholarly_paper.technical}, scholarly_paper.text_section.main_author = {@{docitem ''fred''}}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Shift-Reduce forest of a parsing execution%
+[label = {forest},type = {scholarly_paper.technical}, args={label = {forest},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Shift-Reduce forest of a parsing execution%
 \end{isamarkupsubsection*}\isamarkuptrue%

### 2019-10-22 C11-FrontEnd/document/generated/paper.tex
added ref to FIDE paper

@@
   (known) semantic back-ends in order to validate the design decisions for our
-  back-end interface.%
+  back-end interface.
+
+  \textbf{In case that you consider citing Isabelle/C, please refer to \cite{Tuong-IsabelleC:2019}.  } %
 \end{isamarkuptext*}\isamarkuptrue%

### 2019-10-22 C11-FrontEnd/document/generated/paper.tex
synchronize with fortesse

@@
 
-  \textbf{In case that you consider citing Isabelle/C, please refer to \cite{Tuong-IsabelleC:2019}.  } %
+  \textbf{In case that you consider to cite this work, please refer to \cite{Tuong-IsabelleC:2019}.}%
 \end{isamarkuptext*}\isamarkuptrue%
@@
 \begin{isamarkupfigure*}%
-[label = {hyplinkout},type = {Isa_COL.figure}, args={label = {hyplinkout},type = {Isa_COL.figure}, Isa_COL.figure.relative_width = {40}, Isa_COL.figure.src = {figures/markup-demo}, Isa_COL.figure.spawn_columns = {True}}]Output window showing the evaluation result of \autoref{fig:ml-pos} (clicking on the hyperlink $\protect\house$ makes the cursor jump to the \isatt{@{\char`\{}here{\char`\}}} of \autoref{fig:ml-pos})%
+[label = {hyplinkout},type = {Isa_COL.figure}, args={label = {hyplinkout},type = {Isa_COL.figure}, Isa_COL.figure.relative_width = {40}, Isa_COL.figure.src = {figures/markup-demo}, Isa_COL.figure.spawn_columns = {True}}]Output window showing the evaluation result of \autoref{fig:ml-pos} (the anchor of this hyperlink
+ $\protect\house$ targets at the position marked by \isatt{@{\char`\{}here{\char`\}}})%
 \end{isamarkupfigure*}\isamarkuptrue%
@@
 \begin{isamarkupsubsection*}%
-[label = {lexer_ex},type = {scholarly_paper.technical}, args={label = {lexer_ex},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Preprocessing Lexical Conventions: Comments and Backslash Newlines%
+[label = {lexer_ex},type = {scholarly_paper.technical}, args={label = {lexer_ex},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Preprocessing Lexical Conventions: Comments and Newlines%
 \end{isamarkupsubsection*}\isamarkuptrue%
@@
   \isa{thy{\isacharunderscore}load}, \isa{thy{\isacharunderscore}defn}, etc., for example we should have defined
-  $K_\text{\emph{cmd}}$ as : $K_\text{\emph{cmd}} = \isa{\isacommand{definition}\ {\isacharcolon}{\isacharcolon}\ thy{\isacharunderscore}defn} \isatt{|} \isa{\isacommand{lemma}\ {\isacharcolon}{\isacharcolon}\ thy{\isacharunderscore}goal{\isacharunderscore}stmt}
+  $K_\text{\emph{cmd}}$ as: $K_\text{\emph{cmd}} = \isa{\isacommand{definition}\ {\isacharcolon}{\isacharcolon}\ thy{\isacharunderscore}defn} \isatt{|} \isa{\isacommand{lemma}\ {\isacharcolon}{\isacharcolon}\ thy{\isacharunderscore}goal{\isacharunderscore}stmt}
   \isatt{|} \dots $}
@@
   \end{minipage}
-  \caption{Activating the Isabelle/C/Clean back-end triggers the generation of theorems}
+  \caption{Activating the Isabelle/C/Clean back-end \\ 
+           triggers the generation of theorems}
   \label{fig:clean}
@@
 \end{minipage}
-  \caption{Isabelle/C/AutoCorres: integrating an HOL correctness proof near its C code}
+  \caption{Isabelle/C/AutoCorres: integrating an HOL correctness \\
+           proof as annotation \emph{inside} C code}
   \label{fig:autocorres-c}
@@
 %
-\isamarkupsubsection{A Gentle Zoom on Citadelle's Generator%
+\isamarkupsubsection{A Zoom on Citadelle's HOL Generator%
 }
@@
 \begin{isamarkuptext}%
-In more details, combining Haskabelle and Citadelle is almost direct, as Haskabelle's
-output AST and Citadelle's input AST are already both subsets models of a rich Isar/HOL interface,
+In the generation process of the parsers for Isabelle/C, the Citadelle 
+system~\cite{DBLP:journals/afp/TuongW15} plays a vital role. In particular, it is used to 
+convert Haskell AST presentations into HOL AST presentations through an initial call to 
+Haskabelle. However, the resulting output can be run natively in order to increase efficiency
+via Citadelle.
+
+In more detail, combining Haskabelle and Citadelle is almost direct, as Haskabelle's
+output AST and Citadelle's input AST are already both subset models of a rich Isar/HOL interface,
 defined in past works~\cite{DBLP:journals/afp/TuongW15}. Note that one can configure Citadelle
-for it to generate $\text{AST}^\text{C11}_{\text{HOL}}$ using
-\isa{\isacommand{old{\isacharunderscore}datatype}} commands instead of
-\isa{\isacommand{datatype}}, in particular to gain 10~min on the shallow-reflected
-evaluation side (with the option \isa{quick{\isacharminus}and{\isacharminus}dirty} activated). In a nutshell, our new
-implemented \isa{\isacommand{Haskell{\isacharunderscore}file}} command accepts other various
+to generate $\text{AST}^\text{C11}_{\text{HOL}}$ using \isa{\isacommand{old{\isacharunderscore}datatype}} commands instead of 
+\isa{\isacommand{datatype}}. This results in a gain of 10~min on the shallow-reflected evaluation with the option 
+\isa{quick{\isacharminus}and{\isacharminus}dirty} activated.
+
+In the following, we show how we proceed: 
+we implemented a command \isa{\isacommand{Haskell{\isacharunderscore}file}} that accepts  various
 options:~\footnote{Note that \isa{\isacommand{old{\isacharunderscore}datatype}} is a command,
@@
 
-The advantage of this construction is the possibility to do immediate code value transformations
+This construction has the advantage to allow immediate code value transformations
 obtained from Haskabelle: operationally, \isa{\isacommand{Haskell{\isacharunderscore}file}} makes an
-implicit call to Haskabelle, translates the Haskell's output of Haskabelle to an acceptable HOL
-input, and lets the Citadelle framework execute generated theorems and proofs in native concurrent
-speed, based on a version of Isabelle specially modified for the purpose.\footnote{The use
-  of a modified Isabelle is just optional: the whole Citadelle framework can also be configured to
-  run with the standard version of Isabelle, i.e., at run-time the difference only relies on the
-  performance treatment of consecutive commands.} On the one hand, the measure performance
-of the \isa{\isacommand{datatype}} package is not improving when being generated and
-executed by our Citadelle infrastructure, because the blocking expensive point remains located on
+implicit call to Haskabelle, translates the output of Haskabelle to HOL
+input, and lets the Citadelle framework execute the generated theorems and proofs in parallel.
+For the latter, we use an Isabelle version that has been especially modified for this purpose.
+\footnote{The use of a modified Isabelle is just an optimization: the whole Citadelle framework can 
+also be configured to run on a standard Isabelle version, albeit with a significantly higher
+execution time.}
+
+ On the one hand, the execution of the AST mostly consisting of  \isa{\isacommand{datatype}} commands
+ is not improving when being generated and
+executed by our Citadelle infrastructure, because the blocking point is located in just
 \emph{one} problematic mutually recursive \isa{\isacommand{datatype}}
-command (which is not interacting with other commands). On the other hand, the question
-of: \begin{quote}\emph{``How fast that specific \isa{\isacommand{datatype}}
-  command would perform if from the 20 mutually recursive sub-definitions it were instead generating
-  20 or several (sub-)commands to be executed in native concurrent speed?''}\end{quote} is
-  actually opening an interesting topic of future experiments.%
+command (which is not interacting with other commands). 
+On the other hand, the question of advanced parallelisation techniques in the  \isa{\isacommand{datatype}}
+package is actually opening an interesting topic of future experiments. 
+The Citadelle infrastructure offers a number of mechanisms to address this task.%
 \end{isamarkuptext}\isamarkuptrue%
@@
 \begin{isamarkupsubsection*}%
-[label = {forest},type = {scholarly_paper.technical}, args={label = {forest},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Shift-Reduce forest of a parsing execution%
+[label = {forest},type = {scholarly_paper.technical}, args={label = {forest},type = {scholarly_paper.technical}, Isa_COL.text_element.level = {}, Isa_COL.text_element.referentiable = {False}, Isa_COL.text_element.variants = {{STR ''outline'', STR ''document''}}, scholarly_paper.text_section.main_author = {}, scholarly_paper.text_section.fixme_list = {}, Isa_COL.text_element.level = {}, scholarly_paper.technical.definition_list = {}}]Shift-Reduce Forest of a Parsing Execution%
 \end{isamarkupsubsection*}\isamarkuptrue%

### 2019-10-29 C11-BackEnds/Clean_wrapper/document/root.tex
added another example and a first shot for doc generation of Isabelle/C/Clean

--- 2019-09-17 C11-BackEnds/Clean/document/root.tex
@@
 
-\title{Clean - An Abstract Imperative Programming Language and its Theory}
+\title{Isabelle/C/Clean - A Show-Case for a Semantic Back-End for Isabelle/C}
 \author{%
@@
   \and
-  \href{https://www.lri.fr/~wolff/}{Burkhart Wolff} \\
-  \and
-  (with Contributions of \href{https://www.lri.fr/~keller/}{Chantal Keller})}
+  \href{https://www.lri.fr/~wolff/}{Burkhart Wolff}}
 \publishers{%
@@
 \begin{abstract}
-Clean is based on a simple, abstract execution model for an imperative target language. ``Abstract''
-is understood as contrast to ``Concrete Semantics''; alternatively, the term ``shallow-style
-embedding'' could be used. It strives for a type-safe notation of program-variables, an incremental
-construction of the typed state-space, support of incremental verification, and 
-open-world extensibility of new type definitions being intertwined with the program
-definition.
+Isabelle/C ~\cite{TuongWolff19} is a C11 ~front-end for Isabelle/PIDE providing 
+generic support for C parsing, editing, and highlighting. Isabelle/C also provides 
+a generic interface for semantic interpretations of the C11 programs and program
+fragments. In particular, Isabelle/C also offers the generic framework
+to define \emph{annotation commands} and \emph{C antiquotations} 
+that can be custumized to a specific semantic back-end.
 
-Clean is based on a ``no-frills'' state-exception monad with the usual definitions of \isa{bind} and
-\isa{unit} for the compositional glue of state-based computations. Clean offers conditionals and
-loops supporting C-like control-flow operators such as \isa{break} and \isa{return}. The state-space
-construction is based on the extensible record package. Direct recursion of procedures is supported.
+Clean is such a semantic back-end, i.e. an Isabelle theory providing a
+semantics and execution model. Clean is an abstract, ``shallow-style embedding''  
+for an imperative core language. It strives for a type-safe notation of 
+program-variables, an incremental construction of the typed state-space, 
+support of incremental verification, and  open-world extensibility of new 
+type definitions being intertwined with the program definitions.
 
-Clean's design strives for extreme simplicity. It is geared towards symbolic execution and proven
-correct verification tools. The underlying libraries of this package, however, deliberately restrict
-themselves to the most elementary infrastructure for these tasks. The package is intended to serve
-as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, or for the test-generation
-technique described in~\cite{DBLP:conf/tap/Keller18}.
+Clean is based on a ``no-frills'' state-exception monad with the usual definitions 
+of \isa{bind} and \isa{unit} for the compositional glue of state-based computations. 
+Clean offers conditionals and loops supporting C-like control-flow operators such 
+as \isa{break} and \isa{return}. The state-space construction is based on the 
+extensible record package. Direct recursion of C-functions is supported.
+
+The current session instantiates Isabelle/C with Clean and produces the 
+Isabelle/C/Clean instance. It is conceived as a demonstrator for creating
+other instances of Isabelle/C with other semantic backends such as AutoCorres
+~\cite{DBLP:conf/pldi/GreenawayLAK14},
+IMP2~\cite{DBLP:journals/afp/LammichW19} or Orca~\cite{bockenek:hal-02069705}.
 \end{abstract}
@@
 \newpage
+
+%\newpage
+%\chapter{Appendix : Used Monad Libraries}
+\input{Backend.tex}				
 \input{Clean.tex}				
-
-\input{Quicksort_concept.tex}
-\input{SquareRoot_concept.tex}
-
-\newpage
-\chapter{Appendix : Used Monad Libraries}
-\input{MonadSE.tex}
-\input{Seq_MonadSE.tex}
-\input{Symbex_MonadSE.tex}
-\input{Hoare_MonadSE.tex}
-\input{Hoare_Clean.tex}
+\input{Core.tex}				
+\input{Generator_dynamic_sequential.tex}	
+\input{Init.tex}				
+\input{Isabelle_code_runtime.tex}
+%\input{Isabelle_typedecl.tex}
+%\input{Meta_C.tex}
 

### 2019-10-30 C11-BackEnds/Clean/document/root.tex
Global Restructuring and Document Adaption

@@
   \and
-  (with Contributions of \href{https://www.lri.fr/~keller/}{Chantal Keller})}
+  (with Contributions by \href{https://www.lri.fr/~keller/}{Chantal Keller})}
 \publishers{%
@@
 open-world extensibility of new type definitions being intertwined with the program
-definition.
+definitions.
 
@@
 as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, or for the test-generation
-technique described in~\cite{DBLP:conf/tap/Keller18}.
+techniques described in~\cite{DBLP:conf/tap/Keller18}.
 \end{abstract}
@@
 \input{Clean.tex}
-
 \input{Quicksort_concept.tex}
 \input{SquareRoot_concept.tex}
+\input{LinearSearch}
 
@@
 \input{Symbex_MonadSE.tex}
+\input{Clean_Symbex.tex}
+\input{Test_Clean.tex}
 \input{Hoare_MonadSE.tex}

### 2019-10-30 C11-BackEnds/Clean_wrapper/document/root.tex
generates .pdf with restrictions.

@@
 \usepackage{listings}
-\usepackage{lstisadof}
 \IfFileExists{railsetup.sty}{\usepackage{railsetup}}{}
+
+\newcommand\inputif[1]{\IfFileExists{./#1}{\input{#1}}{}}
 
@@
 {\ifthenelse{\equal{}{#1}}{\index{#3 (#2)|bold}}{\index{#3 (#1\ #2)|bold}}} % from 'isar.sty'
-\newcommand{\isactrlC}{{\bf C}}
+\newcommand{\isactrlC}{{\isacommand C}}
+\newcommand{\isactrlMLPRIME}{{\isacommand MLPRIME}}
 
@@
 \begin{abstract}
-Isabelle/C ~\cite{TuongWolff19} is a C11 ~front-end for Isabelle/PIDE providing 
-generic support for C parsing, editing, and highlighting. Isabelle/C also provides 
-a generic interface for semantic interpretations of the C11 programs and program
-fragments. In particular, Isabelle/C also offers the generic framework
-to define \emph{annotation commands} and \emph{C antiquotations} 
-that can be custumized to a specific semantic back-end.
+Isabelle/C~\cite{TuongWolff19} is a C front-end for Isabelle/PIDE providing
+generic support for C parsing, editing, and highlighting. Isabelle/C also
+provides a generic interface for semantic interpretations of C11 programs and
+program fragments. In particular, Isabelle/C also offers the generic framework
+to define \emph{annotation commands} and \emph{C antiquotations} that can be
+custumized to a specific semantic back-end.
 
 Clean is such a semantic back-end, i.e. an Isabelle theory providing a
-semantics and execution model. Clean is an abstract, ``shallow-style embedding''  
-for an imperative core language. It strives for a type-safe notation of 
-program-variables, an incremental construction of the typed state-space, 
-support of incremental verification, and  open-world extensibility of new 
-type definitions being intertwined with the program definitions.
+semantics and execution model. Clean is an abstract, ``shallow-style
+embedding'' for an imperative core language. It strives for a type-safe
+notation of program-variables, an incremental construction of the typed
+state-space, support of incremental verification, and open-world extensibility
+of new type definitions being intertwined with the program definitions.
 
-Clean is based on a ``no-frills'' state-exception monad with the usual definitions 
-of \isa{bind} and \isa{unit} for the compositional glue of state-based computations. 
-Clean offers conditionals and loops supporting C-like control-flow operators such 
-as \isa{break} and \isa{return}. The state-space construction is based on the 
-extensible record package. Direct recursion of C-functions is supported.
+Clean is based on a ``no-frills'' state-exception monad with the usual
+definitions of \isa{bind} and \isa{unit} for the compositional glue of
+state-based computations.  Clean offers conditionals and loops supporting
+C-like control-flow operators such as \isa{break} and \isa{return}. The
+state-space construction is based on the extensible record package. Direct
+recursion of C-functions is supported.
 
 The current session instantiates Isabelle/C with Clean and produces the
-Isabelle/C/Clean instance. It is conceived as a demonstrator for creating
-other instances of Isabelle/C with other semantic backends such as AutoCorres
-~\cite{DBLP:conf/pldi/GreenawayLAK14},
+Isabelle/C/Clean instance. It is conceived as a demonstrator for creating other
+instances of Isabelle/C with other semantic backends such as
+AutoCorres~\cite{DBLP:conf/pldi/GreenawayLAK14},
 IMP2~\cite{DBLP:journals/afp/LammichW19} or Orca~\cite{bockenek:hal-02069705}.
@@
 \newpage
+\inputif{1/document/Init.tex}
+%\inputif{1/document/Meta_C.tex}
+\inputif{1/document/Core.tex}
+%\inputif{1/document/Isabelle_code_runtime.tex}
+%\inputif{1/document/Isabelle_typedecl.tex}
+%\inputif{1/document/Generator_dynamic_sequential.tex}
+\inputif{1/document/Backend.tex}
+
+%\inputif{2/document/IsPrime_sqrt_outside.tex}
+%\inputif{2/document/Clean_backend_old.tex}
+\inputif{2/document/Prime.tex}
+\inputif{2/document/Quicksort2.tex}
+\inputif{2/document/Quicksort.tex}
 
 %\newpage
-%\chapter{Appendix : Used Monad Libraries}
-\input{Backend.tex}				
-\input{Clean.tex}				
-\input{Core.tex}				
-\input{Generator_dynamic_sequential.tex}	
-\input{Init.tex}				
-\input{Isabelle_code_runtime.tex}
-%\input{Isabelle_typedecl.tex}
-%\input{Meta_C.tex}
+%\chapter{Appendix}
 

### 2019-10-30 C11-BackEnds/Clean_wrapper/document/root.tex
improved the doc structure
build
clean
permute some paragraphs
document
synchronize root.bib

@@
 \newcommand{\isactrlC}{{\isacommand C}}
-\newcommand{\isactrlMLPRIME}{{\isacommand MLPRIME}}
+\newcommand{\isactrlmkUNDERSCOREstring}{\isakeywordcontrol{mk{\isacharunderscore}string}}
+\newcommand{\isactrlMLPRIME}{{\isacommand ML{\isacharprime}}}
 
@@
 \begin{abstract}
-Isabelle/C~\cite{TuongWolff19} is a C front-end for Isabelle/PIDE providing
-generic support for C parsing, editing, and highlighting. Isabelle/C also
-provides a generic interface for semantic interpretations of C11 programs and
-program fragments. In particular, Isabelle/C also offers the generic framework
-to define \emph{annotation commands} and \emph{C antiquotations} that can be
-custumized to a specific semantic back-end.
+Isabelle/C~\cite{Tuong-IsabelleC:2019} is a C front-end for Isabelle/PIDE
+providing generic support for C parsing, editing, and highlighting. Isabelle/C
+also provides a generic interface for semantic interpretations of C11 programs
+and program fragments. In particular, Isabelle/C also offers the generic
+framework to define \emph{annotation commands} and \emph{C antiquotations} that
+can be custumized to a specific semantic back-end.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \input{session}
-\newpage
+
+\inputif{1/document/Clean_Wrapper.tex}
+
+\inputif{2/document/Prime.tex}
+\inputif{2/document/IsPrime_sqrt_outside.tex}
+\inputif{2/document/Quicksort.tex}
+\inputif{2/document/Quicksort2.tex}
+
 \inputif{1/document/Init.tex}
-%\inputif{1/document/Meta_C.tex}
+\inputif{1/document/Meta_C.tex}
 \inputif{1/document/Core.tex}
-%\inputif{1/document/Isabelle_code_runtime.tex}
-%\inputif{1/document/Isabelle_typedecl.tex}
-%\inputif{1/document/Generator_dynamic_sequential.tex}
-\inputif{1/document/Backend.tex}
-
-%\inputif{2/document/IsPrime_sqrt_outside.tex}
-%\inputif{2/document/Clean_backend_old.tex}
-\inputif{2/document/Prime.tex}
-\inputif{2/document/Quicksort2.tex}
-\inputif{2/document/Quicksort.tex}
-
-%\newpage
-%\chapter{Appendix}
+\chapter{Appendix: Miscellaneous (Interface to ``typedecl'')}
+\inputif{1/document/Isabelle_code_runtime.tex}
+\chapter{Appendix: Miscellaneous (Overloading ``code\_reflect'')}
+\inputif{1/document/Isabelle_typedecl.tex}
+\inputif{1/document/Generator_dynamic_sequential.tex}
+\inputif{2/document/Clean_backend_old.tex}
 

### 2019-10-30 C11-BackEnds/AutoCorres_wrapper/document/root.tex
build

--- 2019-10-30 C11-BackEnds/Clean_wrapper/document/root.tex
@@
 \newcommand{\isactrlC}{{\isacommand C}}
-\newcommand{\isactrlmkUNDERSCOREstring}{\isakeywordcontrol{mk{\isacharunderscore}string}}
-\newcommand{\isactrlMLPRIME}{{\isacommand ML{\isacharprime}}}
 
@@
 
-\title{Isabelle/C/Clean - A Show-Case for a Semantic Back-End for Isabelle/C}
+\title{Isabelle/C/AutoCorres - A Show-Case for a Semantic Back-End for Isabelle/C}
 \author{%
@@
 
-Clean is such a semantic back-end, i.e. an Isabelle theory providing a
-semantics and execution model. Clean is an abstract, ``shallow-style
-embedding'' for an imperative core language. It strives for a type-safe
-notation of program-variables, an incremental construction of the typed
-state-space, support of incremental verification, and open-world extensibility
-of new type definitions being intertwined with the program definitions.
-
-Clean is based on a ``no-frills'' state-exception monad with the usual
-definitions of \isa{bind} and \isa{unit} for the compositional glue of
-state-based computations.  Clean offers conditionals and loops supporting
-C-like control-flow operators such as \isa{break} and \isa{return}. The
-state-space construction is based on the extensible record package. Direct
-recursion of C-functions is supported.
-
-The current session instantiates Isabelle/C with Clean and produces the
-Isabelle/C/Clean instance. It is conceived as a demonstrator for creating other
+The current session instantiates Isabelle/C with AutoCorres and produces the
+Isabelle/C/AutoCorres instance. It is conceived as a demonstrator for creating other
 instances of Isabelle/C with other semantic backends such as
-AutoCorres~\cite{DBLP:conf/pldi/GreenawayLAK14},
+Clean~\cite{journals/afp/TuongW19},
 IMP2~\cite{DBLP:journals/afp/LammichW19} or Orca~\cite{bockenek:hal-02069705}.
@@
 
-\inputif{1/document/Clean_Wrapper.tex}
+\inputif{1/document/README.tex}
+\inputif{1/document/AutoCorres_Wrapper.tex}
 
-\inputif{2/document/Prime.tex}
+\inputif{2/document/IsPrime_integrated.tex}
+\inputif{2/document/IsPrime_linear_outside.tex}
 \inputif{2/document/IsPrime_sqrt_outside.tex}
+\inputif{2/document/IsPrime_sqrt_opt_outside.tex}
+\inputif{2/document/Parse_for_loop.tex}
 \inputif{2/document/Quicksort.tex}
-\inputif{2/document/Quicksort2.tex}
-
-\inputif{1/document/Init.tex}
-\inputif{1/document/Meta_C.tex}
-\inputif{1/document/Core.tex}
-\chapter{Appendix: Miscellaneous (Interface to ``typedecl'')}
-\inputif{1/document/Isabelle_code_runtime.tex}
-\chapter{Appendix: Miscellaneous (Overloading ``code\_reflect'')}
-\inputif{1/document/Isabelle_typedecl.tex}
-\inputif{1/document/Generator_dynamic_sequential.tex}
-\inputif{2/document/Clean_backend_old.tex}
+\inputif{2/document/TestSEL4.tex}
 

### 2019-10-30 C11-BackEnds/Clean/document/root.tex
clean

@@
 {\ifthenelse{\equal{}{#1}}{\index{#3 (#2)|bold}}{\index{#3 (#1\ #2)|bold}}} % from 'isar.sty'
-\newcommand{\isactrlC}{{\bf C}}
 
@@
 themselves to the most elementary infrastructure for these tasks. The package is intended to serve
-as demonstrator semantic backend for Isabelle/C~\cite{TuongWolff19}, or for the test-generation
-techniques described in~\cite{DBLP:conf/tap/Keller18}.
+as demonstrator semantic backend for Isabelle/C~\cite{Tuong-IsabelleC:2019}, or for the
+test-generation techniques described in~\cite{DBLP:conf/tap/Keller18}.
 \end{abstract}

### 2021-12-28 Citadelle/src/compiler_generic/document/root.tex
synchronize with 1a42ddd5dbbc https://foss.heptapod.net/isa-afp/afp-devel/-/commit/8602a88cf34434831f86066f12241a398aff3c13

\documentclass[fontsize=11pt,paper=a4,open=right,twoside,abstract=true]{scrreprt}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage[english]{babel}
%\usepackage[draft]{fixme}
\usepackage{graphicx}
\usepackage[numbers, sort&compress, sectionbib]{natbib}
\usepackage{amssymb}
\usepackage{versions}
\usepackage{isabelle,isabellesym}
\usepackage{units}
%\usepackage{eurosym}
\IfFileExists{railsetup.sty}{\usepackage{railsetup}}{}
\usepackage{titletoc}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% short vs. long version

%%%% Short Version:
\includeversion{short}
\excludeversion{extended}

%%%% Extended Version:
%\excludeversion{short}
%\includeversion{extended}

%%%% Misc.:
\newenvironment{shortspace}[1]{}{} %\processifversion{short}{\vspace{#1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% command

\graphicspath{{data/},{figures/}}

%%

\newenvironment{matharray}[1]{\[\begin{array}{#1}}{\end{array}\]} % from 'iman.sty'
\newcommand{\indexdef}[3]%
{\ifthenelse{\equal{}{#1}}{\index{#3 (#2)|bold}}{\index{#3 (#1\ #2)|bold}}} % from 'isar.sty'

%%

\newcommand\inputif[1]{\IfFileExists{./#1}{\input{#1}}{}}
\newcommand\chapterif[2]{\IfFileExists{./#1}{\chapter{#2}}{}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% fix for package declaration to be at the end
\usepackage[pdfpagelabels, pageanchor=false, plainpages=false]{hyperref}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% document

\urlstyle{rm}
\isabellestyle{it}

\begin{document}

\title{A Meta-Model for the Isabelle API}
\author{%
  \href{https://www.lri.fr/~tuong/}{Fr\'ed\'eric Tuong}
  \and
  \href{https://www.lri.fr/~wolff/}{Burkhart Wolff}}
\publishers{%
  \mbox{LRI, Univ. Paris-Sud, CNRS, CentraleSup\'elec, Universit\'e Paris-Saclay} \\
  b\^at. 650 Ada Lovelace, 91405 Orsay, France \texorpdfstring{\\}{}
    \href{mailto:"Frederic Tuong"
    <frederic.tuong@lri.fr>}{frederic.tuong@lri.fr} \hspace{4.5em}
    \href{mailto:"Burkhart Wolff"
    <burkhart.wolff@lri.fr>}{burkhart.wolff@lri.fr} \\[2em]
  %
  IRT SystemX\\
  8 av.~de la Vauve, 91120 Palaiseau, France \texorpdfstring{\\}{}
    \href{mailto:"Frederic Tuong"
    <frederic.tuong@irt-systemx.fr>}{frederic.tuong@irt-systemx.fr} \quad
    \href{mailto:"Burkhart Wolff"
    <burkhart.wolff@irt-systemx.fr>}{burkhart.wolff@irt-systemx.fr}
}

\maketitle

\begin{abstract}
We represent a theory \emph{of} (a fragment of) Isabelle/HOL \emph{in}
Isabelle/HOL. The purpose of this exercise is to write packages for
domain-specific specifications such as class models, B-machines,
\dots, and generally speaking, any domain-specific languages whose
abstract syntax can be defined by a HOL ``datatype''. On this basis, the
Isabelle code-generator can then be used to generate code for global
context transformations as well as tactic code.

Consequently the package is geared towards 
parsing, printing and code-generation to the Isabelle API.
It is at the moment not sufficiently rich for doing meta theory on 
Isabelle itself. Extensions in this direction are possible though.

Moreover, the chosen fragment is fairly rudimentary. However it should be 
easily adapted to one's needs if a package is written on top of it.
The supported API contains types, terms, transformation of
global context like definitions and data-type declarations as well
as infrastructure for Isar-setups.

This theory is drawn from the Featherweight OCL\cite{brucker.ea:featherweight:2014} project where 
it is used to construct a package for object-oriented data-type theories
generated from UML class diagrams. The Featherweight OCL, for example, allows for 
both the direct execution of compiled tactic code by the Isabelle API
as well as the generation of \verb|.thy|-files for debugging purposes.

Gained experience from this project shows that the compiled code is sufficiently
efficient for practical purposes while being based on a formal \emph{model}
on which properties of the package can be proven such as termination of certain
transformations, correctness, etc.
\end{abstract}
\tableofcontents

\parindent 0pt\parskip 0.5ex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\input{session}

\part{A Meta-Model for the Isabelle API}
\chapter{Initialization}
\inputif{Init.tex}
\inputif{Init_rbt.tex}

\chapter{Defining Meta-Models}
\inputif{Meta_Pure.tex}
\inputif{Meta_SML.tex}
\inputif{Meta_Isabelle.tex}
\inputif{Meta_Toy.tex} % toy
\inputif{Meta_Toy_extended.tex} % toy
\inputif{Meta_META.tex}

%\chapter{Toy Libraries Static} % chapter already declared in this following first file:
  \inputif{Toy_Library_Static.tex} % toy

%\chapter{Translating Meta-Models} % chapter already declared in this following first file:
\inputif{Core_init.tex}
\inputif{Floor1_enum.tex}
\inputif{Floor1_infra.tex}
\inputif{Floor1_astype.tex}
\inputif{Floor1_istypeof.tex}
\inputif{Floor1_iskindof.tex}
\inputif{Floor1_allinst.tex}
\inputif{Floor1_access.tex}
\inputif{Floor1_examp.tex}
\inputif{Floor2_examp.tex}
\inputif{Floor1_ctxt.tex}
\inputif{Floor2_ctxt.tex}
\inputif{Core.tex}

\chapter{Parsing Meta-Models}
\inputif{Parser_init.tex}
\inputif{Parser_Pure.tex}
\inputif{Parser_Toy.tex} % toy
\inputif{Parser_Toy_extended.tex} % toy
\inputif{Parser_META.tex}

\chapter{Printing Meta-Models}
\inputif{Printer_init.tex}
\inputif{Printer_Pure.tex}
\inputif{Printer_SML.tex}
\inputif{Printer_Isabelle.tex}
\inputif{Printer_Toy.tex} % toy
\inputif{Printer_Toy_extended.tex} % toy
\inputif{Printer_META.tex}
\inputif{Printer.tex}

\chapter{Main}
\inputif{Generator_static.tex}
\inputif{Generator_dynamic_sequential.tex}

\part{A Toy Example}
\inputif{Toy_Library.tex} % toy
\inputif{Design_deep.tex} % toy
\inputif{Design_shallow.tex} % toy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{abbrvnat}
\bibliography{root}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix
\part{Appendix}
\chapter{Grammars of Commands}
\inputif{Rail.tex}

\chapter{Content of the Directory isabelle\_home}

\begin{itemize}
\item \verb|./src/HOL/ex/Isabelle_Cartouche_Examples.thy|: \\
Some functions have been generalized for supporting cartouches.
\item \verb|./src/Tools/Code/Isabelle_code_runtime.thy|: \\
The option $open$ was introduced in this file for the definition of $code\_reflect'$.
\item \verb|./src/Pure/Isar/Isabelle_typedecl.thy|: \\
Short modification of the argument lifting a $binding$ to a $binding$~$option$ with some signatures removed.
\end{itemize}

\chapter{Content of One Generated File (as example)}
\inputif{Design_generated_generated.tex}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-12-28 Citadelle/src/uml_main/document/root.tex
synchronize with 1a42ddd5dbbc https://foss.heptapod.net/isa-afp/afp-devel/-/commit/8602a88cf34434831f86066f12241a398aff3c13

\documentclass[fontsize=10pt,DIV12,paper=a4,open=right,twoside,abstract=true]{scrreprt}
\usepackage{fixltx2e}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage[english]{babel}
\usepackage{isabelle}
\isatagannexa
  \usepackage{omg}
  \usepackage{draftwatermark}
  \SetWatermarkAngle{55}
  \SetWatermarkLightness{.9}
  \SetWatermarkFontSize{3cm}
  \SetWatermarkScale{1.4}
  \SetWatermarkText{\textbf{\textsf{Draft Proposal}}}
\endisatagannexa
\usepackage[alpine]{ifsym}
\usepackage[nocolortable, noaclist,isasymonly,nocolor]{hol-ocl-isar}
\renewcommand{\lfloor}{\isasymHolOclLiftLeft}
\renewcommand{\rfloor}{\isasymHolOclLiftRight}
\renewcommand{\lceil}{\isasymHolOclDropLeft}
\renewcommand{\rceil}{\isasymHolOclDropRight}
\renewcommand{\oclkeywordstyle}{\bfseries}
\renewcommand{\javakeywordstyle}{\bfseries}
\renewcommand{\smlkeywordstyle}{\bfseries}
\renewcommand{\holoclthykeywordstyle}{}
\renewcommand{\greenkeywordstyle}{}

\usepackage{lstisar}
\usepackage{railsetup}
\usepackage[]{mathtools}
\usepackage{%
  multirow,
  paralist,
  booktabs,     %       "        "      "
  threeparttable,
  longtable,    % Mehrseitige Tabellen 
}

\usepackage{graphicx}
\usepackage[numbers, sort&compress, sectionbib]{natbib}
\usepackage{chapterbib}
\usepackage[caption=false]{subfig}
\usepackage{tabu}
\usepackage{prooftree}
\usepackage[draft]{fixme}
\usepackage[pdfpagelabels, pageanchor=false, bookmarksnumbered, plainpages=false]{hyperref}
\graphicspath{{data/},{figures/}}
\makeatletter
\renewcommand*\l@section{\bprot@dottedtocline{1}{1.5em}{2.8em}}
\renewcommand*\l@subsection{\bprot@dottedtocline{2}{3.8em}{3.7em}}
\renewcommand*\l@subsubsection{\bprot@dottedtocline{3}{7.0em}{5em}}
\renewcommand*\l@paragraph{\bprot@dottedtocline{4}{10em}{6.2em}}
%\renewcommand*\l@paragraph{\bprot@dottedtocline{4}{10em}{5.5em}}
\renewcommand*\l@subparagraph{\bprot@dottedtocline{5}{12em}{7.7em}}
%\renewcommand*\l@subparagraph{\bprot@dottedtocline{5}{12em}{6.5em}}
\makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Overall the (rightfully issued) warning by Koma Script that \rm
%%% etc. should not be used (they are deprecated since more than a
%%% decade)
  \DeclareOldFontCommand{\rm}{\normalfont\rmfamily}{\mathrm}
  \DeclareOldFontCommand{\sf}{\normalfont\sffamily}{\mathsf}
  \DeclareOldFontCommand{\tt}{\normalfont\ttfamily}{\mathtt}
  \DeclareOldFontCommand{\bf}{\normalfont\bfseries}{\mathbf}
  \DeclareOldFontCommand{\it}{\normalfont\itshape}{\mathit}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\setcounter{tocdepth}{3} % printed TOC not too detailed
\hypersetup{bookmarksdepth=3} % more detailed digital TOC (aka bookmarks)
\sloppy
\allowdisplaybreaks[4]
\raggedbottom

\newcommand{\FOL}{FOL\xspace}
\newcommand{\HOL}{HOL\xspace}
\newcommand{\OCL}{OCL\xspace}
\newcommand{\UML}{UML\xspace}
\newcommand{\HOLOCL}{HOL-OCL\xspace}
\newcommand{\FOCL}{Featherweight OCL\xspace}
\newcommand{\ML}{ML\xspace}
\newcommand{\HOCL}{HOL-OCL 2.0\xspace}
\renewcommand{\HolTrue}{\mathrm{True}}
\renewcommand{\HolFalse}{\mathrm{False}}
\newcommand{\ptmi}[1]{\using{\mi{#1}}}
\newcommand{\Lemma}[1]{{\color{BrickRed}%
    \mathbf{\operatorname{lemma}}}~\text{#1:}\quad}
\newcommand{\done}{{\color{OliveGreen}\operatorname{done}}}
\newcommand{\apply}[1]{{\holoclthykeywordstyle%
    \operatorname{apply}}(\text{#1})}
\newcommand{\IIbegin} {{\operatorname{begin}}}
\newcommand{\IIend} {{\operatorname{end}}}
\newcommand{\fun} {{\holoclthykeywordstyle\operatorname{fun}}}
\newcommand{\overloading} {{\holoclthykeywordstyle\operatorname{overloading}}}
\newcommand{\isardef} {{\holoclthykeywordstyle\operatorname{definition}}}
\newcommand{\where} {{\holoclthykeywordstyle\operatorname{where}}}
\newcommand{\datatype} {{\holoclthykeywordstyle\operatorname{datatype}}}
\newcommand{\types} {{\holoclthykeywordstyle\operatorname{types}}}
\newcommand{\Instance} {{\holoclthykeywordstyle\operatorname{Instance}}}
\newcommand{\State} {{\holoclthykeywordstyle\operatorname{State}}}
\newcommand{\Transition} {{\holoclthykeywordstyle\operatorname{Transition}}}
\newcommand{\record} {{\holoclthykeywordstyle\operatorname{record}}}
\newcommand{\tysequence} {\text{\ttfamily Sequence}}
\newcommand{\pglabel}[1]{\text{#1}}
\renewcommand{\isasymOclUndefined}{\ensuremath{\mathtt{invalid}}}
\newcommand{\isasymOclNull}{\ensuremath{\mathtt{null}}}
\newcommand{\isasymOclInvalid}{\isasymOclUndefined}
\DeclareMathOperator{\inv}{inv}
\newcommand{\Null}[1]{{\ensuremath{\mathtt{null}_\text{{#1}}}}}
\newcommand{\testgen}{HOL-TestGen\xspace}
\newcommand{\HolOption}{\mathrm{option}}
\renewcommand{\to}{\Rightarrow}
\newcommand{\ran}{\mathrm{ran}}
\newcommand{\dom}{\mathrm{dom}}
\newcommand{\typedef}{\mathrm{typedef}}
\newcommand{\typesynonym}{\mathrm{type\_synonym}}
\newcommand{\mi}[1]{\,\text{#1}}
\newcommand{\state}[1]{(#1) \operatorname{state}}
\newcommand{\mocl}[1]{\text{\inlineocl|#1|}}
\DeclareMathOperator{\TCnull}{null}
\DeclareMathOperator{\HolNull}{null}
\DeclareMathOperator{\HolBot}{bot}
\newcommand{\isaAA}{\mathfrak{A}}

% urls in roman style, theory text in math-similar italics
\urlstyle{rm}
\isabellestyle{it}
\newcommand{\ie}{i.\,e.\xspace}
\newcommand{\eg}{e.\,g.\xspace}

\newenvironment{isamarkuplazy_text}{\par \isacommand{lazy{\isacharunderscore}text}\isamarkupfalse\isacharverbatimopen\isastyletext\begin{isapar}}{\end{isapar}\isacharverbatimclose}
\newcommand{\isactrlmkUNDERSCOREstring}{\isakeywordcontrol{mk{\isacharunderscore}string}}
\renewcommand{\isasymguillemotleft}{\isatext{\textquotedblleft}}
\renewcommand{\isasymguillemotright}{\isatext{\textquotedblright}}
\begin{document}
\renewcommand{\subsubsectionautorefname}{Section}
\renewcommand{\subsectionautorefname}{Section}
\renewcommand{\sectionautorefname}{Section}
\renewcommand{\chapterautorefname}{Chapter}
\newcommand{\subtableautorefname}{\tableautorefname}
\newcommand{\subfigureautorefname}{\figureautorefname}
\isatagannexa
\renewcommand\thepart{\Alph{part}}
\renewcommand\partname{Annex}
\endisatagannexa

\newenvironment{defholsimple}{\textbf{Definition}\xspace}{}

\newenvironment{matharray}[1]{\[\begin{array}{#1}}{\end{array}\]} % from 'iman.sty'
\newcommand{\indexdef}[3]%
{\ifthenelse{\equal{}{#1}}{\index{#3 (#2)|bold}}{\index{#3 (#1\ #2)|bold}}} % from 'isar.sty'

\isatagafp
  \title{Featherweight OCL}
  \subtitle{A Proposal for a Machine-Checked Formal Semantics for OCL 2.5 %\\
    %\includegraphics[scale=.5]{figures/logo_focl}
  }
\endisatagafp
\isatagannexa
  \title{A Formal Machine-Checked Semantics for OCL 2.5}
  \subtitle{A Proposal for the "Annex A" of the OCL Standard}
\endisatagannexa
\isatagnoexample
  \title{Featherweight OCL (without ``employee'' examples)}
\endisatagnoexample
\author{%
  \href{http://www.brucker.ch/}{Achim D. Brucker}\footnotemark[1]
  \and
  \href{https://www.lri.fr/~tuong/}{Fr\'ed\'eric Tuong}\footnotemark[2]~\footnotemark[3]
  \and
  \href{https://www.lri.fr/~wolff/}{Burkhart Wolff}\footnotemark[2]~\footnotemark[3]}
\publishers{%
  \footnotemark[1]~SAP SE\\
  Vincenz-Priessnitz-Str. 1, 76131 Karlsruhe,
  Germany \texorpdfstring{\\}{} \href{mailto:"Achim D. Brucker"
    <achim.brucker@sap.com>}{achim.brucker@sap.com}\\[2em]
  %
  \footnotemark[2]~LRI, Univ. Paris-Sud, CNRS, CentraleSup\'elec, Universit\'e Paris-Saclay \\
  b\^at. 650 Ada Lovelace, 91405 Orsay, France \texorpdfstring{\\}{}
    \href{mailto:"Frederic Tuong"
    <frederic.tuong@lri.fr>}{frederic.tuong@lri.fr} \hspace{4.5em}
    \href{mailto:"Burkhart Wolff"
    <burkhart.wolff@lri.fr>}{burkhart.wolff@lri.fr} \\[2em]
  %
  \footnotemark[3]~IRT SystemX\\
  8 av.~de la Vauve, 91120 Palaiseau, France \texorpdfstring{\\}{}
    \href{mailto:"Frederic Tuong"
    <frederic.tuong@irt-systemx.fr>}{frederic.tuong@irt-systemx.fr} \quad
    \href{mailto:"Burkhart Wolff"
    <burkhart.wolff@irt-systemx.fr>}{burkhart.wolff@irt-systemx.fr}
}

\maketitle
\isatagannexa
\cleardoublepage
\endisatagannexa

\isatagafp
  \begin{abstract}
    The Unified Modeling Language (UML) is one of the few modeling
    languages that is widely used in industry. While UML is mostly known
    as diagrammatic modeling language (\eg, visualizing class models),
    it is complemented by a textual language, called Object Constraint
    Language (OCL). OCL is a textual annotation language, originally based on a
    three-valued logic, that turns UML into a formal language.
    Unfortunately the semantics of this specification language, captured
    in the ``Annex A'' of the OCL standard, leads to different
    interpretations of corner cases.  Many of these corner cases had
    been subject to formal analysis since more than ten years.

    The situation complicated with the arrival of version 2.3 of the OCL 
    standard. OCL was aligned with the latest version of UML: this led to the 
    extension of the three-valued logic by a second exception element, called
    \inlineocl{null}.  While the first exception element
    \inlineocl{invalid} has a strict semantics, \inlineocl{null} has a
    non strict interpretation. The combination of these semantic features lead
    to remarkable confusion for implementors of OCL compilers and
    interpreters.

    In this paper, we provide a formalization of the core of OCL in
    HOL\@. It provides denotational definitions, a logical calculus and
    operational rules that allow for the execution of OCL expressions by
    a mixture of term rewriting and code compilation. Moreover, we describe
    a coding-scheme for UML class models that were annotated by 
    code-invariants and code contracts. An implementation of this coding-scheme
    has been undertaken: it consists of a kind of compiler that takes a UML class
    model and translates it into a family of definitions and derived
    theorems over them capturing the properties of constructors and selectors,
    tests and casts resulting from the class model. However, this compiler
    is \emph{not} included in this document.

    Our formalization reveals several inconsistencies and contradictions
    in the current version of the OCL standard.  They reflect a challenge
    to define and implement OCL tools in a uniform manner.  Overall, this
    document is intended to provide the basis for a machine-checked text
    ``Annex A'' of the OCL standard targeting at tool implementors.

%% Le Langage de Modélisation Unifié (UML) fait partie des quelques
%% langages de modélisation couramment utilisés dans l'industrie. Alors
%% qu'UML est bien souvent connu comme langage de modélisation de
%% diagrammes (par exemple, comme classes de modèles visuels), il est
%% plus précisément complémenté par un langage textuel, appelé Langage
%% Contraint d'Objet (OCL). OCL est un langage d'annotation textuel,
%% originellement basé sur une logique 3-valuée, et fait ainsi apparaître
%% UML comme un langage plutôt formel. Pourtant la sémantique de ce
%% langage de spécification, instinctivement décrit dans l'annexe A du
%% standard d'OCL, mène à différentes interprétations concernant le sens
%% précis des informations véhiculées. Ces différentes interprétations
%% sont encore en cours d'élucidation depuis plus de dix ans via
%% notamment l'emploi d'outils d'analyse formelle.
%% 
%% La situation s'est compliquée avec la mise à jour vers la version 2.3
%% du standard d'OCL. Étant donné qu'OCL dépends de la dernière version
%% d'UML, il a été nécessaire d'introduire comme extension à la logique
%% 3-valuée un second élément d'exception, qui est null. Ce qui le
%% différencie avec le premier élément d'exception invalid, c'est sa
%% sémantique non-stricte, alors qu'invalid a une sémantique stricte. La
%% combinaison de ces variétés sémantiques a finalement abouti à divers
%% confusions lors de l'implémentation de compilateurs OCL.
%% 
%% Dans ce papier, nous apportons une formalisation du cœur d'OCL en
%% HOL. Il contient des définitions dénotationnelles, un système de
%% calcul logique et des règles opérationnelles permettant l'exécution
%% des expressions OCL à travers une mixture de règles de réécriture et
%% de compilation de code. De plus, nous décrivons un schéma de codage
%% pour les modèles de classes UML pour représenter les invariants et
%% contrats UML. Une implémentation de ce schéma de codage a été
%% effectuée : il s'agit d'un genre particulier de compilateur acceptant
%% en entrée des classes de modèles UML et générant en sortie une famille
%% de définitions, théorèmes associés sur les propriétés des
%% constructeurs et sélecteurs, fonctions de tests ainsi que des
%% mutations de types. Ce compilateur n'est cependant pas inclus dans ce
%% document.
%% 
%% Nos formalisations ont finalement révélés des inconsistances et
%% contradictions concernant la version courante du standard d'OCL. Par
%% ailleurs cela représente un challenge de définir et implémenter des
%% outils pour OCL de manière uniformément cohérente. Ce document a pour
%% but de fournir des bases vérifiées mécaniquement, et servir comme
%% support sémantique à l'Annexe A du standard d'OCL ciblant
%% particulièrement les programmeurs d'outils et compilateurs.
  \end{abstract}
  \tableofcontents
\endisatagafp

\part{Formal Semantics of OCL}
\input{introduction}
%\clearpage
\isatagafp
\input{session}
\endisatagafp
\isatagnoexample
\input{session}
\endisatagnoexample
\isatagannexa
\input{UML_Types.tex}
\input{UML_Logic.tex}
\input{UML_PropertyProfiles.tex}
\input{UML_Boolean.tex}
\input{UML_Void.tex}
\input{UML_Integer.tex}
\input{UML_Real.tex}
\input{UML_String.tex}
\input{UML_Pair.tex}
\input{UML_Bag.tex}
\input{UML_Set.tex}
\input{UML_Sequence.tex}
\input{UML_Library.tex}
\input{UML_State.tex}
\input{UML_Contracts.tex}
%\input{UML_Tools.tex}
%\input{UML_Main.tex}
% \input{Design_UML.tex}
% \input{Design_OCL.tex}
\input{Analysis_UML.tex}
\input{Analysis_OCL.tex}
\part{Bibliography}
\endisatagannexa
\isatagafp
\input{conclusion} %no conclusion for standard document
\endisatagafp
\bibliographystyle{abbrvnat}
\bibliography{root}

\isatagafp
\appendix
\part{Appendix}
\endisatagafp
\input{FOCL_Syntax}

\isatagannexa
  \part{Table of Contents}
  \clearpage {\small \tableofcontents }
\endisatagannexa
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

%  LocalWords:  implementors denotational OCL UML
